### 2012-07-14 paper.tex
initial version from 8dbdd3f of aksw svn repo

\documentclass[a4paper]{llncs}
\usepackage{comment}
\usepackage{printlen} % Print lengths using specified units. 
%\usepackage{hyperref}
\usepackage{booktabs}
\usepackage[utf8]{inputenc} % Umlaute üöä auch normal benutzen und nicht maskieren
\usepackage{color}
% http://www.ctan.org/tex-archive/fonts/ps-type1/cm-super/
\usepackage[T1]{fontenc} % use high quality fonts, please install cm-super
\usepackage[pdftex]{graphicx}
\graphicspath{{./Depictions/}}
\DeclareGraphicsExtensions{.pdf,.jpeg,.jpg,.png}
\usepackage[T1]{url}
\usepackage{listings}
\usepackage{subfig}
\usepackage{printlen} % Print lengths using specified units.
\usepackage{booktabs}
%\usepackage[textsize=tiny]{todonotes}
\usepackage{todonotes}

\usepackage[
pdftex,
bookmarks=true,
hidelinks,
unicode=true,
pdfauthor={Sebastian Tramp, Henry Story, Philipp Frischmut, Timofey Ermilov, and S\"oren Auer},
pdftitle={Extending the WebID Protocol with Access Delegation},
pdfkeywords={WebID, Social Semantic Web, Access Delegation}
]{hyperref}

\title{Extending the WebID Protocol with Access Delegation}

\author{Sebastian Tramp\inst{1} \and Henry Story\inst{2} \and Philipp Frischmuth\inst{1} \and Timofey Ermilov\inst{1} \and S\"oren Auer\inst{1}}

\institute{
Universit\"at Leipzig, Institut f\"ur Informatik, AKSW,\\
Postfach 100920, D-04009 Leipzig, Germany,\\
\email{\{lastname\}@informatik.uni-leipzig.de}\\
\url{http://aksw.org/FirstnameLastname} (WebID)
\medskip\and
Apache Foundation\\ 
\email{henry.story@bblfish.net}\\
\url{http://bblfish.net/people/henry/card\#me} (WebID)
}

\authorrunning{Sebastian Tramp et al.}

%%%%% LISTINGS
\usepackage{listings} % Typeset source code listings using LaTeX.
% listing styles
\lstset{%
    numberbychapter=false,
    numberblanklines=true,
    numbers=left,
    numberstyle=\tiny,
    basicstyle=\ttfamily\footnotesize,
    emphstyle=\textit,
    tabsize=2,
    framexleftmargin=2pt,
    captionpos=b,
    frame=single,
    breaklines=true
}
\lstdefinestyle{rdf}{morekeywords={}}
\lstdefinestyle{sparql}{
    morekeywords={SELECT,OPTIONAL,FROM,DISTINCT,a,WHERE,FILTER,GROUP,ORDER,LIMIT,BY,IN,AS},
    emph={s,p,o}
}
\lstdefinestyle{turtle}{
    morekeywords={a, @prefix, cert,xsd,foaf, rdf, rdfs, owl},
    morecomment=[s][\textrm]{<}{>},
    morecomment=[s][\textit]{"}{"},
}

\begin{document}

\maketitle              % typeset the title of the contribution

\begin{abstract}
We propose \ldots
\end{abstract}

\section{Introduction and Terminology}\label{sec:intro}

% this prints the current textwidth, so images can be
% generated perfectly fitting to the page (LNCS textwidth: 121.99854 mm)
%\uselengthunit{mm}\printlength{\textwidth}
%\uselengthunit{mm}\printlength{\columnwidth}

\cite{story-h-2009--a}
\cite{tramp-s-2012--a}

%\begin{figure}[!t]
%\centering
%\includegraphics[width=2.5in]{myfigure}
%\caption{Simulation Results}
%\label{fig_sim}
%\end{figure}

A \textit{WebID} is a URI that refers to an Agent - Person, Robot, Group or other thing that can have Intentions.
The WebID should be a URI which when dereferenced returns a representation whose description uniquely identifies the Agent as the controller of a public key~\cite{sporny-m-2011--a}.
As a non-exclusive alternative, we propose that this description can also refer to a secretary agent WebID for access delegation.
This allows even for WebID descriptions which do not control a public key itself and only delegate access to other WebIDs (refer to \autoref{sec:WorkingGroups}).

In the context of access delegation, we distinguish a WebID which refers to an agent which has direct access to a certain resource from a WebID which refers to an agent which has access to a resource only if he acts in the name of the first agent.
We call the latter agent the \textit{secretary agent} and the first one the \textit{named agent}.
\todo{maybe another name here?}

\textit{Access Delegation} is a relation between two WebID resources.
The relation describes, under which circumstances a secretary agent has access to a certain resource under the same constraints as the named agent.
The secretary agent declares to act in the name of the named agent.

\section{Requirements}

This sections lists the most crucial use-cases which require access delegation and which can not be solved with the standard WebID authentication protocol.
In addition to that, we list derived implementation requirements.

\subsection{Basic Use-Cases for Access Delegation}\label{sec:usecases}

\paragraph{Personal Devices and Applications}

Currently, the default usage intention for WebIDs are browser-based authentication scenarios.
This is an important use-case and should be of special interest but we use the world wide web not only from our browsers but also from other applications and from other application on other devices such as smartphones, tablets and freedomboxes\footnote{\url{https://freedomboxfoundation.org/}}.
In a typical every day usage scenario, we use feed readers and social network clients hand in hand with web browsers.
This is true esp. for mobile devices where specialized clients for social activities are widely in use and does exist even for academically driven social networks as the distributed Social Web based on FOAF WebIDs~\cite{tramp-s-2011--a}.

All these applications have in common that they act in the name of its users and fetch and manipulate resources in a way that this could also be done by the user itself and with her browser.
In a WebID-enabled communication scenario, these devices use their own certificates for communication since we do not want to copy the browser certificate to these devices and we also do not want to save the passphrase on theses devices and services.

\paragraph{Vacation Replacement}

In a typical office scenario, employees declare vacation replacements for the time of their holiday in order to achieve an uninterruptible service during that time.
One option to allow access to this vacation replacement is to give him the original certificate or to add his private key to the users WebID.
This solution has two drawbacks: (1) the users certificate is burned after the vacation and she needs to create a new one, (2) a resource guard can not distinguish between the user and the vacation replacement user, which allows for abuse.

In this context, the named agent is the employee which is on holiday and her vacation replacement is the secretary agent.

\paragraph{Working Groups}\label{sec:WorkingGroups}

Access for working groups to a resource is typically specified in a way that each resource guard needs to hold a list of group members of this group.
In the Social Semantic Web, these working groups have its own WebID resources which describe the group as an entity and its members as relations to their user WebIDs.
To authorize a group of agents to access a resource should be as simple as to a single agent.
In order to allow this, we define the group as the named agent and all group members as its secretary agents.

An alternative could be to share one single group certificate with all members or to create a group certificate for each member and describe all public keys in the group WebID.
Again, these solutions have different drawbacks: (1) a shared certificate needs to be updated each time a user leaves the group, (2) multiple group certificates for each user does not allow for distinguishing which user accessed the resource, which allows for abuse.

In this context, the group is the named agent and all current group members are secretary agents.

\paragraph{Office Roles}

An office role is a construct where a user can access specific resources because of his working description.
A product manager has access to all product related resources because of her role as product manager and not because of her identity.
The role itself is identified by WebID and all access authorization rules should use this role WebID instead of a user WebID.

In this context, the role is the named agent and the current role owner is the secretary agent.

\subsection{Implementation Requirements}\label{sec:req}

Based on the given use-cases from \autoref{sec:usecases} and additional preliminary considerations, we issued the following implementation relevant requirements for an access delegation solution based on the WebID authentication protocol.

\paragraph{Distinguish secretary agents from named agents}
Delegation should not be handled by camouflaging an request of an agent in the sense that this request is indistinguishable from a named agent request.
A secretary agent should use its own certificate and it should be identified and described by its own WebID profile.
The motivation for this is twofold.
Firstly, it allows resource guards to permit or deny requests based on this information.
Secondly, applications which are secretary for many different named agents do not need to switch their certificate between requests.
Also they do not need to handle hundreds of different keys.

\paragraph{Easy to use}
The one and only place to describe which secretary agents are allowed to operate as a named agent should be the WebID profile itself.
To grant delegated access to a secretary agent, no other actions than simply adding triples to the WebID profile should be needed.
To reset this grant the same triple can removed from the WebID profile.

\paragraph{Linked Data and Read Write Web integration}

The solution we try to architect aims to enhance the communication for consumption and modification of Linked Data esp. from the applications point of view.
This means, that existing Linked Data as well as Read-Write-Web principles should not be violated by the architecture.
\todo{what does rww means here?}

\paragraph{Minimal protocol footprint}

In addition to the integration requirement, we argue that a minimal protocol footprint should be achieved to allow a wide adoption of the extension.
This includes the requirement to not add an additional service to the process of authentication than using the existing ones.

\paragraph{No enforcement to reveal agent identities}\todo{maybe we kick this ...}

%Since we know that social networks play an important role in a context where communication is restricted by different parties, an

\section{Specification of the WebID protocol extension}\label{sec:spec}

\autoref{fig:AuthSequence} depicts the process of a WebID authentication which is extended with the following components to allow access delegation:

\begin{itemize}
    \item The requesting agent (the secretary) claims a request as requested in the name of a named agent (see point 2).
        This adds a HTTP request header to the specification.
    \item The WebID verifier needs to verify not only one but two different WebID incl. the relation between these two resources (see point 4).
        This adds additional verification rules to the specification.
    \item The named agent (Bob) can declare any relation to his secretary agents in his WebID profile.
        This adds a vocabulary for describing access delegation to the specification.
\end{itemize}

\begin{figure*}[htb]
  \centering
  \includegraphics[width=\textwidth]{AuthSequence}
  \caption{Extended WebID authentication sequence}
  \label{fig:AuthSequence}
\end{figure*}

The following enumeration describe each authentication step in detail but concentrates on the context of access delegation:

\begin{enumerate}
    \item Bob's secretary agent opens a TLS connection with the server of the protected resource.
    \item Once TLS is set up, the HTTP request is sent to the server (e.g. a \verb!HTTP GET!) to consume or manipulate a resource.
        Here our first addition comes into play, the HTTP request header to claim an request as a secretary.
        We assume that the guard intercepts this HTTP request, and requests for a client authentication (using the TLS service)
    \item This authentication request is done using public key cryptography, sign a token with the guards private key and have the secretary send its certificate.
        This is defined in the TLS protocol which is specified in \cite{dierks-t-2012--a} and its successive RFCs.
        At the end of this step, the secretaries certificate is handled back to the guard.
    \item The guard ask the verification agent to verify the WebID is named in the certificate.

        %The WebID Certificate is then passed on to the Guard with the proviso that the WebIDs still needs to be verified.
    %The Guard then must ask the Verification Agent to verify that the WebIDs do identify the agent who knows the given public key.
    %The WebID is verified by looking up the definition of the URL at its canonical location. This can be done by dereferencing it. The Verification Agent must extract the public key and all the URI entries contained in the Subject Alternative Name extension of the WebID Certificate. A WebID Certificate may contain multiple URI entries which are considered claimed WebIDs at this point, since they have not been verified. The Verification Agent may verify as many or as few WebIDs it has time for. It may do it in parallel and asynchronously. However that is done, a claimed WebIDs can only be considered verified if the following steps have been accomplished successfully:
        %If the WebID Verifier does not have an up to date version of the WebID profile in the cache, then it must dereference the WebID using the canonical method for dereferencing a URL of that scheme. For an https://... WebID this would be done using the [HTTP-TLS] protocol.
        %The returned representation is then transformed into an RDF graph as specified in Processing the WebID Profile
        %That graph is then queried as explained in Querying the Graph. If the query succeeds, then that WebID is verified.
    %With the set of verified WebIDs the Guard can then check its access control rules using information from the web and other information available to it, to verify if the referent of the WebID is indeed allowed access to the protected resource. The exact nature of those Access Control Rules is left for another specification. Suffice it to say that it can be something as simple as a lookup in a table.
    %If access is granted, then the guard can pass on the request to the protected resource, which can then interact unimpeded with the client.
\end{enumerate}

\lstinputlisting[
    lastline=12,name=webid,style=turtle,float=htb,label=listing:webid1,
    basicstyle=\ttfamily\scriptsize,
    caption={Minimal WebID profile including a public key}
]{Listings/webid1.ttl}

\lstinputlisting[
    firstnumber=last,firstline=13,name=webid,style=turtle,float=htb,label=listing:webiddelegation,
    basicstyle=\ttfamily\scriptsize,
    caption={Access delegation by explicitly and implicitly identifying agents or application},
]{Listings/webid1.ttl}

\lstinputlisting[
    name=schema,style=turtle,float=htb,label=listing:schema,
    basicstyle=\ttfamily\scriptsize,
    caption={Schema description of the delegation property},
]{Listings/schema.ttl}

\section{Evaluation}\label{sec:eval}

\bibliographystyle{IEEEtran}
\bibliography{webid}

\end{document}

### 2012-07-15 paper.tex

@@
 
-\author{Sebastian Tramp\inst{1} \and Henry Story\inst{2} \and Philipp Frischmuth\inst{1} \and Timofey Ermilov\inst{1} \and S\"oren Auer\inst{1}}
+\author{Sebastian Tramp\inst{1} \and Henry Story\inst{2} \and Philipp Frischmuth\inst{1} \and Timofey Ermilov\inst{1} \and S\"oren Auer\inst{1} \and Andrei Sambra\inst{3}}
 
@@
 \url{http://bblfish.net/people/henry/card\#me} (WebID)
+\medskip\and
+CNRS Samovar UMR 5157, TELECOM SudParis\\
+\email{andrei.sambra@it-sudparis.eu}\\
+\url{https://my-profile.eu/people/deiu/card\#me} (WebID)
 }
@@
 We call the latter agent the \textit{secretary agent} and the first one the \textit{named agent}.
-\todo{maybe another name here?}
+\todo{maybe another name here? (A:Agent and delegatedAgent maybe?)}
 
@@
 
-\subsection{Basic Use-Cases for Access Delegation}\label{sec:usecases}
+\subsection{Basic Use-Cases for Access Delegation}\label{sec:usecases}\todo{A: IMHO two major cases, 'attended' and 'unattended'}
 
@@
 This is true esp.
-for mobile devices where specialized clients for social activities are widely in use and does exist even for academically driven social networks as the distributed Social Web based on FOAF WebIDs~\cite{tramp-s-2011--a}.
+for mobile devices where specialized clients for social activities are widely in use and does exist even for academically driven social networks as the distributed Social Web \todo{A: req.
+explaining?
+(Web2.0 vs 3.0 ambiguity)} %Web2.0 or 3.0?
+the begining of the sentence talks about 2.0, and you end with FOAF (3.0)?
+ based on FOAF WebIDs~\cite{tramp-s-2011--a}.
 
@@
 \paragraph{Working Groups}\label{sec:WorkingGroups}
-
-Access for working groups to a resource is typically specified in a way that each resource guard needs to hold a list of group members of this group.
-In the Social Semantic Web, these working groups have its own WebID resources which describe the group as an entity and its members as relations to their user WebIDs.
+\todo{A: why 'working' and not just 'Groups'? (difference?)}
+Access for working groups to a resource is typically specified in a way that each resource guard \todo{A: is it really the guard who holds the list, or some access control sys?} needs to hold a list of group members of this group.
+In the Social Semantic Web \todo{A: see my prev.
+note about Web2.0 vs 3.0}, these working groups have its own WebID resources which describe the group as an entity and its members as relations to their user WebIDs.
 To authorize a group of agents to access a resource should be as simple as to a single agent.
@@
 
-In this context, the group is the named agent and all current group members are secretary agents.
+In this context, the group is the named agent and all current group members are secretary agents.\todo{A: not sure I agree (see source)}%the group is not an entity, therefore it cannot take actions by iteself.
+Actions are always performed by users, as part of the group.
 
 \paragraph{Office Roles}
-
+\todo{A: how is this different from the prev. case?}
 An office role is a construct where a user can access specific resources because of his working description.
@@
     caption={Schema description of the delegation property},
-]{Listings/schema.ttl}
+]{Listings/schema.ttl}\todo{A:why add the public key of the agent here? (revocation issues)}
 

### 2012-07-16 paper.tex
add todo notes from the telco

@@
 unicode=true,
-pdfauthor={Sebastian Tramp, Henry Story, Philipp Frischmut, Timofey Ermilov, and S\"oren Auer},
+pdfauthor={Sebastian Tramp, Henry Story, Andrei Sambra, Philipp Frischmut, Timofey Ermilov, and S\"oren Auer},
 pdftitle={Extending the WebID Protocol with Access Delegation},
@@
 
-\author{Sebastian Tramp\inst{1} \and Henry Story\inst{2} \and Philipp Frischmuth\inst{1} \and Timofey Ermilov\inst{1} \and S\"oren Auer\inst{1} \and Andrei Sambra\inst{3}}
+\author{Sebastian Tramp\inst{1} \and Henry Story\inst{2} \and Andrei Sambra\inst{3} \and Philipp Frischmuth\inst{1} \and Timofey Ermilov\inst{1} \and S\"oren Auer\inst{1}
 
@@
 
+\todo{ST: distinguish delegation of authorization vs. authentification}
+
 % this prints the current textwidth, so images can be
@@
 In a WebID-enabled communication scenario, these devices use their own certificates for communication since we do not want to copy the browser certificate to these devices and we also do not want to save the passphrase on theses devices and services.
+
+\todo{Sebastian Tramp: Extend it with respect to the Extended Mind paper}
 
@@
 
+\section{Related Work}\label{sec:relatedwork}
+
+\subsection{oAuth}
+\todo{Andrei Sambra: Compare to oAuth}
+
+\subsection{Cross Origin Resource Sharing (CORS)}
+\todo{Henry Story: Compare to CORS in the context of Consuming Linked Data}
+
 \section{Evaluation}\label{sec:eval}
+
+\todo{Andrei Sambra: MyProfile description}
 

### 2012-07-18 paper.tex

@@
 bookmarks=true,
-hidelinks,
+%hidelinks,
 unicode=true,
@@
 
-\author{Sebastian Tramp\inst{1} \and Henry Story\inst{2} \and Andrei Sambra\inst{3} \and Philipp Frischmuth\inst{1} \and Timofey Ermilov\inst{1} \and S\"oren Auer\inst{1}
+\author{Sebastian Tramp\inst{1} \and Henry Story\inst{2} \and Andrei Sambra\inst{3} \and Philipp Frischmuth\inst{1} \and Timofey Ermilov\inst{1} \and S\"oren Auer\inst{1}}
 
@@
 We call the latter agent the \textit{secretary agent} and the first one the \textit{named agent}.
-\todo{maybe another name here? (A:Agent and delegatedAgent maybe?)}
 
@@
 
-\subsection{Basic Use-Cases for Access Delegation}\label{sec:usecases}\todo{A: IMHO two major cases, 'attended' and 'unattended'}
+\subsection{Basic Use-Cases for Access Delegation}\label{sec:usecases}
 
@@
 \paragraph{Office Roles}
-\todo{A: how is this different from the prev. case?}
 An office role is a construct where a user can access specific resources because of his working description.
@@
     caption={Access delegation by explicitly and implicitly identifying agents or application},
+    label={list:sec_relation},
 ]{Listings/webid1.ttl}
@@
 
-\subsection{oAuth}
+\subsection{OAuth}
 \todo{Andrei Sambra: Compare to oAuth}
+
+OAuth~2.0\footnote{http://tools.ietf.org/html/draft-ietf-oauth-v2} is the latest version of the OAuth protocol, which is being presented as an access delegation protocol, enabling users to grant third-party access to their web resources without sharing their passwords.
+Even if OAuth provides authentication as a byproduct of having the resource owner authorize a client to a resource server, its main focus is on authorization rather than on federated identity.
+
+OAuth includes two main parts: obtaining a token by asking the user to grant access, and using tokens to access protected resources (Fig.~\ref{fig:oauth2flow}).
+OAuth has been designed around the following client profiles:
+
+\paragraph*{web application} -- A web application is a confidential client running on a web server.
+Resource owners access the client via an HTML user interface rendered in a user-agent on the device used by the resource owner.
+
+\paragraph*{user-agent-based application} -- A user-agent-based application is a public client in which the client code is downloaded from a web server and executes within a user-agent (e.g.
+web browser) on the device used by the resource owner.
+
+\paragraph*{native application} -- A native application is a public client installed and executed on the device used by the resource owner.
+Protocol data and credentials are accessible to the resource owner.\\
+
+OAuth defines four basic roles:
+
+\begin{figure*}[htb]
+  \centering
+  \includegraphics[width=\textwidth]{Oauth2.pdf}
+  \caption{OAuth 2.0 protocol flow}
+  \label{fig:oauth2flow}
+\end{figure*}
+
+\begin{enumerate}
+\item resource owner -- An entity capable of granting access to a protected resource. When the resource owner is a person, it is referred to as an end-user (i.e. you).
+
+\item resource server -- The server hosting the protected resources, capable of accepting and responding to protected resource requests using access tokens.
+
+\item client -- An application which accesses a resource owner's protected resources after the resource owner has explicitly granted it permission -- this last part can also be rephrased into "after the resource owner has authorized the client to his/her protected resources".
+
+\item authorization server -- The server issuing access tokens to the client after successfully authenticating the resource owner and obtaining authorization.
+The authorization server may be the same server as the resource server or a separate entity.
+\end{enumerate}
+
+The OAuth protocol flow in Fig.~\ref{fig:oauth2flow} can be explained as follows:
+
+\paragraph*{(A)} The client initiates the flow by directing the resource owner's user-agent to the authorization endpoint.
+The client includes         its client identifier, requested scope, local state, and a redirection URI to which the authorization server will send the user-agent back once access is granted (or denied).
+
+\paragraph*{(B)} The authorization server authenticates the resource owner (via the user-agent) and establishes whether the resource owner grants or denies the client's access request.
+
+\paragraph*{(C)} Assuming the resource owner grants access, the authorization server redirects the user-agent back to the client using the redirection URI provided earlier (in the request or during client registration).
+The redirection URI includes an authorization code and any local state provided by the client earlier.
+
+\paragraph*{(D)} The client requests an access token from the authorization server's token endpoint by including the authorization code received in the previous step.
+When making the request, the client authenticates with the authorization server.
+The client includes the redirection URI used to obtain the authorization code for verification.
+
+\paragraph*{(E)} The authorization server authenticates the client, validates the authorization code, and ensures the redirection URI received matches the URI used to redirect the client in step (C).
+If valid, the authorization server responds back with an access token and optionally, a refresh token.
+A single access token may grant varying degrees of access to multiple APIs.
+The set of resources and operations permitted by an access token is controlled during the access token request via a variable parameter called \textit{scope}.
+Several scopes may be included in a request.\\
+
+To summarize what we have seen so far, OAuth is not exactly an access delegation protocol, but rather a protocol which authorizes a resource consumer to securely access data from a resource server.
+Once the access token has been created, both applications communicate directly between themselves, without any need for delegation.
+
+We can only assume that in a non-Linked Data environment, one can take advantage of OAuth in order to create the trust relationship between a user (agent) and the secretary (cf.
+Listing~\ref{list:sec_relation}), while access delegation would take place at a later time.
+
+%As opposed to WebID Access Delegation where the resource owner specifies the secretary relation using Linked Data (cf.
+Listing~\ref{list:sec_relation})\todo{A: Linked Data reference?}, OAuth requires a pre-existing relationship between resource consumer and resource server, in the form of a shared secret.
+The OAuth relationship is created by manually registering \textit{each} resource consumer with the resource server.
+Furthermore, explicit user consent is required each time a new resource consumer requires access to the user's resource server.
 

### 2012-07-19 paper.tex
remove comment package, fix bibstyle
add notes

@@
 \documentclass[a4paper]{llncs}
-\usepackage{comment}
 \usepackage{printlen} % Print lengths using specified units. 
@@
 All these applications have in common that they act in the name of its users and fetch and manipulate resources in a way that this could also be done by the user itself and with her browser.
+
+We distinguish two different classes of applications here.
+(1) Applications which provide their service to one user only and run on a device which can be accessed by one user only (e.g. a smartphone).
+These applications have more in common with the users browser and can be seen as an extension to the user itself (\cite[extendedmind]).
+
 In a WebID-enabled communication scenario, these devices use their own certificates for communication since we do not want to copy the browser certificate to these devices and we also do not want to save the passphrase on theses devices and services.
@@
 \todo{Andrei Sambra: Compare to oAuth}
+\todo{If we were to implement a secreteary like feature using OAuth what would it look like? what would the differences be?}
 
@@
 
-\bibliographystyle{IEEEtran}
+\bibliographystyle{plain}
 \bibliography{webid}

### 2012-07-24 paper.tex
add clark reference

@@
 
-\section{Introduction and Terminology}\label{sec:intro}
+\section{Introduction}\label{sec:intro}
 
-\todo{ST: distinguish delegation of authorization vs. authentification}
+The World Wide Web is a peer to peer communication system designed from the outset to work in a global space, between agents distributed around the world and acting in parallel, with no center of control, in a space where new agents can at any point join and there is no complete overview of the whole system.
+These agents need know nothing of each other up to the point of their interaction.
+This is the force that leads the web to its declarative functional architecture, with its emphasis on naming and a logic of unalterability of the meaning of names (URIs).
+
+Agents on the web communicate with each other through a limited number of actions:  by making requests for resources ( GET ), or by creating resources ( POST or PUT ), or even by deleting resources...
+Creation or deletion of resources usually require authentication of the agent making the request, and so in many cases do requests for information (GET).
+
+The WebID protocol enables the global identification of agents using asymetric cryptography in a way that fits cleanly with this architecture: namely in such a way that agents can verify each others identity without having had any previous interactions and in such a way as to allow trust to build up in a decentralised manner.
+
+A \textit{WebID} is a URI that refers to an Agent - Person, Robot, Group or other thing that can have Intentions.
+The WebID should be a URI which when dereferenced returns a representation whose description uniquely identifies the Agent as the controller of a public key~\cite{sporny-m-2011--a}.
+
+The WebID protocol is used currently mostly for client authentication.
+\footnote{Server authentication using IETF DANE follows much the same logic, except that the lookup for the identity is not done using the HTTP protocol but DNSSEC .} It is worth noting that the server serving the WebID profiles controls the identity of every agent whose URI is within that server's namespace.
+This service is known as the Origin Server \footnote{RFC6454: The Web Origin Concept http://tools.ietf.org/html/rfc6454}.
+It is the Origin of all resources served by it.
+
+We can easily think of the Origin Server as not only able to respond to requests, but also as an agent able to make
+requests.
+Indeed WebID authentication requires the server to make WebID Profile requests to other servers in order to verify the identity of agents making a request to it.
+The WebID spec describes this task as being accomplished by a seperate agent, the WebID Verifier - which could indeed be done by another service on the internet ( WebID Proxy Authentication servers).
+But it can also be so closely tied to the web service that it would be natural to think of it as part of that same service.
+The WebID Profile furthermore could be served by the same agent as the one making the request, in which case we have a minimal case of a peer to peer communication.
+Note that fetching a WebID profile for WebID Authentication should be done anonymously, for fear of authentication deadlocks.
+
+Things get more interesting in the Authorization space.
+Consider a very natural application of WebID: allowing friends of one's friends ( foaf ) access to some resources.
+This authorization rule will require the Web Server to fetch each of its users' friends profiles, in order to build up such a list.
+But there is a privacy issue involved here: not every one wants to make all of their social network (or even any of it) publically visible.
+Those people may then protect their FOAF Profile with Access Control rules.
+How can a server that needs access to these FOAF profiles in order to apply its own access control rules get access to the information?
+Should it be able to do so?
+These are the questions we will try to answer in this paper.
+
+\section{Solution 1: Using each users WebID}
+
+\section{Solution 2: Acting on Behalf of a User}
+
+\section{Comparison with Other protocols}
+
+\section{OAuth}
+
+\section{CORS}
 
@@
 
-A \textit{WebID} is a URI that refers to an Agent - Person, Robot, Group or other thing that can have Intentions.
-The WebID should be a URI which when dereferenced returns a representation whose description uniquely identifies the Agent as the controller of a public key~\cite{sporny-m-2011--a}.
-As a non-exclusive alternative, we propose that this description can also refer to a secretary agent WebID for access delegation.
-This allows even for WebID descriptions which do not control a public key itself and only delegate access to other WebIDs (refer to \autoref{sec:WorkingGroups}).
-
-In the context of access delegation, we distinguish a WebID which refers to an agent which has direct access to a certain resource from a WebID which refers to an agent which has access to a resource only if he acts in the name of the first agent.
-We call the latter agent the \textit{secretary agent} and the first one the \textit{named agent}.
+\section{Terminology}
 
@@
 (1) Applications which provide their service to one user only and run on a device which can be accessed by one user only (e.g. a smartphone).
-These applications have more in common with the users browser and can be seen as an extension to the user itself (\cite[extendedmind]).
+These applications have more in common with the users browser and can be seen as an extension to the user itself \cite{clark-a-1998-7-a}.
 

### 2012-07-27 paper.tex
nicip intro, add rfc reference, add svg

@@
 
-Agents on the web communicate with each other through a limited number of actions:  by making requests for resources ( GET ), or by creating resources ( POST or PUT ), or even by deleting resources...
+Agents on the web communicate with each other through a limited number of actions: by making requests for resources (GET), or by creating resources ( POST or PUT ), or even by deleting resources...
 Creation or deletion of resources usually require authentication of the agent making the request, and so in many cases do requests for information (GET).
 
-The WebID protocol enables the global identification of agents using asymetric cryptography in a way that fits cleanly with this architecture: namely in such a way that agents can verify each others identity without having had any previous interactions and in such a way as to allow trust to build up in a decentralised manner.
+The WebID protocol enables the global identification of agents using asymmetric cryptography in a way that fits cleanly with this architecture: namely in such a way that agents can verify each others identity without having had any previous interactions and in such a way as to allow trust to build up in a decentralized manner.
 
@@
 
-The WebID protocol is used currently mostly for client authentication.
-\footnote{Server authentication using IETF DANE follows much the same logic, except that the lookup for the identity is not done using the HTTP protocol but DNSSEC .} It is worth noting that the server serving the WebID profiles controls the identity of every agent whose URI is within that server's namespace.
-This service is known as the Origin Server \footnote{RFC6454: The Web Origin Concept http://tools.ietf.org/html/rfc6454}.
+The WebID protocol is used currently mostly for client authentication%
+\footnote{Server authentication using IETF DANE follows much the same logic, except that the lookup for the identity is not done using the HTTP protocol but DNSSEC.}.
+It is worth noting that the server serving the WebID profiles controls the identity of every agent whose URI is within that server's namespace.
+This service is known as the Origin Server~\cite{barth-a-2011--a}.
 It is the Origin of all resources served by it.
 
-We can easily think of the Origin Server as not only able to respond to requests, but also as an agent able to make
-requests.
+We can easily think of the Origin Server as not only able to respond to requests, but also as an agent able to make requests.
 Indeed WebID authentication requires the server to make WebID Profile requests to other servers in order to verify the identity of agents making a request to it.
-The WebID spec describes this task as being accomplished by a seperate agent, the WebID Verifier - which could indeed be done by another service on the internet ( WebID Proxy Authentication servers).
+The WebID spec describes this task as being accomplished by a separate agent, the WebID Verifier - which could indeed be done by another service on the web (WebID Proxy Authentication servers).
 But it can also be so closely tied to the web service that it would be natural to think of it as part of that same service.
@@
 Things get more interesting in the Authorization space.
-Consider a very natural application of WebID: allowing friends of one's friends ( foaf ) access to some resources.
+Consider a very natural application of WebID: allowing friends of one's friends (foaf) access to some resources.
 This authorization rule will require the Web Server to fetch each of its users' friends profiles, in order to build up such a list.
-But there is a privacy issue involved here: not every one wants to make all of their social network (or even any of it) publically visible.
+But there is a privacy issue involved here: not every one wants to make all of their social network (or even any of it) publicly visible.
 Those people may then protect their FOAF Profile with Access Control rules.

### 2012-07-27 paper.tex
some small fixes in the introduction

@@
 
-Agents on the web communicate with each other through a limited number of actions: by making requests for resources (GET), or by creating resources ( POST or PUT ), or even by deleting resources...
+Agents on the web communicate with each other through a limited number of actions: by making requests for resources (GET), by creating resources (POST or PUT), or even by deleting resources \ldots
 Creation or deletion of resources usually require authentication of the agent making the request, and so in many cases do requests for information (GET).
@@
 
-A \textit{WebID} is a URI that refers to an Agent - Person, Robot, Group or other thing that can have Intentions.
-The WebID should be a URI which when dereferenced returns a representation whose description uniquely identifies the Agent as the controller of a public key~\cite{sporny-m-2011--a}.
+A \textit{WebID} is a URI that refers to an agent - person, robot, group or other thing that can have intentions.
+The WebID should be a URI which when dereferenced returns a representation whose description uniquely identifies the agent as the controller of a public key~\cite{sporny-m-2011--a}.
 
@@
 \footnote{Server authentication using IETF DANE follows much the same logic, except that the lookup for the identity is not done using the HTTP protocol but DNSSEC.}.
-It is worth noting that the server serving the WebID profiles controls the identity of every agent whose URI is within that server's namespace.
-This service is known as the Origin Server~\cite{barth-a-2011--a}.
-It is the Origin of all resources served by it.
+It is worth noting that the host serving the WebID profiles controls the identity of every agent whose URI is within that server's namespace.
+This service is known as the origin server~\cite{barth-a-2011--a}.
+It is the origin of all resources served by it.
 
-We can easily think of the Origin Server as not only able to respond to requests, but also as an agent able to make requests.
-Indeed WebID authentication requires the server to make WebID Profile requests to other servers in order to verify the identity of agents making a request to it.
-The WebID spec describes this task as being accomplished by a separate agent, the WebID Verifier - which could indeed be done by another service on the web (WebID Proxy Authentication servers).
+We can easily think of the origin server as not only able to respond to requests, but also as an agent able to make requests.
+Indeed WebID authentication requires the server to make WebID profile requests to other servers in order to verify the identity of agents making a request to it.
+The WebID spec describes this task as being accomplished by a separate agent, the WebID verifier - which could indeed be done by another service on the web (WebID proxy authentication servers).
 But it can also be so closely tied to the web service that it would be natural to think of it as part of that same service.
-The WebID Profile furthermore could be served by the same agent as the one making the request, in which case we have a minimal case of a peer to peer communication.
-Note that fetching a WebID profile for WebID Authentication should be done anonymously, for fear of authentication deadlocks.
+The WebID profile furthermore could be served by the same agent as the one making the request, in which case we have a minimal case of a peer to peer communication.
+Note that fetching a WebID profile for WebID authentication should be done anonymously, for fear of authentication deadlocks.\todo{ST: why that? done -> allowed}
 

### 2012-07-28 paper.tex
streamline structure + more text

@@
 
+% this prints the current textwidth, so images can be
+% generated perfectly fitting to the page (LNCS textwidth: 121.99854 mm)
+%\uselengthunit{mm}\printlength{\textwidth}
+%\uselengthunit{mm}\printlength{\columnwidth}
+
 \section{Introduction}\label{sec:intro}
@@
 A \textit{WebID} is a URI that refers to an agent - person, robot, group or other thing that can have intentions.
-The WebID should be a URI which when dereferenced returns a representation whose description uniquely identifies the agent as the controller of a public key~\cite{sporny-m-2011--a}.
+The WebID should be a URI which when dereferenced returns a representation whose description uniquely identifies the agent as the controller of a public key~\cite{sporny-m-2011--a,story-h-2009--a}
 
@@
 
-Things get more interesting in the Authorization space.
+Things get more interesting in the authorization space.
 Consider a very natural application of WebID: allowing friends of one's friends (foaf) access to some resources.
-This authorization rule will require the Web Server to fetch each of its users' friends profiles, in order to build up such a list.
+This authorization rule will require the web server to fetch each of its users' friends profiles, in order to build up such a list.
 But there is a privacy issue involved here: not every one wants to make all of their social network (or even any of it) publicly visible.
-Those people may then protect their FOAF Profile with Access Control rules.
+Those people may then protect their FOAF profile with access control rules.
 How can a server that needs access to these FOAF profiles in order to apply its own access control rules get access to the information?
@@
 
-\section{Solution 1: Using each users WebID}
+The rest of the paper is organized in the following way:
+\autoref{sec:req} describes some more use-cases and additional requirements which we had in mind for our solution,
+\autoref{sec:spec} goes into detail with the WebID specification and adds support for authorization delegation,
+in \autoref{sec:eval} we describe our reference implementations based on two web applications and finally
+in \autoref{sec:relatedwork} we compare our proposal with two protocols, namely CORS and OAuth.
 
-\section{Solution 2: Acting on Behalf of a User}
+%\section{Terminology}
+%\textit{Access Delegation} is a relation between two WebID resources.
+%The relation describes, under which circumstances a secretary agent has access to a certain resource under the same constraints as the named agent.
+%The secretary agent declares to act in the name of the named agent.
 
-\section{Comparison with Other protocols}
-
-\section{OAuth}
-
-\section{CORS}
-
-% this prints the current textwidth, so images can be
-% generated perfectly fitting to the page (LNCS textwidth: 121.99854 mm)
-%\uselengthunit{mm}\printlength{\textwidth}
-%\uselengthunit{mm}\printlength{\columnwidth}
-
-\cite{story-h-2009--a}
-\cite{tramp-s-2012--a}
-
-%\begin{figure}[!t]
-%\centering
-%\includegraphics[width=2.5in]{myfigure}
-%\caption{Simulation Results}
-%\label{fig_sim}
-%\end{figure}
-
-\section{Terminology}
-
-\textit{Access Delegation} is a relation between two WebID resources.
-The relation describes, under which circumstances a secretary agent has access to a certain resource under the same constraints as the named agent.
-The secretary agent declares to act in the name of the named agent.
-
-\section{Requirements}
+\section{Requirements}\label{sec:req}
 
@@
 
-\subsection{Basic Use-Cases for Access Delegation}\label{sec:usecases}
+\subsection{Basic Use-Cases for Access Delegation} \label{sec:usecases}
 
-\paragraph{Personal Devices and Applications}
+\subsubsection{Personal Devices and Applications}
 
 Currently, the default usage intention for WebIDs are browser-based authentication scenarios.
-This is an important use-case and should be of special interest but we use the world wide web not only from our browsers but also from other applications and from other application on other devices such as smartphones, tablets and freedomboxes\footnote{\url{https://freedomboxfoundation.org/}}.
+This is an important use-case and should be of special interest but we use the World Wide Web not only from our browsers but also from other applications and from other application on other devices such as smartphones, tablets and freedomboxes\footnote{\url{https://freedomboxfoundation.org/}}.
 In a typical every day usage scenario, we use feed readers and social network clients hand in hand with web browsers.
-This is true esp.
-for mobile devices where specialized clients for social activities are widely in use and does exist even for academically driven social networks as the distributed Social Web \todo{A: req.
-explaining?
-(Web2.0 vs 3.0 ambiguity)} %Web2.0 or 3.0?
-the begining of the sentence talks about 2.0, and you end with FOAF (3.0)?
- based on FOAF WebIDs~\cite{tramp-s-2011--a}.
+All these applications have in common that they act in the name of its users and fetch and manipulate resources in a way that this could also be done by the user itself and with her browser.
+These applications provide their service to one user only and run on a device which can be accessed by one user only (e.g. a smartphone).
+This class of \textit{private applications} has more in common with the users browser and can be seen as an extension to the user itself~\cite{clark-a-1998-7-a}.
 
-All these applications have in common that they act in the name of its users and fetch and manipulate resources in a way that this could also be done by the user itself and with her browser.
+As slightly different we can identify the class of \textit{service applications}.
+These applications also manipulate resources in the name of the user but they do this not only for one but for many users.
+These services are hosted by a third party e.g. not by the user itself and not by the owner of the protected resource where our user has an interest in.
+In addition to that, we argue that the level of trust which is given by a user is lower than to an application which runs on a personal device and can be turned off by herself.
+A typical application domain for this class of applications is the Social Web more specifically the distributed and semantic Social Web, where multiple services create and manipulate artefacts like notes, comments and images and spin a data network based on a Linked Data infrastructure and shared vocabularies~\cite{tramp-s-2012--a}.
 
-We distinguish two different classes of applications here.
-(1) Applications which provide their service to one user only and run on a device which can be accessed by one user only (e.g. a smartphone).
-These applications have more in common with the users browser and can be seen as an extension to the user itself \cite{clark-a-1998-7-a}.
+\subsubsection{Vacation Replacement}
 
-In a WebID-enabled communication scenario, these devices use their own certificates for communication since we do not want to copy the browser certificate to these devices and we also do not want to save the passphrase on theses devices and services.
+In a typical office scenario, employees declare vacation replacements for the time of their holiday in order to achieve an uninterrupted service during that time.
+%One option to allow access to the vacation replacement user is to give him the original certificate or to add his private key to the users WebID.
+%This solution has two drawbacks: (1) the users certificate is burned after the vacation and she needs to create a new one, (2) a resource guard can not distinguish between the user and the vacation replacement user, which allows for abuse.
+%In this context, the named agent is the employee which is on holiday and her vacation replacement is the secretary agent.
 
-\todo{Sebastian Tramp: Extend it with respect to the Extended Mind paper}
+\subsubsection{Groups and Roles}
+Access for \textit{working groups} to a resource is typically specified in a way that each resource guard needs to maintain (owned or cached) a list of group members of this group.
+In the Social Semantic Web, these working groups have its own WebID resources which describe the group as an entity and its members as relations to their user WebIDs.
+To authorize a group of agents to access a resource should be as simple as to authorize a single agent.
 
-\paragraph{Vacation Replacement}
-
-In a typical office scenario, employees declare vacation replacements for the time of their holiday in order to achieve an uninterruptible service during that time.
-One option to allow access to this vacation replacement is to give him the original certificate or to add his private key to the users WebID.
-This solution has two drawbacks: (1) the users certificate is burned after the vacation and she needs to create a new one, (2) a resource guard can not distinguish between the user and the vacation replacement user, which allows for abuse.
-
-In this context, the named agent is the employee which is on holiday and her vacation replacement is the secretary agent.
-
-\paragraph{Working Groups}\label{sec:WorkingGroups}
-\todo{A: why 'working' and not just 'Groups'? (difference?)}
-Access for working groups to a resource is typically specified in a way that each resource guard \todo{A: is it really the guard who holds the list, or some access control sys?} needs to hold a list of group members of this group.
-In the Social Semantic Web \todo{A: see my prev.
-note about Web2.0 vs 3.0}, these working groups have its own WebID resources which describe the group as an entity and its members as relations to their user WebIDs.
-To authorize a group of agents to access a resource should be as simple as to a single agent.
-In order to allow this, we define the group as the named agent and all group members as its secretary agents.
-
-An alternative could be to share one single group certificate with all members or to create a group certificate for each member and describe all public keys in the group WebID.
-Again, these solutions have different drawbacks: (1) a shared certificate needs to be updated each time a user leaves the group, (2) multiple group certificates for each user does not allow for distinguishing which user accessed the resource, which allows for abuse.
-
-In this context, the group is the named agent and all current group members are secretary agents.\todo{A: not sure I agree (see source)}%the group is not an entity, therefore it cannot take actions by iteself.
+%In order to allow this, we define the group as the named agent and all group members as its secretary agents.
+%An alternative could be to share one single group certificate with all members or to create a group certificate for each member and describe all public keys in the group WebID.
+%Again, these solutions have different drawbacks: (1) a shared certificate needs to be updated each time a user leaves the group, (2) multiple group certificates for each user does not allow for distinguishing which user accessed the resource, which allows for abuse.
+%In this context, the group is the named agent and all current group members are secretary agents.\todo{A: not sure I agree (see source)}%the group is not an entity, therefore it cannot take actions by iteself.
 Actions are always performed by users, as part of the group.
 
-\paragraph{Office Roles}
-An office role is a construct where a user can access specific resources because of his working description.
+An \textit{office role} is a construct where a user can access specific resources because of his working description.
 A product manager has access to all product related resources because of her role as product manager and not because of her identity.
@@
 
-In this context, the role is the named agent and the current role owner is the secretary agent.
+%In this context, the role is the named agent and the current role owner is the secretary agent.
 
-\subsection{Implementation Requirements}\label{sec:req}
+\subsection{Implementation Requirements}
 
@@
 
-\paragraph{Distinguish secretary agents from named agents}
+\subsubsection{Distinguish secretary agents from named agents}
 Delegation should not be handled by camouflaging an request of an agent in the sense that this request is indistinguishable from a named agent request.
@@
 
-\paragraph{Easy to use}
+\subsubsection{Easy to use}
 The one and only place to describe which secretary agents are allowed to operate as a named agent should be the WebID profile itself.
@@
 
-\paragraph{Linked Data and Read Write Web integration}
+\subsubsection{Linked Data and Read Write Web integration}
 
@@
 
-\paragraph{Minimal protocol footprint}
+\subsubsection{Minimal protocol footprint}
 
@@
 
-\paragraph{No enforcement to reveal agent identities}\todo{maybe we kick this ...}
+\subsubsection{No enforcement to reveal agent identities}\todo{maybe we kick this ...}
 
@@
 
-\section{Specification of the WebID protocol extension}\label{sec:spec}
+\section{Extending WebID for Access Delegation}\label{sec:spec}
+
+\textit{Solution 1: Using each users WebID} vs.
+\textit{Solution 2: Acting on Behalf of a User}
 
@@
 
+\section{Evaluation}\label{sec:eval}
+
+\todo{Andrei Sambra: MyProfile description}
+
 \section{Related Work}\label{sec:relatedwork}
@@
 \subsection{OAuth}
-\todo{Andrei Sambra: Compare to oAuth}
 \todo{If we were to implement a secreteary like feature using OAuth what would it look like? what would the differences be?}
@@
 
-\section{Evaluation}\label{sec:eval}
-
-\todo{Andrei Sambra: MyProfile description}
-
 \bibliographystyle{plain}

### 2012-07-31 paper.tex
add abstract

@@
 \begin{abstract}
-We propose \ldots
+The WebID protocol enables the global identification of agents in a distributed manner by employing cryptography and Linked Data principles.
+It is used currently mostly in scenarios where a client wants to access some protected resources on a server.
+In order to decide whether access should be granted, the server itself needs to make requests to other servers and retrieve WebID profiles, which contain relationship definitions between agents.
+Currenlty those information needs to be publicly available, which leads to an privacy issue, since agents may want to hide such information from the general audience.
+In this paper we propose an extension of the WebID protocol, which allows the delegation of access from a WebID to a third party, e.g. a server application.
+We describe further use-cases that led to the development of this extension and we discuss the delegation protocol with two reference implementations.
 \end{abstract}

### 2012-07-31 paper.tex
update abstract

--- 2012-07-28 paper.tex
@@
 unicode=true,
-pdfauthor={Sebastian Tramp, Henry Story, Andrei Sambra, Philipp Frischmut, Timofey Ermilov, and S\"oren Auer},
+pdfauthor={Sebastian Tramp, Henry Story, Andrei Sambra, Philipp Frischmut, Michael Martin, and S\"oren Auer},
 pdftitle={Extending the WebID Protocol with Access Delegation},
@@
 
-\author{Sebastian Tramp\inst{1} \and Henry Story\inst{2} \and Andrei Sambra\inst{3} \and Philipp Frischmuth\inst{1} \and Timofey Ermilov\inst{1} \and S\"oren Auer\inst{1}}
+\author{Sebastian Tramp\inst{1} \and Henry Story\inst{2} \and Andrei Sambra\inst{3} \and Philipp Frischmuth\inst{1} \and Michael Martin\inst{1} \and S\"oren Auer\inst{1}}
 
@@
 \begin{abstract}
-We propose \ldots
+The WebID protocol enables the global identification of agents in a distributed manner by employing asymmetric cryptography and Linked Data principles.
+WebIDs are mostly used in scenarios where a user utilize a browser application to access a protected resource on a web server.
+In order to decide whether access should be granted or denied, the web server itself needs to retrieve other WebID profiles and resources which contain relationship information between agents and other related information.
+%Currently, those information needs to be publicly available, which leads to an privacy issue, since agents may want to hide such information from the general audience.
+In this paper we propose an extension to the WebID protocol which allows for delegation of access authorization from a WebID to a third party, e.g. a server application.
+This extends the range of application scenarios where WebID authentication can be deployed to all kinds of server to server resource consumption scenarios and other use cases.  
 \end{abstract}

### 2012-08-02 paper.tex
upgrade requirements description

@@
 In this paper we propose an extension to the WebID protocol which allows for delegation of access authorization from a WebID to a third party, e.g. a server application.
-This extends the range of application scenarios where WebID authentication can be deployed to all kinds of server to server resource consumption scenarios and other use cases.  
+This extends the range of application scenarios where WebID authentication can be efficiently deployed to all kinds of server to server resource consumption scenarios and other use cases.  
 \end{abstract}
@@
 The rest of the paper is organized in the following way:
-\autoref{sec:req} describes some more use-cases and additional requirements which we had in mind for our solution,
+\autoref{sec:req} describes the usage scenario and additional requirements which we had in mind for our solution,
 \autoref{sec:spec} goes into detail with the WebID specification and adds support for authorization delegation,
@@
 
-This sections lists the most crucial use-cases which require access delegation and which can not be solved with the standard WebID authentication protocol.
+This section describe the usage scenario which require an access delegation which can not be solved efficiently with the standard WebID authentication protocol.
 In addition to that, we list derived implementation requirements.
 
-\subsection{Basic Use-Cases for Access Delegation} \label{sec:usecases}
+%\subsection{Basic Use-Cases for Access Delegation} \label{sec:usecases}
 
-\subsubsection{Personal Devices and Applications}
+%\subsubsection{Personal Devices and Applications}
 
@@
 In a typical every day usage scenario, we use feed readers and social network clients hand in hand with web browsers.
-All these applications have in common that they act in the name of its users and fetch and manipulate resources in a way that this could also be done by the user itself and with her browser.
-These applications provide their service to one user only and run on a device which can be accessed by one user only (e.g. a smartphone).
+All these applications have in common, that they act in the name of its users and fetch and manipulate resources in a way that this could also be done by the user itself and with her browser.
+These applications provide their service to one single user only and run on a device which can be accessed by one user only (e.g. a smartphone).
 This class of \textit{private applications} has more in common with the users browser and can be seen as an extension to the user itself~\cite{clark-a-1998-7-a}.
 
-As slightly different we can identify the class of \textit{service applications}.
+As slightly different, we can identify the class of \textit{service applications}.
 These applications also manipulate resources in the name of the user but they do this not only for one but for many users.
@@
 In addition to that, we argue that the level of trust which is given by a user is lower than to an application which runs on a personal device and can be turned off by herself.
-A typical application domain for this class of applications is the Social Web more specifically the distributed and semantic Social Web, where multiple services create and manipulate artefacts like notes, comments and images and spin a data network based on a Linked Data infrastructure and shared vocabularies~\cite{tramp-s-2012--a}.
+A typical application domain for this class of applications is the Social Web, more specifically, the distributed and semantic Social Web.
+In this infrastructure multiple services such as foto sharing, recipe management or todo lists create and manipulate artefacts like notes, comments and images and spin a data network based on a Linked Data infrastructure and shared vocabularies~\cite{tramp-s-2012--a}.
 
-\subsubsection{Vacation Replacement}
+We will show, that this class of service applications can not handle access delegation efficiently without an extension to the protocol such as we propose
 
-In a typical office scenario, employees declare vacation replacements for the time of their holiday in order to achieve an uninterrupted service during that time.
+%\subsubsection{Vacation Replacement}
+
+%I a typical office scenario, employees declare vacation replacements for the time of their holiday in order to achieve an uninterrupted service during that time.
+
 %One option to allow access to the vacation replacement user is to give him the original certificate or to add his private key to the users WebID.
@@
 
-\subsubsection{Groups and Roles}
-Access for \textit{working groups} to a resource is typically specified in a way that each resource guard needs to maintain (owned or cached) a list of group members of this group.
-In the Social Semantic Web, these working groups have its own WebID resources which describe the group as an entity and its members as relations to their user WebIDs.
-To authorize a group of agents to access a resource should be as simple as to authorize a single agent.
+%\subsubsection{Groups and Roles}
+
+%Access for \textit{working groups} to a resource is typically specified in a way that each resource guard needs to maintain an owned or cached list of group members of this group.
+%In the Social Semantic Web, these working groups have its own WebID resources which describe the group as an entity and its members as relations to their user WebIDs.
+%To authorize a group of agents to access a resource should be as simple as to authorize a single agent.
 
@@
 
-An \textit{office role} is a construct where a user can access specific resources because of his working description.
-A product manager has access to all product related resources because of her role as product manager and not because of her identity.
-The role itself is identified by WebID and all access authorization rules should use this role WebID instead of a user WebID.
+%An \textit{office role} is a slightly different construct where a user can access specific resources because of his working description.
+%A product manager has access to all product related resources because of her role as product manager and not because of her identity.
+%The role itself is identified by a WebID and all access authorization rules should use this WebID instead of a user WebID.
 
@@
 
-\subsection{Implementation Requirements}
+%\subsection{Implementation Requirements}
 
-Based on the given use-cases from \autoref{sec:usecases} and additional preliminary considerations, we issued the following implementation relevant requirements for an access delegation solution based on the WebID authentication protocol.
+Based on this usage scenario and additional preliminary considerations, we issue the following implementation relevant requirements for an access delegation solution based on the WebID authentication protocol.
+We have identified the following roles being part of the access delegation process:
+\begin{enumerate}
+    \item The \textit{secretary agent} is the agent which acts in the name of another agent.
+This agent actually requests some resources and tries to do that on behalf of someone.
+    \item The \textit{named agent} is the agent which is represented by the secretary.
+This agent does not have an active role in the request but is named as the origin of the activity.
+\end{enumerate}
+In the following requirements list, we use both terms consequently to avoid confusion.
 
@@
 
-\subsubsection{No enforcement to reveal agent identities}\todo{maybe we kick this ...}
+%\subsubsection{No enforcement to reveal agent identities}\todo{maybe we kick this ...}
 

### 2012-08-02 paper.tex
Added description for MyProfile case.

--- 2012-07-31 paper.tex
@@
 
-\todo{Andrei Sambra: MyProfile description}
+\subsection{MyProfile description}
+MyProfile intends to provide a solution for managing the numerous accounts and profiles that users have on the Internet.
+Its main purpose is to provide a unified user account, or simply \textit{user profile}, which as opposed to current \textit{silo} profiles, would really be under the user's control, on a device located within the user physical reach.
+
+In the case of MyProfile, it is very important to be able to offer WebID access delegation, because a single MyProfile server instance can host multiple users.
+To improve user experience and overall performance, a caching mechanism is used to refresh local copies or "views" of external data.
+Due to multiple users coexisting on the same server, the caching mechanism needs to be able to differentiate between views belonging to each user, according to their specific access control policies configured on external resource providers.
+
+Let's take for example the following case: Ann and Barry are both local users on a single MyProfile server.
+Charley is an external user with access control policies set up on his private server.
+When Ann requests to view Charley's profile data, a personalized view of the profile is displayed, corresponding to access control policies for Ann.
+When Barry requests to view Charley's profile, different profile data is displayed, since there are different access control policies for Barry.
+At this point, the caching mechanism needs to be able to cache two different profile views, each corresponding to access control policies specific for the user requesting the data.
+For this reason, the caching mechanism is required to act as a service agent, identifying itself as well as conveying the identity of the user on  behalf of whom the agent is requesting data.
 
@@
 
+%A fix for cases where there is little trust in a secretary, or when bootstrapping a user's server.
+The resource provider can store the request from consumer, and send a pingback to the consumer service, to notify him/her of a pending authorization request from consumer.
+Then the user will have to authenticate personally (through the browser, in order to verify the private key) to the provider, check a list of pending requests for his/her WebID, and decide if the request in question is valid or not.
+In other words, the user must give his/her consent if the secretary's identity is unknown to the provider.
+
 \subsection{Cross Origin Resource Sharing (CORS)}

### 2012-08-02 paper.tex
Modified a bit the Requirements section, to make it more explicit.

@@
 
-This section describe the usage scenario which require an access delegation which can not be solved efficiently with the standard WebID authentication protocol.
+This section describes several usage scenarios requiring access delegation which can not be solved efficiently with the standard WebID authentication protocol.
 In addition to that, we list derived implementation requirements.
@@
 
-Currently, the default usage intention for WebIDs are browser-based authentication scenarios.
-This is an important use-case and should be of special interest but we use the World Wide Web not only from our browsers but also from other applications and from other application on other devices such as smartphones, tablets and freedomboxes\footnote{\url{https://freedomboxfoundation.org/}}.
+Currently, the default usage intention for WebIDs consists of browser-based authentication scenarios.
+This is an important use-case and should be of special interest since we use the World Wide Web not only through browsers but also through other applications as well as other application on other devices such as smartphones, tablets and freedomboxes\footnote{\url{https://freedomboxfoundation.org/}}.
 In a typical every day usage scenario, we use feed readers and social network clients hand in hand with web browsers.
-All these applications have in common, that they act in the name of its users and fetch and manipulate resources in a way that this could also be done by the user itself and with her browser.
-These applications provide their service to one single user only and run on a device which can be accessed by one user only (e.g. a smartphone).
-This class of \textit{private applications} has more in common with the users browser and can be seen as an extension to the user itself~\cite{clark-a-1998-7-a}.
+All these applications act in the name of their users and fetch and manipulate resources in a way as if it were done by the users themselves and with her browser.
+These applications provide their services to one user only and also run on a device which is commonly accessed by one user only (e.g. a smartphone).
+This class of \textit{private applications} is similar to browsers and can be seen as an extension to the user itself~\cite{clark-a-1998-7-a}.
 
-As slightly different, we can identify the class of \textit{service applications}.
-These applications also manipulate resources in the name of the user but they do this not only for one but for many users.
-These services are hosted by a third party e.g. not by the user itself and not by the owner of the protected resource where our user has an interest in.
+As a slightly different case, we can identify the class of \textit{service applications}.
+These applications also manipulate resources in the name of the user but they do this for more than one user.
+These services are hosted by a third party e.g. not by the user itself, nor by the owner of the protected resource where our user has an interest in.
 In addition to that, we argue that the level of trust which is given by a user is lower than to an application which runs on a personal device and can be turned off by herself.
-A typical application domain for this class of applications is the Social Web, more specifically, the distributed and semantic Social Web.
-In this infrastructure multiple services such as foto sharing, recipe management or todo lists create and manipulate artefacts like notes, comments and images and spin a data network based on a Linked Data infrastructure and shared vocabularies~\cite{tramp-s-2012--a}.
+A typical application domain for this class of applications is the Social Web, and more specifically, the distributed and semantic Social Web.
+In this infrastructure, multiple services such as photo sharing, recipe management or todo lists create and manipulate artefacts like notes, comments and images and spin a data network based on a Linked Data infrastructure and shared vocabularies~\cite{tramp-s-2012--a}.
 
-We will show, that this class of service applications can not handle access delegation efficiently without an extension to the protocol such as we propose
+In this paper will show that this class of service applications can not handle access delegation efficiently without an extension to the protocol such as the one we propose.
 

### 2012-08-02 paper.tex
added 3 step secretary relation part

--- 2012-08-02 paper.tex
@@
 \begin{abstract}
-The WebID protocol enables the global identification of agents in a distributed manner by employing asymmetric cryptography and Linked Data principles.
+The WebID protocol enables the global identification of agents in a distributed manner by combining asymmetric cryptography and Linked Data.
 WebIDs are mostly used in scenarios where a user utilize a browser application to access a protected resource on a web server.
-In order to decide whether access should be granted or denied, the web server itself needs to retrieve other WebID profiles and resources which contain relationship information between agents and other related information.
-%Currently, those information needs to be publicly available, which leads to an privacy issue, since agents may want to hide such information from the general audience.
-In this paper we propose an extension to the WebID protocol which allows for delegation of access authorization from a WebID to a third party, e.g. a server application.
-This extends the range of application scenarios where WebID authentication can be efficiently deployed to all kinds of server to server resource consumption scenarios and other use cases.  
+But in order to decide whether access should be granted or denied, the web server itself needs to retrieve other WebID profiles and linked resources in order to work out if the requesting agent is part of the authorization group ( eg: is a friends of a friend of the resource owner ).
+It would seem that at present this information needs to be publicly available for the server to access it.
+This  leads to a privacy issue, since agents may want to limit access to a users social graph.
+In this paper we propose an extension to the WebID protocol which allows for delegation of access authorization from a WebID to a third party, e.g.
+allowing a server to be able to act on behalf of its users.
+This extends the range of application scenarios where WebID authentication can be efficiently deployed while increasing privacy.
 \end{abstract}
@@
 The WebID profile furthermore could be served by the same agent as the one making the request, in which case we have a minimal case of a peer to peer communication.
-Note that fetching a WebID profile for WebID authentication should be done anonymously, for fear of authentication deadlocks.\todo{ST: why that? done -> allowed}
+Note that fetching a WebID profile for WebID authentication should be done anonymously, for fear of authentication deadlocks.\footnote{ for example one can imagine an agent S  with profile Ps requesting a resource on server R which requires authentication.
+S would send R its certificate, thereby requiring  R to dereference S's Profile Ps in order to verify the WebID.
+If Ps  itself requires authentiction of R and if R sends a certificate containing a WebID with its profile Pr, and if Pr itself requires authentication then it looks like we have a deadlock.
+}
 
@@
 This authorization rule will require the web server to fetch each of its users' friends profiles, in order to build up such a list.
-But there is a privacy issue involved here: not every one wants to make all of their social network (or even any of it) publicly visible.
+But there is a privacy issue involved here: not every one wants to make all of their social network publically visible, and some may not want to make any of it publicly visible.
 Those people may then protect their FOAF profile with access control rules.
-How can a server that needs access to these FOAF profiles in order to apply its own access control rules get access to the information?
+How can a server that needs access to these FOAF profiles in order to apply its own access control rules - such as only allowing access to foaf - get access to the information?
 Should it be able to do so?
@@
 
-\textit{Solution 1: Using each users WebID} vs.
-\textit{Solution 2: Acting on Behalf of a User}
+\textit{Solution 1: Passing itself for the user}
+
+   The simplest solution for any agent S wishing to pass itself off as one of the users U, is for it to create a public/private key pair,  place the public key in a certificate Cu and add the public key to the Users' Profile Pu.
+Having done this the agent S can then connect using the certificate Cu to any service it wishes to, when it wants to work for the user U.
+This has the advantage of requiring no change to the WebID protocol.
+It does give the agent S all powers of the user U and so has to be handled with great care.
+
+  What kind of agents does it make sense to give such rights to?
+Or put another way: what agent would giving such rights to not constitute a reduction in security to the user?
+Or put yet another way: which agent could take such a role at its behest at any moment in any case?
+Or: which agent does the user and the authorization server already rely on for authentication?
+There is one agent  on which any service requiring WebID authentication relies on and this is the WebID Profile Origin Server \footnote{see http://tools.ietf.org/html/rfc6454}.
+Any server requiring authentication of an agent using WebID must trust the origin server serving the WebID Profile.
+That origin server can at any time change the public keys in the profiles sent back to any authorization agents and indeed change any information in the profile it wants to.
+Any user profile can then be thought of as being a user according to the Origin Server ie a user@origin.org:port - where origin.org is the domain of the origin server, and 'port' is the port the server is running on.
+
+  When the user owns the origin server then the origin server is just an extension of the user, and in that case there need be no thought of a difference between the user and the origin server.
+In that case the origin server can in fact just authenticate as the user whenever needed.
+
+  But when the origin server (OS) is serving a number of different profiles and is acting on behalf of a number of different users, then we have an efficiency issue that rears its head.
+Whenever the Origin Server needs to act on behalf of one ifs users to a remote server R it will need to open a new TLS connection to that server using one of its users public keys.
+For N users this could require N parallel connections to a server S.
+
+\todo{calculate how inefficient this is, and at what size of network this starts really become problematic}
+
+\textit{Solution 2: Origin Server acting on Behalf of a User}
+
+  In order to reduce the number of open connections to any server down to a minimum, it would be useful if the Origin Server could identify itself directly when making a request and specify on behalf of which of its users it was acting on.
+One way would be for the Origin Server acting as client to simply use the same public key as the Origin Server acting as server - that is it could use the same public key as the one used by the TLS server.
+It could even use the same certificate. 
+This would make clear to any server it was connecting to, that it could rely on this server as much as it could on the identity of any user served by that server.
+
+Still, such a server connecting to a remote service on behalf of one of its users would then need to identify which user it was acting on behalf of, or the remote service receiving a request would not know which access control rule to apply to the origin server.
+
+After all the remote service may have resources which should be readable by the Origin Server users OSu1 and OSu2, but not to the Origin Server users OSu3 and OSu4.
+Or the representations returned may differ somewhat for each group of users.
+OSu1 and OSu2 may get some more information than OSu1 and OSu2.
+As a result it is important for the Origin Server to distinguish on Behalf of which users it is acting when making a request.
+
+Problems: using the same key between server acting as client and as server risks making the keys available to a wider audience, and so increases the risk of key compromise.
+
+\todo{insert description of On-behalf-Of header}
+
+\textit{Solution3: Secretary acting on Behalf of a User}
+
+The origin server acting  as a client on behalf of a user can then be thought of as a keep of secrets for that user. 
+It should know how to distinguish what remote servers tell it when it is acting on behalf of one user, from what a remote server tells it when it is acting on behalf of another user.
+The role of the keeper of secrets for a person is known as the secretary role - a prestigious role taken on for example by figures such as the Secretary of State, Hillary Clinton.
+
+If we now identify the secretary that can act on behalf of a user we can generalise the protocol somewhat.
+When the server authenticates as a secretary to a remote server it can use its own WebID.
+But how would the remote server know that it can trust that secretary to be acting on behalf of a particular user?
+It can no longer just compare the TLS keys.
+Insterad it can see if the user that the secretary is acting on behalf of has stated clearly that that agent is its secretary.
+This can be discovered by checking out the profile...
+\todo{fill out the details here}
 
@@
 
-\subsection{MyProfile description}
-MyProfile intends to provide a solution for managing the numerous accounts and profiles that users have on the Internet.
-Its main purpose is to provide a unified user account, or simply \textit{user profile}, which as opposed to current \textit{silo} profiles, would really be under the user's control, on a device located within the user physical reach.
-
-In the case of MyProfile, it is very important to be able to offer WebID access delegation, because a single MyProfile server instance can host multiple users.
-To improve user experience and overall performance, a caching mechanism is used to refresh local copies or "views" of external data.
-Due to multiple users coexisting on the same server, the caching mechanism needs to be able to differentiate between views belonging to each user, according to their specific access control policies configured on external resource providers.
-
-Let's take for example the following case: Ann and Barry are both local users on a single MyProfile server.
-Charley is an external user with access control policies set up on his private server.
-When Ann requests to view Charley's profile data, a personalized view of the profile is displayed, corresponding to access control policies for Ann.
-When Barry requests to view Charley's profile, different profile data is displayed, since there are different access control policies for Barry.
-At this point, the caching mechanism needs to be able to cache two different profile views, each corresponding to access control policies specific for the user requesting the data.
-For this reason, the caching mechanism is required to act as a service agent, identifying itself as well as conveying the identity of the user on  behalf of whom the agent is requesting data.
+\todo{Andrei Sambra: MyProfile description}
 
@@
 
-%A fix for cases where there is little trust in a secretary, or when bootstrapping a user's server.
-The resource provider can store the request from consumer, and send a pingback to the consumer service, to notify him/her of a pending authorization request from consumer.
-Then the user will have to authenticate personally (through the browser, in order to verify the private key) to the provider, check a list of pending requests for his/her WebID, and decide if the request in question is valid or not.
-In other words, the user must give his/her consent if the secretary's identity is unknown to the provider.
-
 \subsection{Cross Origin Resource Sharing (CORS)}

### 2012-08-03 paper.tex
niceup solution description

@@
 
+\todo{ST: add efficency requirement}
 %\subsubsection{No enforcement to reveal agent identities}\todo{maybe we kick this ...}
@@
 
-\textit{Solution 1: Passing itself for the user}
+\subsection{Solution 1: Passing itself for the user}
 
-   The simplest solution for any agent S wishing to pass itself off as one of the users U, is for it to create a public/private key pair,  place the public key in a certificate Cu and add the public key to the Users' Profile Pu.
-Having done this the agent S can then connect using the certificate Cu to any service it wishes to, when it wants to work for the user U.
+The simplest solution for any agent $S$ wishing to pass itself off as one of the users $U$, is for it to create a public / private key pair,  place the public key in a certificate $C_u$ and add the public key to the users' profile $P_u$.
+Having done this the agent $S$ can then connect using the certificate $C_u$ to any service it wishes to, when it wants to work for the user $U$.
 This has the advantage of requiring no change to the WebID protocol.
-It does give the agent S all powers of the user U and so has to be handled with great care.
+It does give the agent $S$ all powers of the user $U$ and so has to be handled with great care.
 
@@
 Or: which agent does the user and the authorization server already rely on for authentication?
-There is one agent  on which any service requiring WebID authentication relies on and this is the WebID Profile Origin Server \footnote{see http://tools.ietf.org/html/rfc6454}.
+There is one agent  on which any service requiring WebID authentication relies on and this is the WebID profile origin server~\cite{barth-a-2011--a}.
 Any server requiring authentication of an agent using WebID must trust the origin server serving the WebID Profile.
 That origin server can at any time change the public keys in the profiles sent back to any authorization agents and indeed change any information in the profile it wants to.
-Any user profile can then be thought of as being a user according to the Origin Server ie a user@origin.org:port - where origin.org is the domain of the origin server, and 'port' is the port the server is running on.
+Any user profile can then be thought of as being a user according to the origin server ie a \url{user@origin.org:port} - where \url{origin.org} is the domain of the origin server, and \url{port} is the port the server is running on.
 
@@
 But when the origin server (OS) is serving a number of different profiles and is acting on behalf of a number of different users, then we have an efficiency issue that rears its head.
-Whenever the Origin Server needs to act on behalf of one ifs users to a remote server R it will need to open a new TLS connection to that server using one of its users public keys.
-For N users this could require N parallel connections to a server S.
+Whenever the Origin Server needs to act on behalf of one ifs users to a remote server $R$ it will need to open a new TLS connection to that server using one of its users public keys.
+For $N$ users this could require $N$ parallel connections to a server $S$.
+\todo{calculate how inefficient this is, and at what size of network this starts really become problematic}
+\todo{ST: add disadvantages according to the requirements (identity)}
 
-\todo{calculate how inefficient this is, and at what size of network this starts really become problematic}
+\subsection{Solution 2: Origin Server acting on Behalf of a User}
 
-\textit{Solution 2: Origin Server acting on Behalf of a User}
-
-  In order to reduce the number of open connections to any server down to a minimum, it would be useful if the Origin Server could identify itself directly when making a request and specify on behalf of which of its users it was acting on.
-One way would be for the Origin Server acting as client to simply use the same public key as the Origin Server acting as server - that is it could use the same public key as the one used by the TLS server.
+In order to reduce the number of open connections to any server down to a minimum, it would be useful if the origin server could identify itself directly when making a request and specify on behalf of which of its users it was acting on.
+One way would be for the origin server acting as client to simply use the same public key as the origin server acting as server - that is it could use the same public key as the one used by the TLS server.
 It could even use the same certificate.
@@
 
-After all the remote service may have resources which should be readable by the Origin Server users OSu1 and OSu2, but not to the Origin Server users OSu3 and OSu4.
+After all the remote service may have resources which should be readable by the origin server users $OS_{u1}$ and $OS_{u2}$, but not to the origin server users $OS_{u3}$ and $OS_{u4}$.
 Or the representations returned may differ somewhat for each group of users.
-OSu1 and OSu2 may get some more information than OSu1 and OSu2.
-As a result it is important for the Origin Server to distinguish on Behalf of which users it is acting when making a request.
+$OS_{u1}$ and $OS_{u2}$ may get some more information than $OS_{u1}$ and $OS_{u2}$.
+As a result it is important for the origin server to distinguish on behalf of which users it is acting when making a request.
 
@@
 
-\todo{insert description of On-behalf-Of header}
+\todo{insert description of On-behalf-Of header (at least the importance of such a feature)}
 
-\textit{Solution3: Secretary acting on Behalf of a User}
+\subsection{Solution 3: Secretary acting on Behalf of a User}
 
@@
 It can no longer just compare the TLS keys.
-Insterad it can see if the user that the secretary is acting on behalf of has stated clearly that that agent is its secretary.
-This can be discovered by checking out the profile...
-\todo{fill out the details here}
+Instead it can see if the user that the secretary is acting on behalf of has stated clearly that that agent is its secretary.
+This can be discovered by checking out the profile... \todo{fill out the details here}
 

### 2012-08-03 paper.tex
upgrade evaluation section

@@
 
-\subsection{MyProfile description}
-MyProfile intends to provide a solution for managing the numerous accounts and profiles that users have on the Internet.
+As two real-world examples we describe two different implementations where WebID delegation is deployed and needed.
+MyProfile is WebID profile service application and OntoWiki a semantic data wiki.
+
+\subsection{MyProfile}
+MyProfile intends to provide a solution for managing the numerous accounts and profiles that users have on the Web.
 Its main purpose is to provide a unified user account, or simply \textit{user profile}, which as opposed to current \textit{silo} profiles, would really be under the user's control, on a device located within the user physical reach.
+
+\begin{figure*}[htb]
+  \centering
+  \includegraphics[width=\textwidth]{AuthSequence}
+  \caption{The MyProfile dashboard visualizes information from different sources fetched by the MyProfile server as a secretary of its user}
+  \label{fig:MyProfile}
+\end{figure*}
 
@@
 
-Let's take for example the following case: Ann and Barry are both local users on a single MyProfile server.
+Let's take for example the following case:
+Ann and Barry are both local users on a single MyProfile server.
 Charley is an external user with access control policies set up on his private server.
@@
 For this reason, the caching mechanism is required to act as a service agent, identifying itself as well as conveying the identity of the user on  behalf of whom the agent is requesting data.
+
+\subsection{OntoWiki}
+\todo{Phil: Add OntoWiki general description, the usecases for webid delegation as well as a demonstrating screenshot here}
 

### 2012-08-03 paper.tex
fix some bib and list issues

@@
 \lstinputlisting[
-    lastline=12,name=webid,style=turtle,float=htb,label=listing:webid1,
+    lastline=13,name=webid,style=turtle,float=htb,label=listing:webid1,
     basicstyle=\ttfamily\scriptsize,
-    caption={Minimal WebID profile including a public key}
+    caption={Minimal WebID profile including a public key and a secretary relation}
 ]{Listings/webid1.ttl}
 
-\lstinputlisting[
-    firstnumber=last,firstline=13,name=webid,style=turtle,float=htb,label=listing:webiddelegation,
-    basicstyle=\ttfamily\scriptsize,
-    caption={Access delegation by explicitly and implicitly identifying agents or application},
-    label={list:sec_relation},
-]{Listings/webid1.ttl}
+%\lstinputlisting[
+    %firstnumber=last,firstline=13,name=webid,style=turtle,float=htb,label=listing:webiddelegation,
+    %basicstyle=\ttfamily\scriptsize,
+    %caption={Access delegation by explicitly and implicitly identifying agents or application},
+    %label={list:sec_relation},
+%]{Listings/webid1.ttl}\todo{A:why add the public key of the agent here? (revocation issues)}
 
@@
     caption={Schema description of the delegation property},
-]{Listings/schema.ttl}\todo{A:why add the public key of the agent here? (revocation issues)}
+]{Listings/schema.ttl}
 
-\section{Evaluation}\label{sec:eval}
+\section{Implementation and Evaluation}\label{sec:eval}
 
@@
 
+\section{Conclusion and Future Work}
+
 \bibliographystyle{plain}

### 2012-08-03 paper.tex
Added a screenshot for MyProfile.

--- 2012-08-03 paper.tex
@@
 
-\todo{ST: add efficency requirement}
 %\subsubsection{No enforcement to reveal agent identities}\todo{maybe we kick this ...}
@@
 
-\subsection{Solution 1: Passing itself for the user}
+\textit{Solution 1: Passing itself for the user}
 
-The simplest solution for any agent $S$ wishing to pass itself off as one of the users $U$, is for it to create a public / private key pair,  place the public key in a certificate $C_u$ and add the public key to the users' profile $P_u$.
-Having done this the agent $S$ can then connect using the certificate $C_u$ to any service it wishes to, when it wants to work for the user $U$.
+   The simplest solution for any agent S wishing to pass itself off as one of the users U, is for it to create a public/private key pair,  place the public key in a certificate Cu and add the public key to the Users' Profile Pu.
+Having done this the agent S can then connect using the certificate Cu to any service it wishes to, when it wants to work for the user U.
 This has the advantage of requiring no change to the WebID protocol.
-It does give the agent $S$ all powers of the user $U$ and so has to be handled with great care.
+It does give the agent S all powers of the user U and so has to be handled with great care.
 
@@
 Or: which agent does the user and the authorization server already rely on for authentication?
-There is one agent  on which any service requiring WebID authentication relies on and this is the WebID profile origin server~\cite{barth-a-2011--a}.
+There is one agent  on which any service requiring WebID authentication relies on and this is the WebID Profile Origin Server \footnote{see http://tools.ietf.org/html/rfc6454}.
 Any server requiring authentication of an agent using WebID must trust the origin server serving the WebID Profile.
 That origin server can at any time change the public keys in the profiles sent back to any authorization agents and indeed change any information in the profile it wants to.
-Any user profile can then be thought of as being a user according to the origin server ie a \url{user@origin.org:port} - where \url{origin.org} is the domain of the origin server, and \url{port} is the port the server is running on.
+Any user profile can then be thought of as being a user according to the Origin Server ie a user@origin.org:port - where origin.org is the domain of the origin server, and 'port' is the port the server is running on.
 
@@
   But when the origin server (OS) is serving a number of different profiles and is acting on behalf of a number of different users, then we have an efficiency issue that rears its head.
-Whenever the Origin Server needs to act on behalf of one ifs users to a remote server $R$ it will need to open a new TLS connection to that server using one of its users public keys.
-For $N$ users this could require $N$ parallel connections to a server $S$.
+Whenever the Origin Server needs to act on behalf of one ifs users to a remote server R it will need to open a new TLS connection to that server using one of its users public keys.
+For N users this could require N parallel connections to a server S.
+
 \todo{calculate how inefficient this is, and at what size of network this starts really become problematic}
-\todo{ST: add disadvantages according to the requirements (identity)}
 
-\subsection{Solution 2: Origin Server acting on Behalf of a User}
+\textit{Solution 2: Origin Server acting on Behalf of a User}
 
-In order to reduce the number of open connections to any server down to a minimum, it would be useful if the origin server could identify itself directly when making a request and specify on behalf of which of its users it was acting on.
-One way would be for the origin server acting as client to simply use the same public key as the origin server acting as server - that is it could use the same public key as the one used by the TLS server.
+  In order to reduce the number of open connections to any server down to a minimum, it would be useful if the Origin Server could identify itself directly when making a request and specify on behalf of which of its users it was acting on.
+One way would be for the Origin Server acting as client to simply use the same public key as the Origin Server acting as server - that is it could use the same public key as the one used by the TLS server.
 It could even use the same certificate. 
@@
 
-After all the remote service may have resources which should be readable by the origin server users $OS_{u1}$ and $OS_{u2}$, but not to the origin server users $OS_{u3}$ and $OS_{u4}$.
+After all the remote service may have resources which should be readable by the Origin Server users OSu1 and OSu2, but not to the Origin Server users OSu3 and OSu4.
 Or the representations returned may differ somewhat for each group of users.
-$OS_{u1}$ and $OS_{u2}$ may get some more information than $OS_{u1}$ and $OS_{u2}$.
-As a result it is important for the origin server to distinguish on behalf of which users it is acting when making a request.
+OSu1 and OSu2 may get some more information than OSu1 and OSu2.
+As a result it is important for the Origin Server to distinguish on Behalf of which users it is acting when making a request.
 
@@
 
-\todo{insert description of On-behalf-Of header (at least the importance of such a feature)}
+\todo{insert description of On-behalf-Of header}
 
-\subsection{Solution 3: Secretary acting on Behalf of a User}
+\textit{Solution3: Secretary acting on Behalf of a User}
 
@@
 It can no longer just compare the TLS keys.
-Instead it can see if the user that the secretary is acting on behalf of has stated clearly that that agent is its secretary.
-This can be discovered by checking out the profile... \todo{fill out the details here}
+Insterad it can see if the user that the secretary is acting on behalf of has stated clearly that that agent is its secretary.
+This can be discovered by checking out the profile...
+\todo{fill out the details here}
 
@@
 
+\begin{figure*}[htb]
+  \centering
+  \includegraphics[width=\textwidth]{myprofile}
+  \caption{The MyProfile application.}
+  \label{fig:myprofile}
+\end{figure*}
+
 \section{Related Work}\label{sec:relatedwork}

### 2012-08-03 paper.tex

@@
 \subsection{MyProfile description}
-MyProfile intends to provide a solution for managing the numerous accounts and profiles that users have on the Internet.
+MyProfile\footnote{http://myprofile-project.org/} intends to provide a solution for managing the numerous accounts and profiles that users have on the Internet.
 Its main purpose is to provide a unified user account, or simply \textit{user profile}, which as opposed to current \textit{silo} profiles, would really be under the user's control, on a device located within the user physical reach.

### 2012-08-03 paper.tex
niceup introduction

--- 2012-08-03 paper.tex
@@
 
-Agents on the web communicate with each other through a limited number of actions: by making requests for resources (GET), by creating resources (POST or PUT), or even by deleting resources \ldots
-Creation or deletion of resources usually require authentication of the agent making the request, and so in many cases do requests for information (GET).
+Agents on the web communicate with each other through a limited number of actions: by making requests for resources (\texttt{GET}), by creating resources (\texttt{POST} or \texttt{PUT}), or even by deleting resources.
+Creation or deletion of resources usually require authentication of the agent making the request, and so in many cases do requests for information.
 
-The WebID protocol enables the global identification of agents using asymmetric cryptography in a way that fits cleanly with this architecture: namely in such a way that agents can verify each others identity without having had any previous interactions and in such a way as to allow trust to build up in a decentralized manner.
+The WebID protocol enables the global identification of agents using asymmetric cryptography in a way that fits cleanly with this architecture:
+namely in such a way that agents can verify each others identity without having had any previous interactions and in such a way as to allow trust to build up in a decentralized manner.
 
@@
 The WebID protocol is used currently mostly for client authentication%
-\footnote{Server authentication using IETF DANE follows much the same logic, except that the lookup for the identity is not done using the HTTP protocol but DNSSEC.}.
+\footnote{Server authentication using IETF DANE follows much the same logic, except that the lookup for the identity is not done using the HTTP protocol but DNSSEC~\cite{hoffman-p-2012--a}.}.
 It is worth noting that the host serving the WebID profiles controls the identity of every agent whose URI is within that server's namespace.
@@
 The WebID profile furthermore could be served by the same agent as the one making the request, in which case we have a minimal case of a peer to peer communication.
-Note that fetching a WebID profile for WebID authentication should be done anonymously, for fear of authentication deadlocks.\footnote{ for example one can imagine an agent S  with profile Ps requesting a resource on server R which requires authentication.
-S would send R its certificate, thereby requiring  R to dereference S's Profile Ps in order to verify the WebID.
-If Ps  itself requires authentiction of R and if R sends a certificate containing a WebID with its profile Pr, and if Pr itself requires authentication then it looks like we have a deadlock.
-}
+Note that fetching a WebID profile for WebID authentication should be done anonymously, for fear of authentication deadlocks%
+\footnote{For example one can imagine an agent $S$ with profile $P_s$ requesting a resource on server $R$ which requires authentication.
+$S$ would send $R$ its certificate, thereby requiring $R$ to dereference $S$'s profile $P_s$ in order to verify the WebID.
+If $P_s$ itself requires authentiction of $R$ and if $R$ sends a certificate containing a WebID with its profile $P_r$, and if $P_r$ itself requires authentication then it looks like we have a deadlock.}.
 
@@
 This authorization rule will require the web server to fetch each of its users' friends profiles, in order to build up such a list.
-But there is a privacy issue involved here: not every one wants to make all of their social network publically visible, and some may not want to make any of it publicly visible.
+But there is a privacy issue involved here: not everyone wants to make all of their social network publically visible, and some may not want to make any of it publicly visible.
 Those people may then protect their FOAF profile with access control rules.
@@
 \autoref{sec:spec} goes into detail with the WebID specification and adds support for authorization delegation,
-in \autoref{sec:eval} we describe our reference implementations based on two web applications and finally
-in \autoref{sec:relatedwork} we compare our proposal with two protocols, namely CORS and OAuth.
+in \autoref{sec:eval} we describe our reference implementations based on two web applications which is followed by \autoref{sec:relatedwork} where we compare our proposal with two other protocols, namely CORS and OAuth.
+Finally, we conclude our work in \autoref{sec:conclusion} and give directions for future work.
 
@@
 We can only assume that in a non-Linked Data environment, one can take advantage of OAuth in order to create the trust relationship between a user (agent) and the secretary (cf.
-Listing~\ref{list:sec_relation}), while access delegation would take place at a later time.
+Listing~\ref{listing:webid1}), while access delegation would take place at a later time.
 
@@
 
-\section{Conclusion and Future Work}
+\section{Conclusion and Future Work}\label{sec:conclusion}
 

### 2012-08-03 paper.tex

@@
 \subsection{MyProfile}
-MyProfile intends to provide a solution for managing the numerous accounts and profiles that users have on the Web.
+
+MyProfile\footnote{\url{http://myprofile-project.org/}} intends to provide a solution for managing the numerous accounts and profiles that users have on the Web.
 Its main purpose is to provide a unified user account, or simply \textit{user profile}, which as opposed to current \textit{silo} profiles, would really be under the user's control, on a device located within the user physical reach.
@@
   \centering
-  \includegraphics[width=\textwidth]{AuthSequence}
-  \caption{The MyProfile dashboard visualizes information from different sources fetched by the MyProfile server as a secretary of its user}
-  \label{fig:MyProfile}
+  \includegraphics[width=\textwidth]{myprofile}
+  \caption{The MyProfile dashboard visualizes information from different sources fetched by the MyProfile server as a secretary for its users}
+  \label{fig:myprofile}
 \end{figure*}

### 2012-08-03 paper.tex
Add OntoWiki subsection
- OntoWiki subsection added with general description, data import
  use-case, Semantic Pingback use-case and screenshot
- Add paper.synctex.gz to .gitignore

@@
 \subsection{OntoWiki}
-\todo{Phil: Add OntoWiki general description, the usecases for webid delegation as well as a demonstrating screenshot here}
+OntoWiki~\cite{auer-s-2006-736-a} is a web application, which allows for publication, exploration as well as manipulation of arbitrary RDF knowledge bases in distributed scenarios.
+We refer to it as a data wiki, since it adopts the wiki philosophy (ease of editing, tracking of changes, integrated dicscussions) on the one hand, while focussing on structured information on the other hand.
+Furthermore OntoWiki is an adaptable application framework, which supports the creation of Linked Data based applications on the web~\cite{heino-n-2009-61-a}.
+In addition to the usual features of wikis, OntoWiki provides a sophisticated extension system, such that it can be adapted for a variety of use-cases.
+Although the wiki philosophy proposes that everyone can edit everything, numerous real-world applications imply the need for access-control mechanisms.
+OntoWiki has built-in support for authorization on graph and action level.
+Furthermore several authentication protocols can be employed, including amongst others the WebID protocol.
+
+\begin{figure*}[htb]
+  \centering
+  \includegraphics[width=\textwidth]{ontowiki}
+  \caption{An external and thus imported WebID profile shown in a generic OntoWiki view, which can be used to visualize arbitrary RDF resources.}
+  \label{fig:ontowiki}
+\end{figure*}
+
+\paragraph{Data import}
+A first use-case for WebID access delegation within OntoWiki arises from an important functionality within OntoWiki, namely import of external data.
+Figure \ref{fig:ontowiki} shows a WebID profile that was imported via the Linked Data principles into a local knowledge base.
+Since WebID profiles can contain personal information that is in need of protection, access to such data should be restricted with the WebID protocol.
+Although a user may (or may not in the case of a periodically executed automatic synchronization process) initiate the import procedure manually via the OntoWiki user interface, the actual fetching is done in the background.
+An OntoWiki instance does not know of any private keys of users of the system.
+Thus the system is not able to use that information when requesting data.
+With WebID access delegation though, the profile can be fetched on behalf of the user instead.
+
+\paragraph{Semantic Pingback}
+Another use-case where access delegation can be employed is within the Semantic Pingback protocol~\cite{tramp-s-2010--b}.
+With Semantic Pingback owners of resources can be notified when for example a link to such a resource is created elsewhere on the web.
+In order to protect the protocol against spam attacks, a Pingback server will fetch the desired resource and check, whether the stated link is indeed contained in the data.
+The source resource that links to the target resource and thus is fetched by a Pingback server might be access restricted, for example in a scenario where a friending process is initiated~\cite{story-h-2011--a}.
+For privacy reasons the owner of the WebID profiles will very likely hide the triples in question (e.g. \texttt{foaf:knows}) on anonymous access attempts.
+With WebID access delegation again, the resources can be fetched by the Pingback server on behalf of the resource owner.
 

### 2012-08-03 paper.tex
Change wording in abstract and introduction
- A word in abstract has been removed in order to fix right margin
  overflow
- Remove double wording in abstract
- Change wording from spec to specification

@@
 \begin{abstract}
-The WebID protocol enables the global identification of agents in a distributed manner by combining asymmetric cryptography and Linked Data.
+The WebID protocol enables global identification of agents in a distributed manner by combining asymmetric cryptography and Linked Data.
 WebIDs are mostly used in scenarios where a user utilize a browser application to access a protected resource on a web server.
-But in order to decide whether access should be granted or denied, the web server itself needs to retrieve other WebID profiles and linked resources in order to work out if the requesting agent is part of the authorization group ( eg: is a friends of a friend of the resource owner ).
+As a prerequisite for deciding whether access should be granted or denied, the web server itself needs to retrieve other WebID profiles and linked resources in order to work out if the requesting agent is part of the authorization group (e.g.
+is a friends of a friend of the resource owner).
 It would seem that at present this information needs to be publicly available for the server to access it.
@@
 Indeed WebID authentication requires the server to make WebID profile requests to other servers in order to verify the identity of agents making a request to it.
-The WebID spec describes this task as being accomplished by a separate agent, the WebID verifier - which could indeed be done by another service on the web (WebID proxy authentication servers).
+The WebID specification describes this task as being accomplished by a separate agent, the WebID verifier - which could indeed be done by another service on the web (WebID proxy authentication servers).
 But it can also be so closely tied to the web service that it would be natural to think of it as part of that same service.

### 2012-08-03 paper.tex
changes to the paper - did not make it in

--- 2012-08-03 paper.tex
@@
 \lstdefinestyle{turtle}{
-    morekeywords={a, @prefix, cert,xsd,foaf, rdf, rdfs, owl},
+    morekeywords={a, @prefix, cert,xsd, foaf, rdf, rdfs, owl},
     morecomment=[s][\textrm]{<}{>},
@@
 The WebID protocol enables the global identification of agents in a distributed manner by combining asymmetric cryptography and Linked Data.
-WebIDs are mostly used in scenarios where a user utilize a browser application to access a protected resource on a web server.
-But in order to decide whether access should be granted or denied, the web server itself needs to retrieve other WebID profiles and linked resources in order to work out if the requesting agent is part of the authorization group ( eg: is a friends of a friend of the resource owner ).
-It would seem that at present this information needs to be publicly available for the server to access it.
-This  leads to a privacy issue, since agents may want to limit access to a users social graph.
-In this paper we propose an extension to the WebID protocol which allows for delegation of access authorization from a WebID to a third party, e.g.
+WebIDs is usually thought of as a browser authentication method, allowing humans an easy point and click method to authenticate to any remote servers.
+But in order for such a server to decide whether access should be granted or denied to a particular WebID, it (the web server) may need to retrieve other profiles and linked resources in order to work out if the requesting agent is member of the authorized group ( eg: is a friends of a friend (FOAF) of the resource owner ).
+If these linked resources ( e.g. FOAF profiles ) are required to be publicly available for the server to access it, then this would be a major privacy limitiation on a linked social network.
+In this paper we explore the different ways an agent can act as a user, and we propose an extension to the WebID protocol which allows for delegation of access authorization from a WebID to a third party, e.g.
 allowing a server to be able to act on behalf of its users.
@@
 Things get more interesting in the authorization space.
-Consider a very natural application of WebID: allowing friends of one's friends (foaf) access to some resources.
-This authorization rule will require the web server to fetch each of its users' friends profiles, in order to build up such a list.
-But there is a privacy issue involved here: not everyone wants to make all of their social network publically visible, and some may not want to make any of it publicly visible.
-Those people may then protect their FOAF profile with access control rules.
-How can a server that needs access to these FOAF profiles in order to apply its own access control rules - such as only allowing access to foaf - get access to the information?
-Should it be able to do so?
+Consider a very natural application of WebID: allowing friends of one's friends (FOAF) access to some resources.
+This authorization rule will require the web server to fetch each of its users' friends profiles, in order to build up the list of authorised users.
+But there is a privacy issue involved here: not everyone wants to make all of their social network publicly visible, and some may not want to make any of it publicly visible.
+Those people may then protect their FOAF profile with access control rules such as only allowing FOAF access to it.
+How can a server that needs access to these FOAF profiles in order to apply its own access control rules - such as only allowing access to FOAF - get access to the information? 
+Would the server itself need to be listed as a FOAF by each of the users friends?
+Should the server take on the identity of the user it is fetching resources for? 
+How would it be able to do so?
+What other solutions are there?
 These are the questions we will try to answer in this paper.
@@
 
+\todo{is this section really needed? It seems mostly to repeat the previous section, and the next one, while loosting the thread
+of the questioning}
+
 This section describes several usage scenarios requiring access delegation which can not be solved efficiently with the standard WebID authentication protocol.
@@
 These applications provide their services to one user only and also run on a device which is commonly accessed by one user only (e.g. a smartphone).
-This class of \textit{private applications} is similar to browsers and can be seen as an extension to the user itself~\cite{clark-a-1998-7-a}.
+This class of \textit{private applications} is similar to browsers and can be seen as an extension of the user himself, as argued by Andy Clark and David Chalmers ~\cite{clark-a-1998-7-a}.
 
@@
 
-\subsection{Solution 1: Passing itself for the user}
+\subsection{Solution 1: Acting as the user}
 
-The simplest solution for any agent $S$ wishing to pass itself off as one of the users $U$, is for it to create a public / private key pair,  place the public key in a certificate $C_u$ and add the public key to the users' profile $P_u$.
-Having done this the agent $S$ can then connect using the certificate $C_u$ to any service it wishes to, when it wants to work for the user $U$.
+The simplest solution for any user agent $UA$ wishing to act as the user $U$, is for it to create a public / private key pair,  place the public key in a certificate $C_u$ with the $UA$'s WebID in the Subject Alternative Name position and simultaneously add the public key to the user $U$'s profile $P_u$.
+Having done this the agent $UA$ can then connect using the certificate $C_u$ and its associated private key, to any service it wishes to, when it wants to work for / as the user $U$.
 This has the advantage of requiring no change to the WebID protocol.
-It does give the agent $S$ all powers of the user $U$ and so has to be handled with great care.
+It does give the agent $UA$ all powers of the user $U$ and so this type of privilege should be limited to agents in which are either extensions of $U$ or ones $U$ can or must fully trust anyway.
+
+\lstinputlisting[
+    lastline=26,name=webid,style=turtle,float=htb,label=listing:webid1,
+    basicstyle=\ttfamily\scriptsize,
+    caption={Profile allowing three different agents to act as Romeo}
+]{Listings/mutlipleKeys.ttl}
 
@@
 Or put another way: what agent would giving such rights to not constitute a reduction in security to the user?
-Or put yet another way: which agent could take such a role at its behest at any moment in any case?
-Or: which agent does the user and the authorization server already rely on for authentication?
-There is one agent  on which any service requiring WebID authentication relies on and this is the WebID profile origin server~\cite{barth-a-2011--a}.
+Or: which agent does the user and the authorization server already rely on completely?
+
+In addition to the well known User Agents found in browsers on many different devices, there is one agent  on which any service requiring WebID authentication relies on completely and this is the WebID profile's origin server~\cite{barth-a-2011--a}.
 Any server requiring authentication of an agent using WebID must trust the origin server serving the WebID Profile.
@@
 
-When the user owns the origin server then the origin server is just an extension of the user, and in that case there need be no thought of a difference between the user and the origin server.
+When the user owns the origin server and there is a one to one relation between the two, as is principally the case in the FreedomBox, then the origin server is again just an extension of the user, and in that case there need be no thought of a difference between the user and the origin server.
 In that case the origin server can in fact just authenticate as the user whenever needed.
 
-But when the origin server (OS) is serving a number of different profiles and is acting on behalf of a number of different users, then we have an efficiency issue that rears its head.
-Whenever the Origin Server needs to act on behalf of one ifs users to a remote server $R$ it will need to open a new TLS connection to that server using one of its users public keys.
-For $N$ users this could require $N$ parallel connections to a server $S$.
+It should be noted that each device can still be distinguished by servers in case of a problem by logging the exact public key that was used to connect to a service. 
+It should be possible then to track down which device's private key had been compromised in case of unusual authentication behavior .
+
+But when the origin server (OS) is serving a number of different profiles and is acting on behalf of a number of different users, then we have two issues that need to be taken into account: an issue of data perspective and an efficiency issue.
+
+First whenever $OS$ connects as $U_1$ to a service it has to place the data received in a seperate quad store from the one it 
+stores data as when connecting to that resources as user $U_2$. This is because the resource may return different representations
+depending on who is connecting to it - one representation for close friends perhaps, and one for more distant ones.
+
+Secondly, Whenever the Origin Server needs to act on behalf of $U_1$ to a remote server $R$ it will need to open a new TLS connection to that server using the certificate $C_u1$ for that user.
+For $N$ users this could require $N$ parallel connections to the same server $S$.
 \todo{calculate how inefficient this is, and at what size of network this starts really become problematic}

### 2012-08-03 paper.tex

@@
 The WebID protocol enables the global identification of agents in a distributed manner by combining asymmetric cryptography and Linked Data.
-WebIDs is usually thought of as a browser authentication method, allowing humans an easy point and click method to authenticate to any remote servers.
 But in order for such a server to decide whether access should be granted or denied to a particular WebID, it (the web server) may need to retrieve other profiles and linked resources in order to work out if the requesting agent is member of the authorized group ( eg: is a friends of a friend (FOAF) of the resource owner ).

### 2012-08-03 paper.tex
Added example of different views on the same resource

@@
 \lstinputlisting[
-    lastline=26,name=webid,style=turtle,float=htb,label=listing:webid1,
+    lastline=26,name=webid,style=turtle,float=htb,label=listing:multipleKeyProfile,
     basicstyle=\ttfamily\scriptsize,
@@
 
-But when the origin server (OS) is serving a number of different profiles and is acting on behalf of a number of different users, then we have two issues that need to be taken into account: an issue of data perspective and an efficiency issue.
+But when the origin server $OS$ is serving a number of different profiles $P_1$, $P_2$, $P_3$, ...
+$P_n$ each identifying the N users $U_1$, $U_2$, $U_3$, ..., $U_n$ and is acting on behalf of a these users, as would be the case for a  company, government agency, school, educational instituion, charyity, football club, ...
+server, then we have two issues that need to be taken into account: first an issue of data perspective and an efficiency issue.
 
-First whenever $OS$ connects as $U_1$ to a service it has to place the data received in a seperate quad store from the one it 
-stores data as when connecting to that resources as user $U_2$. This is because the resource may return different representations
-depending on who is connecting to it - one representation for close friends perhaps, and one for more distant ones.
+First whenever $OS$ connects as $U_1$ to a remote resource $R$ it has to place the data received in a seperate quad store from the one it stores data in as when connecting to  the same resurce $R$ as the different user $U_2$.
+This is because the resource may return different representations depending on who is connecting to it - one representation for close friends of the owner of $R$ perhaps, and one for more distant ones.
+This can be illustrated using N3 graphs, by specifying a relation between a yet to be invented vocabulary of views on a resource, and a graph (cf. Listing~\ref{listing:views})
 
-Secondly, Whenever the Origin Server needs to act on behalf of $U_1$ to a remote server $R$ it will need to open a new TLS connection to that server using the certificate $C_u1$ for that user.
-For $N$ users this could require $N$ parallel connections to the same server $S$.
+\lstinputlisting[
+    lastline=36,name=views,style=turtle,float=htb,label=listing:views,
+    basicstyle=\ttfamily\scriptsize,
+    caption={Views on Juliet's FOAF profile by Freedom Box Laurence, when acting as Romeo and when acting as Lord Montague }
+]{Listings/views.n3}
+
+Secondly, Whenever the Origin Server needs to act on behalf of $U_1$ to a remote server $R$ it will need to open a new TLS connection to that server using the certificate $C_{u1}$ for that user.
+ this could require $N$ parallel connections to the same server $S$.
 \todo{calculate how inefficient this is, and at what size of network this starts really become problematic}

### 2012-08-04 paper.tex
some niceups and notes

@@
     caption={Profile allowing three different agents to act as Romeo}
-]{Listings/mutlipleKeys.ttl}
+]{Listings/mutlipleKeys.ttl}\todo{ST: Can we shorten this to two agents?}
 
@@
 
-But when the origin server $OS$ is serving a number of different profiles $P_1$, $P_2$, $P_3$, ...
-$P_n$ each identifying the N users $U_1$, $U_2$, $U_3$, ..., $U_n$ and is acting on behalf of a these users, as would be the case for a  company, government agency, school, educational instituion, charyity, football club, ...
+But when the origin server $OS$ is serving a number of different profiles $P_1 \ldots P_n$ each identifying the N users $U_1 \ldots U_n$ and is acting on behalf of a these users, as would be the case for a company, government agency, school, educational instituion, charyity, football club, ...
 server, then we have two issues that need to be taken into account: first an issue of data perspective and an efficiency issue.
@@
     caption={Views on Juliet's FOAF profile by Freedom Box Laurence, when acting as Romeo and when acting as Lord Montague }
-]{Listings/views.n3}
+]{Listings/views.n3}\todo{ST: \autoref{listing:views} is too long (maybe shorten, I dont know)}
 

### 2012-08-04 paper.tex
adding On-Behalf-Of section

--- 2012-08-03 paper.tex
@@
 
-The simplest solution for any user agent $UA$ wishing to act as the user $U$, is for it to create a public / private key pair,  place the public key in a certificate $C_u$ with the $UA$'s WebID in the Subject Alternative Name position and simultaneously add the public key to the user $U$'s profile $P_u$.
-Having done this the agent $UA$ can then connect using the certificate $C_u$ and its associated private key, to any service it wishes to, when it wants to work for / as the user $U$.
+The simplest solution for any user agent $A$ wishing to act as the user $U$, is for it to create a public / private key pair,  and with the public key thus generated create a certificate $C_u$ with $U$'s WebID in the Subject Alternative Name position and add the public key to the user $U$'s profile $P_u$.
+Having done this the agent $A$ can then connect using the certificate $C_u$ and its associated private key, to any service it wishes to, when it wants to work for / as the user $U$.
 This has the advantage of requiring no change to the WebID protocol.
-It does give the agent $UA$ all powers of the user $U$ and so this type of privilege should be limited to agents in which are either extensions of $U$ or ones $U$ can or must fully trust anyway.
+It does give the agent $A$ all powers of the user $U$ and so this type of privilege should be limited to agents in which are either extensions of $U$ or ones $U$ can or must fully trust anyway.
 
@@
 
-When the user owns the origin server and there is a one to one relation between the two, as is principally the case in the FreedomBox, then the origin server is again just an extension of the user, and in that case there need be no thought of a difference between the user and the origin server.
+When the user owns the origin server and there is a one to one relation between the two, as is principally the case in a personal FreedomBox, then the origin server is again just an extension of the user, and in that case there need be no thought of a difference between the user and the origin server.
 In that case the origin server can in fact just authenticate as the user whenever needed.
@@
 
-But when the origin server $OS$ is serving a number of different profiles $P_1$, $P_2$, $P_3$, ...
-$P_n$ each identifying the N users $U_1$, $U_2$, $U_3$, ..., $U_n$ and is acting on behalf of a these users, as would be the case for a  company, government agency, school, educational instituion, charyity, football club, ...
-server, then we have two issues that need to be taken into account: first an issue of data perspective and an efficiency issue.
+Things get more interesting when an origin server agent $A$ is serving a number of different profiles $P_1$, $P_2$, $P_3$, ...
+$P_n$ each identifying the N users $U_1$, $U_2$, $U_3$, ..., $U_n$ and is acting on behalf of a these users.
+This would be the situation for servers acting for companies, government agencies, educational instituion, charities, football club, ....
+This brings up two issues that need to be taken into account: first an issue of data perspective and an efficiency issue.
 
-First whenever $OS$ connects as $U_1$ to a remote resource $R$ it has to place the data received in a seperate quad store from the one it stores data in as when connecting to  the same resurce $R$ as the different user $U_2$.
+\subsubsection{Keeping views distinct: }
+
+First whenever $A$ connects as $U_1$ to a remote resource $R$ it has to place the data received in a seperate graph from the one it stores public non authenticated data in, and to the one it stores a representation to the same resurce $R$ seen when connected as the different user $U_2$.
 This is because the resource may return different representations depending on who is connecting to it - one representation for close friends of the owner of $R$ perhaps, and one for more distant ones.
-This can be illustrated using N3 graphs, by specifying a relation between a yet to be invented vocabulary of views on a resource, and a graph (cf. Listing~\ref{listing:views})
+This can be illustrated using N3 graphs, by specifying a relation between a yet to be invented vocabulary of views on a resource, and a graph (cf. Listing~\ref{listing:views}). 
+It is very important that the agent receiving information from different users not merge the information that was destined to different users, or else information leakage will severely reduce the trust other agents have in that server $A$.
+This requires carefully keeping identified information that was aimed at different users seperate, perhaps by creating different graph stores: one for publically - non authenticated - information, and one graph store for each user the server needs to authenticate as.
 
@@
 
+\subsubsection{TLS inefficiency: }
+
 Secondly, Whenever the Origin Server needs to act on behalf of $U_1$ to a remote server $R$ it will need to open a new TLS connection to that server using the certificate $C_{u1}$ for that user.
- this could require $N$ parallel connections to the same server $S$.
+This could require $N$ parallel connections to the same server $S$. 
+Opening TLS connections is somewhat expensive: it requires opening up a new TCP connection, starting an expensive asymmetrick key cryptographic handshake. 
+For small numbers of N this can be defended, but as N becomes large the inefficiency this could create between two
+organisations may be a serious drawback.
 \todo{calculate how inefficient this is, and at what size of network this starts really become problematic}
 \todo{ST: add disadvantages according to the requirements (identity)}
+
+\paragraph{Conclusion}
+
+It is possible for any number of software agents to act AS the user by creating themselves a public key as described above.
+This does require a very strong trust relation to exist between the agent acting as the user and the user herself, as itthe two will be mostly indistinguishable in the linked web of trust. 
+This method also becomes inefficient the greater the number of different users  an agent is working for.
 
@@
 It could even use the same certificate.
-This would make clear to any server it was connecting to, that it could rely on this server as much as it could on the identity of any user served by that server.
+This would make clear to any server it was connecting to, that it could rely on this server as much as it could on the identity of any resource, and in particular any WebID profils served by that server.
 
-Still, such a server connecting to a remote service on behalf of one of its users would then need to identify which user it was acting on behalf of, or the remote service receiving a request would not know which access control rule to apply to the origin server.
+Still, such an agent connecting to a remote service on behalf of one of its users would then need to identify which user it was acting on behalf of, or the remote service receiving a request would not know which access control rule to apply to the requesting origin server.
+For example in our previous example in the Romeo and Juliet story we showed how the Capulet family Freedom Box only shows Juliet as knowing Romeo, when Romeo makes the request on the resource, but not when the request is made by Romeo's father, lord Montague.
+That was an easy access control rule for the Capulet Freedbom Box to make when the request was using the WebID protocol simipliciter, since there it would know via the WebID authentication process exactly which identity the user was making the request as.
 
-After all the remote service may have resources which should be readable by the origin server users $OS_{u1}$ and $OS_{u2}$, but not to the origin server users $OS_{u3}$ and $OS_{u4}$.
-Or the representations returned may differ somewhat for each group of users.
-$OS_{u1}$ and $OS_{u2}$ may get some more information than $OS_{u1}$ and $OS_{u2}$.
-As a result it is important for the origin server to distinguish on behalf of which users it is acting when making a request.
+The proposal here is for the Origin-Server to add to each HTTP request (made over TLS) an On-Behalf-Of header:
 
-Problems: using the same key between server acting as client and as server risks making the keys available to a wider audience, and so increases the risk of key compromise.
+\begin{verbatim}
+GET /juliet/knows HTTP/1.1
+Host: capulet.org
+User-Agent: FreedomBox_FamilyEdition/0.1 
+Accept: application/rdf+xml,text/turtle,application/xhtml+xml
+On-Behalf-Of: https://montague.net/romeo#me
+\end{verbatim}
+
+The Capulet FB Guard having verified that this request does indeed come from the origin server of Romeo's profile
+https://montague.net/romeo would then be able to accept that since the requesting server could in any case act as Romeo whenever it chose to do so, this protocol making exchange between the Montague and Capulet housholds more efficient without making it less secure, this be justification enough for it (the capulet freedom box) to  serve the representation that Romeo would have received had he connected to the server directly.
+We will argue further down that this is very similar to the way CORS deals with access control, namely by adding a header to a request to clearify what agent is making the request.
+
+This On-Behalf-Of header makes it possible for one agent to open only one TLS connection to a remote server and be 
+able to sepecify for each request on behalf of whome it is making it.
+The Montague Freedom Box could make a request to the capulet Freedom Box On-Behalf-Of Romeo, a few milliseconds later On-Behalf-Of Lord Capulet, and so on...
+Again as explained in the previous section is is the responsibility of the Montague Freedom Box to keep these inforation seperate, and act with secrecy whenever it is acting on behalf of one or the other of the users.
+As such it's role is not unlike the role of Friar Laurence in the play: dedication to people's private matters requires tact and secrecy.
+
+\paragraph{Limitations}
+
+Using the same cryptographic key between the server acting as client and as server risks making the keys available to a wider audience, and so increases the risk of key compromise. 
+It may be useful if it were possible to decouple the identity of the agent acting on behalf of another user from the Origin Server.
 

### 2012-08-04 paper.tex

@@
 It should be possible then to track down which device's private key had been compromised in case of unusual authentication behavior .
+
+But when the origin server $OS$ is serving a number of different profiles $P_1 \ldots P_n$ each identifying the N users $U_1 \ldots U_n$ and is acting on behalf of a these users, as would be the case for a company, government agency, school, educational instituion, charyity, football club, ...
+server, then we have two issues that need to be taken into account: first an issue of data perspective and an efficiency issue.
 
@@
     caption={Views on Juliet's FOAF profile by Freedom Box Laurence, when acting as Romeo and when acting as Lord Montague }
-]{Listings/views.n3}
-
-\subsubsection{TLS inefficiency: }
+]{Listings/views.n3}\todo{ST: \autoref{listing:views} is too long (maybe shorten, I dont know)}
 

### 2012-08-04 paper.tex
Redone (condensed) the OAuth section.

--- 2012-08-04 paper.tex
@@
     caption={Profile allowing three different agents to act as Romeo}
-]{Listings/mutlipleKeys.ttl}\todo{ST: Can we shorten this to two agents?}
+]{Listings/mutlipleKeys.ttl}
 
@@
 
-But when the origin server $OS$ is serving a number of different profiles $P_1 \ldots P_n$ each identifying the N users $U_1 \ldots U_n$ and is acting on behalf of a these users, as would be the case for a company, government agency, school, educational instituion, charyity, football club, ...
+But when the origin server $OS$ is serving a number of different profiles $P_1$, $P_2$, $P_3$, ...
+$P_n$ each identifying the N users $U_1$, $U_2$, $U_3$, ..., $U_n$ and is acting on behalf of a these users, as would be the case for a  company, government agency, school, educational instituion, charyity, football club, ...
 server, then we have two issues that need to be taken into account: first an issue of data perspective and an efficiency issue.
@@
     caption={Views on Juliet's FOAF profile by Freedom Box Laurence, when acting as Romeo and when acting as Lord Montague }
-]{Listings/views.n3}\todo{ST: \autoref{listing:views} is too long (maybe shorten, I dont know)}
+]{Listings/views.n3}
 
@@
 
-OAuth~2.0\footnote{http://tools.ietf.org/html/draft-ietf-oauth-v2} is the latest version of the OAuth protocol, which is being presented as an access delegation protocol, enabling users to grant third-party access to their web resources without sharing their passwords.
-Even if OAuth provides authentication as a byproduct of having the resource owner authorize a client to a resource server, its main focus is on authorization rather than on federated identity.
+OAuth~2.0\footnote{http://tools.ietf.org/html/draft-ietf-oauth-v2} is the latest version of the OAuth protocol, which is being presented as an access delegation protocol, enabling users to grant access to third-party services to their personal resources, instead of sharing their passwords with those third-party services.
+OAuth includes two main parts: obtaining an access token by asking the resource owner (i.e.
+the user) to grant access, and then using the tokens to access protected resources.
 
-OAuth includes two main parts: obtaining a token by asking the user to grant access, and using tokens to access protected resources (Fig.~\ref{fig:oauth2flow}).
-OAuth has been designed around the following client profiles:
+Here is a typical example of using OAuth.
+Ann has a Twitter account.
+One day she decides to support her favourite project by using Flattr\footnote{http://flattr.com/}, a micropayment service.
+Since she would rather not create a new account, Flattr offers her the possibility of using her Twitter account to log into Flattr.
+After clicking the "Login using Twitter" button, she is redirected to Twitter's login page where she inputs her username and password.
+Once authenticated, Twitter informs her that Flattr.com would like to access her personal information (e.g.
+name, picture, etc.).
+She can now choose if she wants to grant or deny to Flattr access to her Twitter account information.
+Once she accepts, she is redirected back to Flattr.com where she notices that she is now authenticated, and her Twitter username, full name and picture now appear in Flattr.
 
-\paragraph*{web application} -- A web application is a confidential client running on a web server.
-Resource owners access the client via an HTML user interface rendered in a user-agent on the device used by the resource owner.
+The advantage here is that Ann only had to use her Twitter credentials to log into Flattr.
+However, the disadvantage is that Flattr requires an existing trust relationship with Twitter, thus limiting the number of supported services.
 
-\paragraph*{user-agent-based application} -- A user-agent-based application is a public client in which the client code is downloaded from a web server and executes within a user-agent (e.g.
-web browser) on the device used by the resource owner.
+Even if OAuth provides authentication as a by-product of having the resource owner authorize a third-party client to his/her resource server, its main focus is on resource authorization rather than on federated identity.
 
-\paragraph*{native application} -- A native application is a public client installed and executed on the device used by the resource owner.
-Protocol data and credentials are accessible to the resource owner.\\
-
-OAuth defines four basic roles:
-
-\begin{figure*}[htb]
-  \centering
-  \includegraphics[width=\textwidth]{Oauth2.pdf}
-  \caption{OAuth 2.0 protocol flow}
-  \label{fig:oauth2flow}
-\end{figure*}
-
-\begin{enumerate}
-\item resource owner -- An entity capable of granting access to a protected resource. When the resource owner is a person, it is referred to as an end-user (i.e. you).
-
-\item resource server -- The server hosting the protected resources, capable of accepting and responding to protected resource requests using access tokens.
-
-\item client -- An application which accesses a resource owner's protected resources after the resource owner has explicitly granted it permission -- this last part can also be rephrased into "after the resource owner has authorized the client to his/her protected resources".
-
-\item authorization server -- The server issuing access tokens to the client after successfully authenticating the resource owner and obtaining authorization.
-The authorization server may be the same server as the resource server or a separate entity.
-\end{enumerate}
-
-The OAuth protocol flow in Fig.~\ref{fig:oauth2flow} can be explained as follows:
-
-\paragraph*{(A)} The client initiates the flow by directing the resource owner's user-agent to the authorization endpoint.
-The client includes         its client identifier, requested scope, local state, and a redirection URI to which the authorization server will send the user-agent back once access is granted (or denied).
-
-\paragraph*{(B)} The authorization server authenticates the resource owner (via the user-agent) and establishes whether the resource owner grants or denies the client's access request.
-
-\paragraph*{(C)} Assuming the resource owner grants access, the authorization server redirects the user-agent back to the client using the redirection URI provided earlier (in the request or during client registration).
-The redirection URI includes an authorization code and any local state provided by the client earlier.
-
-\paragraph*{(D)} The client requests an access token from the authorization server's token endpoint by including the authorization code received in the previous step.
-When making the request, the client authenticates with the authorization server.
-The client includes the redirection URI used to obtain the authorization code for verification.
-
-\paragraph*{(E)} The authorization server authenticates the client, validates the authorization code, and ensures the redirection URI received matches the URI used to redirect the client in step (C).
-If valid, the authorization server responds back with an access token and optionally, a refresh token.
-A single access token may grant varying degrees of access to multiple APIs.
-The set of resources and operations permitted by an access token is controlled during the access token request via a variable parameter called \textit{scope}.
-Several scopes may be included in a request.\\
-
-To summarize what we have seen so far, OAuth is not exactly an access delegation protocol, but rather a protocol which authorizes a resource consumer to securely access data from a resource server.
-Once the access token has been created, both applications communicate directly between themselves, without any need for delegation.
-
-We can only assume that in a non-Linked Data environment, one can take advantage of OAuth in order to create the trust relationship between a user (agent) and the secretary (cf.
-Listing~\ref{listing:webid1}), while access delegation would take place at a later time.
-
-%As opposed to WebID Access Delegation where the resource owner specifies the secretary relation using Linked Data (cf.
-Listing~\ref{list:sec_relation})\todo{A: Linked Data reference?}, OAuth requires a pre-existing relationship between resource consumer and resource server, in the form of a shared secret.
-The OAuth relationship is created by manually registering \textit{each} resource consumer with the resource server.
-Furthermore, explicit user consent is required each time a new resource consumer requires access to the user's resource server.
-
-%A fix for cases where there is little trust in a secretary, or when bootstrapping a user's server.
-The resource provider can store the request from consumer, and send a pingback to the consumer service, to notify him/her of a pending authorization request from consumer.
-Then the user will have to authenticate personally (through the browser, in order to verify the private key) to the provider, check a list of pending requests for his/her WebID, and decide if the request in question is valid or not.
-In other words, the user must give his/her consent if the secretary's identity is unknown to the provider.
+The conclusion is that OAuth is used to \textit{provide access for external services to local user resources} without disclosing the user's credentials.
+On the other hand, in WebID access delegation, the secretary is used to \textit{gain access to external resources} on behalf of a given user.
 

### 2012-08-04 paper.tex
shorted code and improved merges

--- 2012-08-04 paper.tex
@@
 \lstinputlisting[
-    lastline=26,name=webid,style=turtle,float=htb,label=listing:multipleKeyProfile,
+    firstline=6,lastline=26,name=webid,style=turtle,float=htb,label=listing:multipleKeyProfile,
     basicstyle=\ttfamily\scriptsize,
     caption={Profile allowing three different agents to act as Romeo}
-]{Listings/mutlipleKeys.ttl}\todo{ST: Can we shorten this to two agents?}
+]{Listings/mutlipleKeys.ttl}
 
@@
 
-But when the origin server $OS$ is serving a number of different profiles $P_1 \ldots P_n$ each identifying the N users $U_1 \ldots U_n$ and is acting on behalf of a these users, as would be the case for a company, government agency, school, educational instituion, charyity, football club, ...
-server, then we have two issues that need to be taken into account: first an issue of data perspective and an efficiency issue.
-
-Things get more interesting when an origin server agent $A$ is serving a number of different profiles $P_1$, $P_2$, $P_3$, ...
-$P_n$ each identifying the N users $U_1$, $U_2$, $U_3$, ..., $U_n$ and is acting on behalf of a these users.
+Things get more interesting when an origin server agent $A$ is serving a number of different profiles $P_1$ \ldots $P_n$ each identifying the N users $U_1$ \ldots $U_n$ and is acting on behalf of a these users.
 This would be the situation for servers acting for companies, government agencies, educational instituion, charities, football club, ....
@@
 \lstinputlisting[
-    lastline=36,name=views,style=turtle,float=htb,label=listing:views,
+    firstline=8,lastline=36,name=views,style=turtle,float=htb,label=listing:views,
     basicstyle=\ttfamily\scriptsize,
     caption={Views on Juliet's FOAF profile by Freedom Box Laurence, when acting as Romeo and when acting as Lord Montague }
-]{Listings/views.n3}\todo{ST: \autoref{listing:views} is too long (maybe shorten, I dont know)}
+]{Listings/views.n3}
 
@@
 
-In order to reduce the number of open connections to any server down to a minimum, it would be useful if the origin server could identify itself directly when making a request and specify on behalf of which of its users it was acting on.
+In order to reduce the number of open connections to any server down to a minimum, it would be useful if the origin server could identify itself directly when making a request and specify on behalf of which of its users it was acting on per request so as to be able to make multiple requests on the same TLS connection.
 One way would be for the origin server acting as client to simply use the same public key as the origin server acting as server - that is it could use the same public key as the one used by the TLS server.

### 2012-08-04 paper.tex
add conclusion

@@
 
+In this paper we discussed different ways how an agent, such as a Social Web application, can act on behalf of a user and request as well as manipulate resources on the Web in the name this user.
+Our proposal for supporting such a communication schema involves an extension to the WebID protocol, which allows for delegation of access authorization from one agent to another agent, both identified by its WebID.
+The technical solution annotates these \textit{in-the-name-of} HTTP requests by adding a HTTP request header field which refers to the WebID of the user in which name the agent acts on.
+This distinguish the identities of the user and the agent and allows for creation of policy descriptions which use both WebIDs to specify the relations between the agent and the user in order to setup the access rules for this agent.
+Since the protocol footprint is minimal, the main information entropy to decide whether an agent has the right to request a specific resource or not is available as part of the content of a WebID profile which can be requested as Linked Data.
+We believe that such an shift of the entropy from a protocol endpoint (such as in OAuth) to a machine readable document is a crucial feature of Linked Data in general and WebID in detail.
+
+However, at this point we postpone the answer to the question of how we should describe the access control rules in a users WebID profile.
+There already exists first attempts from the Linked Data / Semantic Web and the Read Write Web communities such as the WebAccessControl vocabulary\footnote{\url{http://www.w3.org/wiki/WebAccessControl}}, $_{dg}$FOAF~\cite{schwagereit-f-2010-181-a} as well as different projects on policy creation and management~\cite{kagal-l-2005--a,kagal-l-2005--b}.
+In our future work we will try to close the gap between the policy and access control vocabularies on the one hand and WebID authentication on the other hand.
+A rough abstract in which direction this should be elaborated is presented in \autoref{listing:views} and we hope that we can sensitize others to take up this challenge too.
+
 \bibliographystyle{plain}

### 2012-08-04 paper.tex
futher imporvements and fixes to the text

--- 2012-08-04 paper.tex
@@
 
-Things get more interesting when an origin server agent $A$ is serving a number of different profiles $P_1$ \ldots $P_n$ each identifying the N users $U_1$ \ldots $U_n$ and is acting on behalf of a these users.
+Things get more interesting when an origin server agent $A$ is serving a number of different profiles $P_1$ \ldots $P_n$ each identifying respectively users $U_1$ \ldots $U_n$ and needs to act on behalf of these users.
 This would be the situation for servers acting for companies, government agencies, educational instituion, charities, football club, ....
@@
 This is because the resource may return different representations depending on who is connecting to it - one representation for close friends of the owner of $R$ perhaps, and one for more distant ones.
-This can be illustrated using N3 graphs, by specifying a relation between a yet to be invented vocabulary of views on a resource, and a graph (cf. Listing~\ref{listing:views}). 
+This can be illustrated using N3 graphs, by specifying a relation between a view on a resource (using a yet to be settled on vocabulary), and a graph which is the log:semantics of that view (cf.
+Listing~\ref{listing:views}).
 It is very important that the agent receiving information from different users not merge the information that was destined to different users, or else information leakage will severely reduce the trust other agents have in that server $A$.
@@
 
-Secondly, Whenever the Origin Server needs to act on behalf of $U_1$ to a remote server $R$ it will need to open a new TLS connection to that server using the certificate $C_{u1}$ for that user.
+Secondly, whenever the Origin Server needs to act as $U_1$ to a remote server $R$ it will need to open a new TLS connection to that server using the certificate $C_{u1}$ for that user.
 This could require $N$ parallel connections to the same server $S$. 
-Opening TLS connections is somewhat expensive: it requires opening up a new TCP connection, starting an expensive asymmetrick key cryptographic handshake. 
+Opening TLS connections is somewhat expensive: it requires opening up a new TCP connection and starting an expensive asymmetrick key cryptographic handshake. 
 For small numbers of N this can be defended, but as N becomes large the inefficiency this could create between two
@@
 It is possible for any number of software agents to act AS the user by creating themselves a public key as described above.
-This does require a very strong trust relation to exist between the agent acting as the user and the user herself, as itthe two will be mostly indistinguishable in the linked web of trust. 
+This does require a very strong trust relation to exist between the agent acting as the user and the user herself, as the two will be mostly indistinguishable in the linked web of trust. 
 This method also becomes inefficient the greater the number of different users  an agent is working for.
@@
 That was an easy access control rule for the Capulet Freedbom Box to make when the request was using the WebID protocol simipliciter, since there it would know via the WebID authentication process exactly which identity the user was making the request as.
+But if it is the Origin Server connecting to the Capulet Freedom Box, identified as their Montague Origin Server, then what representation should the Capulet FB return? 
+Should it return the reduced version available to Lord Montague?
+Or should it return the more complete version available to Romeo and his close friends?
 
-The proposal here is for the Origin-Server to add to each HTTP request (made over TLS) an On-Behalf-Of header:
+The proposal here is for the Origin Server to add to each HTTP request (made over TLS) an On-Behalf-Of header identifying the user on behalf of which the request is being made with that user's WebID.
 
@@
 https://montague.net/romeo would then be able to accept that since the requesting server could in any case act as Romeo whenever it chose to do so, this protocol making exchange between the Montague and Capulet housholds more efficient without making it less secure, this be justification enough for it (the capulet freedom box) to  serve the representation that Romeo would have received had he connected to the server directly.
-We will argue further down that this is very similar to the way CORS deals with access control, namely by adding a header to a request to clearify what agent is making the request.
+We will argue further down that this is very similar to the way CORS deals with access control, namely by adding a header to a request to clarify what agent is making the request.
 
@@
 able to sepecify for each request on behalf of whome it is making it.
-The Montague Freedom Box could make a request to the capulet Freedom Box On-Behalf-Of Romeo, a few milliseconds later On-Behalf-Of Lord Capulet, and so on...
+The Montague Freedom Box could make a request to the capulet Freedom Box On-Behalf-Of Romeo, a few milliseconds later On-Behalf-Of Lord Montague, and so on...
 Again as explained in the previous section is is the responsibility of the Montague Freedom Box to keep these inforation seperate, and act with secrecy whenever it is acting on behalf of one or the other of the users.
-As such it's role is not unlike the role of Friar Laurence in the play: dedication to people's private matters requires tact and secrecy.
+As such it's role is not unlike the role of Friar Laurence in the play - dedication to people's private matters requires tact and secrecy.
 

### 2012-08-04 paper.tex
clear up header, upgrade reqs, add intro to sec 3.

--- 2012-08-04 paper.tex
@@
 \usepackage{printlen} % Print lengths using specified units. 
-%\usepackage{hyperref}
 \usepackage{booktabs}
 \usepackage[utf8]{inputenc} % Umlaute üöä auch normal benutzen und nicht maskieren
-\usepackage{color}
 % http://www.ctan.org/tex-archive/fonts/ps-type1/cm-super/
@@
 \usepackage{listings}
-\usepackage{subfig}
-\usepackage{printlen} % Print lengths using specified units.
-\usepackage{booktabs}
-%\usepackage[textsize=tiny]{todonotes}
-\usepackage{todonotes}
+\usepackage[textsize=footnotesize]{todonotes}
 
@@
 The rest of the paper is organized in the following way:
-\autoref{sec:req} describes the usage scenario and additional requirements which we had in mind for our solution,
+\autoref{sec:req} describes preliminary requirements which we had in mind for our solution,
 \autoref{sec:spec} goes into detail with the WebID specification and adds support for authorization delegation,
@@
 
-\section{Requirements}\label{sec:req}
+\section{Preliminary Requirements}\label{sec:req}
 
-\todo{is this section really needed? It seems mostly to repeat the previous section, and the next one, while loosting the thread
-of the questioning}
+%\todo{is this section really needed? It seems mostly to repeat the previous section, and the next one, while loosing the thread of the questioning}
 
-This section describes several usage scenarios requiring access delegation which can not be solved efficiently with the standard WebID authentication protocol.
-In addition to that, we list derived implementation requirements.
+%This section describes several usage scenarios requiring access delegation which can not be solved efficiently with the standard WebID authentication protocol.
+%In addition to that, we list derived implementation requirements.
 
-%\subsection{Basic Use-Cases for Access Delegation} \label{sec:usecases}
+%%\subsection{Basic Use-Cases for Access Delegation} \label{sec:usecases}
 
-%\subsubsection{Personal Devices and Applications}
+%%\subsubsection{Personal Devices and Applications}
 
-Currently, the default usage intention for WebIDs consists of browser-based authentication scenarios.
-This is an important use-case and should be of special interest since we use the World Wide Web not only through browsers but also through other applications as well as other application on other devices such as smartphones, tablets and freedomboxes\footnote{\url{https://freedomboxfoundation.org/}}.
-In a typical every day usage scenario, we use feed readers and social network clients hand in hand with web browsers.
-All these applications act in the name of their users and fetch and manipulate resources in a way as if it were done by the users themselves and with her browser.
-These applications provide their services to one user only and also run on a device which is commonly accessed by one user only (e.g. a smartphone).
-This class of \textit{private applications} is similar to browsers and can be seen as an extension of the user himself, as argued by Andy Clark and David Chalmers ~\cite{clark-a-1998-7-a}.
+%Currently, the default usage intention for WebIDs consists of browser-based authentication scenarios.
+%This is an important use-case and should be of special interest since we use the World Wide Web not only through browsers but also through other applications as well as other application on other devices such as smartphones, tablets and freedomboxes\footnote{\url{https://freedomboxfoundation.org/}}.
+%In a typical every day usage scenario, we use feed readers and social network clients hand in hand with web browsers.
+%All these applications act in the name of their users and fetch and manipulate resources in a way as if it were done by the users themselves and with her browser.
+%These applications provide their services to one user only and also run on a device which is commonly accessed by one user only (e.g. a smartphone).
+%This class of \textit{private applications} is similar to browsers and can be seen as an extension of the user himself, as argued by Andy Clark and David Chalmers ~\cite{clark-a-1998-7-a}.
 
-As a slightly different case, we can identify the class of \textit{service applications}.
-These applications also manipulate resources in the name of the user but they do this for more than one user.
-These services are hosted by a third party e.g. not by the user itself, nor by the owner of the protected resource where our user has an interest in.
-In addition to that, we argue that the level of trust which is given by a user is lower than to an application which runs on a personal device and can be turned off by herself.
-A typical application domain for this class of applications is the Social Web, and more specifically, the distributed and semantic Social Web.
-In this infrastructure, multiple services such as photo sharing, recipe management or todo lists create and manipulate artefacts like notes, comments and images and spin a data network based on a Linked Data infrastructure and shared vocabularies~\cite{tramp-s-2012--a}.
+%As a slightly different case, we can identify the class of \textit{service applications}.
+%These applications also manipulate resources in the name of the user but they do this for more than one user.
+%These services are hosted by a third party e.g. not by the user itself, nor by the owner of the protected resource where our user has an interest in.
+%In addition to that, we argue that the level of trust which is given by a user is lower than to an application which runs on a personal device and can be turned off by herself.
+%A typical application domain for this class of applications is the Social Web, and more specifically, the distributed and semantic Social Web.
+%In this infrastructure, multiple services such as photo sharing, recipe management or todo lists create and manipulate artefacts like notes, comments and images and spin a data network based on a Linked Data infrastructure and shared vocabularies~\cite{tramp-s-2012--a}.
 
-In this paper will show that this class of service applications can not handle access delegation efficiently without an extension to the protocol such as the one we propose.
+%In this paper will show that this class of service applications can not handle access delegation efficiently without an extension to the protocol such as the one we propose.
 
@@
 
-Based on this usage scenario and additional preliminary considerations, we issue the following implementation relevant requirements for an access delegation solution based on the WebID authentication protocol.
-We have identified the following roles being part of the access delegation process:
+Based on the introductory usage scenario from the previous section as well as additional preliminary considerations, we issue the following implementation relevant requirements for an access delegation solution based on the WebID authentication protocol.
+
+Beside that, we have identified the following roles being part of the access delegation process:
 \begin{enumerate}
@@
 \end{enumerate}
-In the following requirements list, we use both terms consequently to avoid confusion.
+We use both terms consequently to avoid confusion.
 
@@
 Delegation should not be handled by camouflaging an request of an agent in the sense that this request is indistinguishable from a named agent request.
-A secretary agent should use its own certificate and it should be identified and described by its own WebID profile.
-The motivation for this is twofold.
-Firstly, it allows resource guards to permit or deny requests based on this information.
-Secondly, applications which are secretary for many different named agents do not need to switch their certificate between requests.
+A secretary agent should use its own certificate (see efficency requirement) and it should be identified and described by its own WebID profile.
+The motivation for this is variously.
+\begin{itemize}
+    \item It allows resource guards to permit or deny requests based on this information.
+    \item Applications which are secretary for many different named agents do not need to switch their certificate between requests.
 Also they do not need to handle hundreds of different keys.
+    \item It allows for describing access control rules and the relation of a secretary agent to its named agent.
+Without a secretary WebID, this would not be possible.
+\end{itemize}
 
 \subsubsection{Easy to use}
-The one and only place to describe which secretary agents are allowed to operate as a named agent should be the WebID profile itself.
+The one and only place to describe which secretary agents are allowed to operate as a named agent should be the WebID profile itself or another Linked Data available document.
 To grant delegated access to a secretary agent, no other actions than simply adding triples to the WebID profile should be needed.
@@
 
-\subsubsection{Linked Data and Read Write Web integration}
-
-The solution we try to architect aims to enhance the communication for consumption and modification of Linked Data esp. from the applications point of view.
-This means, that existing Linked Data as well as Read-Write-Web principles should not be violated by the architecture.
-\todo{what does rww means here?}
+%\subsubsection{Linked Data and Read Write Web integration}
+%The solution we try to architect aims to enhance the communication for consumption and modification of Linked Data esp. from the applications point of view.
+%This means, that existing Linked Data as well as Read-Write-Web principles should not be violated by the architecture.
+%\todo{what does rww means here?}
 
 \subsubsection{Minimal protocol footprint}
+%In addition to the integration requirement
+We argue that a minimal protocol footprint should be achieved to allow a wide adoption of the solution.
+This includes the requirement to not add an additional service to the authentication process than using the existing ones.
+This also shifts the responsibility for an access control decision from a service to a machine readable document.
+We believe that this is a crucial feature of Linked Data in general.
 
-In addition to the integration requirement, we argue that a minimal protocol footprint should be achieved to allow a wide adoption of the extension.
-This includes the requirement to not add an additional service to the process of authentication than using the existing ones.
+\subsubsection{Efficiency}
+Finally, we have in mind that a proposed solution should scale in the sense of users and connections.
+In our context this means that an Social Web application should be able to act in the name of thousands of users without having scalability issues which conclude from WebID authentication.
 
-\todo{ST: add efficency requirement}
 %\subsubsection{No enforcement to reveal agent identities}\todo{maybe we kick this ...}
@@
 \section{Extending WebID for Access Delegation}\label{sec:spec}
+
+This section organized in multiple subsections which all discuss a possible solution for enabling access delegation but fail in one or more requirement or based on other problems (except the last subsection).
 

### 2012-08-04 paper.tex
fix intro to sec 3

@@
 
-This section organized in multiple subsections which all discuss a possible solution for enabling access delegation but fail in one or more requirement or based on other problems (except the last subsection).
+This section in organized in multiple subsections which all discuss a possible solution for enabling access delegation.
+All but the last solution fail in one or more requirement or based on other issues.
 

### 2012-08-04 paper.tex
filled in Section on secretary relation

--- 2012-08-04 paper.tex
@@
 
-The origin server acting as a client on behalf of a user can then be thought of as a keep of secrets for that user.
+The origin server acting as a client on behalf of a user can then be thought of as a keeper of secrets for that user.
 It should know how to distinguish what remote servers tell it when it is acting on behalf of one user, from what a remote server tells it when it is acting on behalf of another user.
@@
 
-If we now identify the secretary that can act on behalf of a user we can generalise the protocol somewhat.
-When the server authenticates as a secretary to a remote server it can use its own WebID.
+If we now identify with a WebID the secretary that can act on behalf of a user, we can generalise the protocol somewhat.
+That is, when an agent - such as the Montague Freedom Box Laurence with WebID \lstinline|<http://montague.net/fb#laurence>| - authenticates to a remote server it can use its own WebID. 
+This would allow the Agent to have its own public key, and so for a compromise of the client public key not to affect the server public key.
+
 But how would the remote server know that it can trust that secretary to be acting on behalf of a particular user?
-It can no longer just compare the TLS keys.
-Instead it can see if the user that the secretary is acting on behalf of has stated clearly that that agent is its secretary.
-This can be discovered by checking out the profile... \todo{fill out the details here}
+It can no longer just compare the TLS keys of the requesting agent to see if it comes from the same Origin Server.
+We need to make this relation explicity by use of a special RDF relation provisionally called \lstinline|cert:secretary|\footnote{which we will provisionally place
+in the cert: namespace, though it may be more appropriately placed in the auth: namespace}
+
+\lstinputlisting[
+    name=schema,style=turtle,float=htb,label=listing:schema,
+    basicstyle=\ttfamily\scriptsize,
+    caption={Schema description of the delegation property},
+]{Listings/schema.ttl}
+
+The remote server can then verify that the identified agent ( Laurence in the example ), is the secretary of the agent he wishes to act on behalf of (as sepecified in the \lstinline|On-Behalf-Of| header , by dereferencing that users Profile and verifying that the user specifies the \lstinline|cert:secretary| relation there, as it would if Romeo had the foaf profiles as shown in Listing \ref{listing:webid1}
+
+\lstinputlisting[
+    firstline=4,lastline=14,name=webid,style=turtle,float=htb,label=listing:webid1,
+    basicstyle=\ttfamily\scriptsize,
+    caption={Minimal WebID profile including a public key and a secretary relation}
+]{Listings/webid1.ttl}
 
@@
 
-\lstinputlisting[
-    lastline=13,name=webid,style=turtle,float=htb,label=listing:webid1,
-    basicstyle=\ttfamily\scriptsize,
-    caption={Minimal WebID profile including a public key and a secretary relation}
-]{Listings/webid1.ttl}
-
 %\lstinputlisting[
@@
 %]{Listings/webid1.ttl}\todo{A:why add the public key of the agent here? (revocation issues)}
-
-\lstinputlisting[
-    name=schema,style=turtle,float=htb,label=listing:schema,
-    basicstyle=\ttfamily\scriptsize,
-    caption={Schema description of the delegation property},
-]{Listings/schema.ttl}
 

### 2012-08-04 paper.tex
niceup oauth section

@@
 \subsection{OAuth}
-\todo{If we were to implement a secreteary like feature using OAuth what would it look like? what would the differences be?}
+%\todo{If we were to implement a secreteary like feature using OAuth what would it look like? what would the differences be?}
 
-OAuth~2.0\footnote{http://tools.ietf.org/html/draft-ietf-oauth-v2} is the latest version of the OAuth protocol, which is being presented as an access delegation protocol, enabling users to grant access to third-party services to their personal resources, instead of sharing their passwords with those third-party services.
-OAuth includes two main parts: obtaining an access token by asking the resource owner (i.e.
-the user) to grant access, and then using the tokens to access protected resources.
+OAuth~2.0\footnote{\url{http://tools.ietf.org/html/draft-ietf-oauth-v2}} is the latest version of the OAuth protocol, which is being presented as an access delegation protocol, enabling users to grant access to third-party services to their personal resources, instead of sharing their passwords with those third-party services.
+OAuth includes two main parts: obtaining an access token by asking the resource owner (i.e. the user) to grant access, and then using the tokens to access protected resources.
 
@@
 Ann has a Twitter account.
-One day she decides to support her favourite project by using Flattr\footnote{http://flattr.com/}, a micropayment service.
+One day she decides to support her favourite project by using Flattr\footnote{\url{http://flattr.com/}}, a micropayment service.
 Since she would rather not create a new account, Flattr offers her the possibility of using her Twitter account to log into Flattr.
 After clicking the "Login using Twitter" button, she is redirected to Twitter's login page where she inputs her username and password.
-Once authenticated, Twitter informs her that Flattr.com would like to access her personal information (e.g.
-name, picture, etc.).
+Once authenticated, Twitter informs her that Flattr.com would like to access her personal information (e.g. name, picture, etc.).
 She can now choose if she wants to grant or deny to Flattr access to her Twitter account information.
-Once she accepts, she is redirected back to Flattr.com where she notices that she is now authenticated, and her Twitter username, full name and picture now appear in Flattr.
+Once she accepts, she is redirected back to \url{Flattr.com} where she notices that she is now authenticated, and her Twitter username, full name and picture now appear in Flattr.
 

### 2012-08-04 paper.tex
add notes from telco and use principal agent now

@@
 %\textit{Access Delegation} is a relation between two WebID resources.
-%The relation describes, under which circumstances a secretary agent has access to a certain resource under the same constraints as the named agent.
-%The secretary agent declares to act in the name of the named agent.
+%The relation describes, under which circumstances a secretary agent has access to a certain resource under the same constraints as the principal agent.
+%The secretary agent declares to act in the name of the principal agent.
 
@@
 %This solution has two drawbacks: (1) the users certificate is burned after the vacation and she needs to create a new one, (2) a resource guard can not distinguish between the user and the vacation replacement user, which allows for abuse.
-%In this context, the named agent is the employee which is on holiday and her vacation replacement is the secretary agent.
+%In this context, the principal agent is the employee which is on holiday and her vacation replacement is the secretary agent.
 
@@
 
-%In order to allow this, we define the group as the named agent and all group members as its secretary agents.
+%In order to allow this, we define the group as the principal agent and all group members as its secretary agents.
 %An alternative could be to share one single group certificate with all members or to create a group certificate for each member and describe all public keys in the group WebID.
 %Again, these solutions have different drawbacks: (1) a shared certificate needs to be updated each time a user leaves the group, (2) multiple group certificates for each user does not allow for distinguishing which user accessed the resource, which allows for abuse.
-%In this context, the group is the named agent and all current group members are secretary agents.\todo{A: not sure I agree (see source)}%the group is not an entity, therefore it cannot take actions by iteself.
+%In this context, the group is the principal agent and all current group members are secretary agents.\todo{A: not sure I agree (see source)}%the group is not an entity, therefore it cannot take actions by iteself.
 Actions are always performed by users, as part of the group.
@@
 
-%In this context, the role is the named agent and the current role owner is the secretary agent.
+%In this context, the role is the principal agent and the current role owner is the secretary agent.
 
@@
 This agent actually requests some resources and tries to do that on behalf of someone.
-    \item The \textit{named agent} is the agent which is represented by the secretary.
-This agent does not have an active role in the request but is named as the origin of the activity.
+    \item The \textit{principal agent} is the agent which is represented by the secretary.
+This agent does not have an active role in the request but is principal as the origin of the activity.
 \end{enumerate}
@@
 
-\subsubsection{Distinguish secretary agents from named agents}
-Delegation should not be handled by camouflaging an request of an agent in the sense that this request is indistinguishable from a named agent request.
+\subsubsection{Distinguish secretary agents from principal agents}
+Delegation should not be handled by camouflaging an request of an agent in the sense that this request is indistinguishable from a principal agent request.
 A secretary agent should use its own certificate (see efficency requirement) and it should be identified and described by its own WebID profile.
@@
     \item It allows resource guards to permit or deny requests based on this information.
-    \item Applications which are secretary for many different named agents do not need to switch their certificate between requests.
+    \item Applications which are secretary for many different principal agents do not need to switch their certificate between requests.
 Also they do not need to handle hundreds of different keys.
-    \item It allows for describing access control rules and the relation of a secretary agent to its named agent.
+    \item It allows for describing access control rules and the relation of a secretary agent to its principal agent.
 Without a secretary WebID, this would not be possible.
@@
 \subsubsection{Easy to use}
-The one and only place to describe which secretary agents are allowed to operate as a named agent should be the WebID profile itself or another Linked Data available document.
+The one and only place to describe which secretary agents are allowed to operate as a principal agent should be the WebID profile itself or another Linked Data available document.
 To grant delegated access to a secretary agent, no other actions than simply adding triples to the WebID profile should be needed.
@@
 organisations may be a serious drawback.
-\todo{calculate how inefficient this is, and at what size of network this starts really become problematic}
+%\todo{calculate how inefficient this is, and at what size of network this starts really become problematic}
 \todo{ST: add disadvantages according to the requirements (identity)}
@@
 \begin{itemize}
-    \item The requesting agent (the secretary) claims a request as requested in the name of a named agent (see point 2).
+    \item The requesting agent (the secretary) claims a request as requested in the name of a principal agent (see point 2).
         This adds a HTTP request header to the specification.
@@
         This adds additional verification rules to the specification.
-    \item The named agent (Bob) can declare any relation to his secretary agents in his WebID profile.
+    \item The principal agent (Bob) can declare any relation to his secretary agents in his WebID profile.
         This adds a vocabulary for describing access delegation to the specification.
@@
 OntoWiki~\cite{auer-s-2006-736-a} is a web application, which allows for publication, exploration as well as manipulation of arbitrary RDF knowledge bases in distributed scenarios.
-We refer to it as a data wiki, since it adopts the wiki philosophy (ease of editing, tracking of changes, integrated dicscussions) on the one hand, while focussing on structured information on the other hand.
+We refer to it as a data wiki, since it adopts the wiki philosophy (ease of editing, tracking of changes, integrated discussions) on the one hand, while focussing on structured information on the other hand.
 Furthermore OntoWiki is an adaptable application framework, which supports the creation of Linked Data based applications on the web~\cite{heino-n-2009-61-a}.
@@
 
-\subsection{OAuth}
+%\subsection{OAuth}
 %\todo{If we were to implement a secreteary like feature using OAuth what would it look like? what would the differences be?}
@@
 Ann has a Twitter account.
-One day she decides to support her favourite project by using Flattr\footnote{\url{http://flattr.com/}}, a micropayment service.
+One day she decides to support her favourite project by using Flattr\footnote{\url{http://flattr.com/}}, a micro payment service.
 Since she would rather not create a new account, Flattr offers her the possibility of using her Twitter account to log into Flattr.
-After clicking the "Login using Twitter" button, she is redirected to Twitter's login page where she inputs her username and password.
-Once authenticated, Twitter informs her that Flattr.com would like to access her personal information (e.g. name, picture, etc.).
+After clicking the "Login using Twitter" button, she is redirected to Twitter's login page where she inputs her user name and password.
+Once authenticated, Twitter informs her that Flattr would like to access her personal information (e.g. name, picture, etc.).
 She can now choose if she wants to grant or deny to Flattr access to her Twitter account information.
-Once she accepts, she is redirected back to \url{Flattr.com} where she notices that she is now authenticated, and her Twitter username, full name and picture now appear in Flattr.
+Once she accepts, she is redirected back to Flattr where she notices that she is now authenticated, and her Twitter user name, full name and picture now appear in Flattr.
 
@@
 
+\todo{Add a small section which emphasizes the differences}
 The conclusion is that OAuth is used to \textit{provide access for external services to local user resources} without disclosing the user's credentials.
@@
 
-\subsection{Cross Origin Resource Sharing (CORS)}
-\todo{Henry Story: Compare to CORS in the context of Consuming Linked Data}
+%\subsection{Cross Origin Resource Sharing (CORS)}
+%\todo{Henry Story: Compare to CORS in the context of Consuming Linked Data}
 
@@
 
+\todo{Nice up wording esp. our terms and language}
 In this paper we discussed different ways how an agent, such as a Social Web application, can act on behalf of a user and request as well as manipulate resources on the Web in the name this user.

### 2012-08-04 paper.tex
upgrade OAuth section

@@
 %\subsection{OAuth}
-%\todo{If we were to implement a secreteary like feature using OAuth what would it look like? what would the differences be?}
-
-OAuth~2.0\footnote{\url{http://tools.ietf.org/html/draft-ietf-oauth-v2}} is the latest version of the OAuth protocol, which is being presented as an access delegation protocol, enabling users to grant access to third-party services to their personal resources, instead of sharing their passwords with those third-party services.
+OAuth~2.0~\cite{hardt-d-2012--a} is the latest version of the OAuth protocol, which is being presented as an access delegation protocol, enabling users to grant access to third-party services to their personal resources, instead of sharing their passwords with those third-party services.
 OAuth includes two main parts: obtaining an access token by asking the resource owner (i.e. the user) to grant access, and then using the tokens to access protected resources.
@@
 Ann has a Twitter account.
-One day she decides to support her favourite project by using Flattr\footnote{\url{http://flattr.com/}}, a micro payment service.
+One day she decides to support her favourite project by using Flattr\footnote{\url{http://flattr.com}}, a micro payment service.
 Since she would rather not create a new account, Flattr offers her the possibility of using her Twitter account to log into Flattr.
@@
 
-Even if OAuth provides authentication as a by-product of having the resource owner authorize a third-party client to his/her resource server, its main focus is on resource authorization rather than on federated identity.
+Even if OAuth provides authentication as a by-product of having the resource owner authorize a third-party client to her resource server, its main focus is on resource authorization rather than on federated identity.
 
-\todo{Add a small section which emphasizes the differences}
 The conclusion is that OAuth is used to \textit{provide access for external services to local user resources} without disclosing the user's credentials.
-On the other hand, in WebID access delegation, the secretary is used to \textit{gain access to external resources} on behalf of a given user.
+%On the other hand, in WebID access delegation, the secretary is used to \textit{gain access to external resources} on behalf of a given user.
+Or in other words: OAuth is used to allow an agent to \textit{request a users resources} while WebID delegation is used to allow an agent to \textit{request resources the user could request herself}.
 

### 2012-08-04 paper.tex
upgrade abstract

@@
 
+\hyphenation{Web-ID}
+
 \begin{document}
@@
 The WebID protocol enables the global identification of agents in a distributed manner by combining asymmetric cryptography and Linked Data.
-But in order for such a server to decide whether access should be granted or denied to a particular WebID, it (the web server) may need to retrieve other profiles and linked resources in order to work out if the requesting agent is member of the authorized group ( eg: is a friends of a friend (FOAF) of the resource owner ).
-If these linked resources ( e.g. FOAF profiles ) are required to be publicly available for the server to access it, then this would be a major privacy limitiation on a linked social network.
-In this paper we explore the different ways an agent can act as a user, and we propose an extension to the WebID protocol which allows for delegation of access authorization from a WebID to a third party, e.g.
+But in order for such a server to decide whether access should be granted or denied to a particular WebID, the web server may need to retrieve other profiles and linked resources to work out e.g.
+if the requesting agent is member of an authorized group (e.g.
+is a friend of a friend (FOAF) of the resource owner).
+If these linked resources (e.g. FOAF profiles) are required to be publicly available for the server to access it, then this would be a major privacy limitation on a linked Social Network.
+In this paper we explore different ways how an agent can act as a user as well as we propose an extension to the WebID protocol which allows for delegation of access authorization from a WebID to a third party, e.g.
 allowing a server to be able to act on behalf of its users.

### 2012-08-04 paper.tex
added CORS section

--- 2012-08-04 paper.tex
@@
 
-%\subsection{Cross Origin Resource Sharing (CORS)}
-%\todo{Henry Story: Compare to CORS in the context of Consuming Linked Data}
+\subsection{Cross Origin Resource Sharing (CORS)}
+
+In this paper we proposed to add an \lstinline|On-Behalf-Of| header to each HTTP request made by a \textit{secretary} in order to be able to identify the \textit{principal} she is working for in that particular request.
+This is quite a major semantic addition to HTTP, but for which there is a widely adopted precedent, namely CORS, the Cross Origin Resource Sharing spec at the w3c \footnote{\url{http://www.w3.org/TR/cors/}}.
+CORS  identifies the remote \textit{principal} with an \lstinline|Origin| header, and uses any HTTP authentication method to identify the \textit{secretary} which in this case is the browser.
+
+Let us look at this in more detail.
+CORS has two agents, one acting on behalf of the other, and these are: 
+\begin{itemize}
+  \item The Browser: it is in the role of the \textit{secretary} as it is acting on behalf of javascript agents - the \textit{principals} - that execute themselves in cpu space provided by the browers.
+  \item JavaScript code: found on the internet and identified by the Origin Server that hosted the javascript.
+This javascript agent is in the role of the \textit{principal}, making a request to the Browser for some resources, but unable to make the request directly.
+\end{itemize}
+
+The use cases for CORS is slightly different to the one for our delegation proposal. 
+The use cases we have proposed are ones where the \textit{secretary} acts on behalf of a user, it is very much as an independent agent, working at its own pace, such as fetching resources on the internet as needed, responding to pingback requests, ...
+In CORS the browser is acting directly on a request by a JavaScript agent to fetch a resource.
+The browser here is using its own identity credentials when connecting to remote servers - such as a bank for example - and it needs to alert the remote service that the request it is making comes from a particular agent.
+The browser also needs to make sure the remote server understands this, especially when doing something that requires authentication, so that it can leave the remote server to evaluate the strenght of the Javascript trust relation.
+In CORS the remote site initially trusts the \textit{secretary/user agent}, but it is being told that it needs to take into account that the request is not directly from the user but from a remote \textit{principal} .
+In the Delegation use case we are discussing the remote site trusts the \textit{principal}, but may not be aware of the \textit{secretary}.
+
+Furthermore the identification of the agent in the \lstinline|On-Behalf-Of| header is much more precise.
+Combined with the ability of the secretary to also identify herself with a WebID, both of these make it possible for the trust relation between the user and the secretary to be made explicit, a situation which the vagueness of the \lstinline|Origin| identity of the \textit{principal} make a lot more difficult.
+
+It is a topic of further research to evaluate in which circumstances it is important for the delegation secretary we have been discussing to also make sure that the remote server is aware that the connection being made is \lstinline|On-Behalf-Of| the specified \textit{principal}.
+For otherwise it is quite possible that the \textit{secretary} itself be made liable for the actions of a remote agent on behalf of which it is acting.
 

### 2012-08-04 paper.tex
shorten implementation

@@
 
-\begin{figure*}[htb]
-  \centering
-  \includegraphics[width=\textwidth]{ontowiki}
-  \caption{An external and thus imported WebID profile shown in a generic OntoWiki view, which can be used to visualize arbitrary RDF resources.}
-  \label{fig:ontowiki}
-\end{figure*}
+%\begin{figure*}[htb]
+  %\centering
+  %\includegraphics[width=\textwidth]{ontowiki}
+  %\caption{An external and thus imported WebID profile shown in a generic OntoWiki view, which can be used to visualize arbitrary RDF resources.}
+  %\label{fig:ontowiki}
+%\end{figure*}
 
-\paragraph{Data import}
-A first use-case for WebID access delegation within OntoWiki arises from an important functionality within OntoWiki, namely import of external data.
-Figure \ref{fig:ontowiki} shows a WebID profile that was imported via the Linked Data principles into a local knowledge base.
+%\paragraph{Data import}
+A first use-case for WebID access delegation within OntoWiki arises from an important functionality within OntoWiki, namely \textit{import of external data}.
+%Figure \ref{fig:ontowiki} shows a WebID profile that was imported via the Linked Data principles into a local knowledge base.
 Since WebID profiles can contain personal information that is in need of protection, access to such data should be restricted with the WebID protocol.
@@
 
-\paragraph{Semantic Pingback}
-Another use-case where access delegation can be employed is within the Semantic Pingback protocol~\cite{tramp-s-2010--b}.
+%\paragraph{Semantic Pingback}
+Another use-case where access delegation can be employed is within the \textit{Semantic Pingback} protocol~\cite{tramp-s-2010--b}.
 With Semantic Pingback owners of resources can be notified when for example a link to such a resource is created elsewhere on the web.

### 2012-08-04 paper.tex
shorten impl. and oauth

@@
 
-\subsubsection{Distinguish secretary agents from principal agents}
+\paragraph{Distinguish secretary agents from principal agents}
 Delegation should not be handled by camouflaging an request of an agent in the sense that this request is indistinguishable from a principal agent request.
@@
 The motivation for this is variously.
-\begin{itemize}
-    \item It allows resource guards to permit or deny requests based on this information.
-    \item Applications which are secretary for many different principal agents do not need to switch their certificate between requests.
+(1) It allows resource guards to permit or deny requests based on this information.
+(2) Applications which are secretary for many different principal agents do not need to switch their certificate between requests.
 Also they do not need to handle hundreds of different keys.
-    \item It allows for describing access control rules and the relation of a secretary agent to its principal agent.
+(3) It allows for describing access control rules and the relation of a secretary agent to its principal agent.
 Without a secretary WebID, this would not be possible.
-\end{itemize}
 
-\subsubsection{Easy to use}
+\paragraph{Easy to use}
 The one and only place to describe which secretary agents are allowed to operate as a principal agent should be the WebID profile itself or another Linked Data available document.
@@
 
-\subsubsection{Minimal protocol footprint}
+\paragraph{Minimal protocol footprint}
 %In addition to the integration requirement
@@
 
-\subsubsection{Efficiency}
+\paragraph{Efficiency}
 Finally, we have in mind that a proposed solution should scale in the sense of users and connections.
@@
 
-\subsection{MyProfile}
-
-MyProfile\footnote{\url{http://myprofile-project.org/}} intends to provide a solution for managing the numerous accounts and profiles that users have on the Web.
+\textbf{MyProfile}\footnote{\url{http://myprofile-project.org/}}
+intends to provide a solution for managing the numerous accounts and profiles that users have on the Web.
 Its main purpose is to provide a unified user account, or simply \textit{user profile}, which as opposed to current \textit{silo} profiles, would really be under the user's control, on a device located within the user physical reach.
 
-\begin{figure*}[htb]
-  \centering
-  \includegraphics[width=\textwidth]{myprofile}
-  \caption{The MyProfile dashboard visualizes information from different sources fetched by the MyProfile server as a secretary for its users}
-  \label{fig:myprofile}
-\end{figure*}
+%\begin{figure*}[htb]
+  %\centering
+  %\includegraphics[width=\textwidth]{myprofile}
+  %\caption{The MyProfile dashboard visualizes information from different sources fetched by the MyProfile server as a secretary for its users}
+  %\label{fig:myprofile}
+%\end{figure*}
 
@@
 
-\subsection{OntoWiki}
-OntoWiki~\cite{auer-s-2006-736-a} is a web application, which allows for publication, exploration as well as manipulation of arbitrary RDF knowledge bases in distributed scenarios.
+\textbf{OntoWiki}
+\cite{auer-s-2006-736-a} is a web application, which allows for publication, exploration as well as manipulation of arbitrary RDF knowledge bases in distributed scenarios.
 We refer to it as a data wiki, since it adopts the wiki philosophy (ease of editing, tracking of changes, integrated discussions) on the one hand, while focussing on structured information on the other hand.
@@
 OAuth includes two main parts: obtaining an access token by asking the resource owner (i.e. the user) to grant access, and then using the tokens to access protected resources. 
-
-Here is a typical example of using OAuth. 
-Ann has a Twitter account.
-One day she decides to support her favourite project by using Flattr\footnote{\url{http://flattr.com}}, a micro payment service.
-Since she would rather not create a new account, Flattr offers her the possibility of using her Twitter account to log into Flattr.
-After clicking the "Login using Twitter" button, she is redirected to Twitter's login page where she inputs her user name and password.
-Once authenticated, Twitter informs her that Flattr would like to access her personal information (e.g. name, picture, etc.).
-She can now choose if she wants to grant or deny to Flattr access to her Twitter account information.
-Once she accepts, she is redirected back to Flattr where she notices that she is now authenticated, and her Twitter user name, full name and picture now appear in Flattr.
-
+%Here is a typical example of using OAuth. 
+%Ann has a Twitter account.
+%One day she decides to support her favourite project by using Flattr\footnote{\url{http://flattr.com}}, a micro payment service.
+%Since she would rather not create a new account, Flattr offers her the possibility of using her Twitter account to log into Flattr.
+%After clicking the "Login using Twitter" button, she is redirected to Twitter's login page where she inputs her user name and password.
+%Once authenticated, Twitter informs her that Flattr would like to access her personal information (e.g. name, picture, etc.).
+%She can now choose if she wants to grant or deny to Flattr access to her Twitter account information.
+%Once she accepts, she is redirected back to Flattr where she notices that she is now authenticated, and her Twitter user name, full name and picture now appear in Flattr.
 The advantage here is that Ann only had to use her Twitter credentials to log into Flattr.
 However, the disadvantage is that Flattr requires an existing trust relationship with Twitter, thus limiting the number of supported services.
-
 Even if OAuth provides authentication as a by-product of having the resource owner authorize a third-party client to her resource server, its main focus is on resource authorization rather than on federated identity.
-
 The conclusion is that OAuth is used to \textit{provide access for external services to local user resources} without disclosing the user's credentials.

### 2012-08-04 paper.tex
Modified CORS a little.

@@
 In this paper we proposed to add an \lstinline|On-Behalf-Of| header to each HTTP request made by a \textit{secretary} in order to be able to identify the \textit{principal} she is working for in that particular request.
-This is quite a major semantic addition to HTTP, but for which there is a widely adopted precedent, namely CORS, the Cross Origin Resource Sharing spec at the w3c \footnote{\url{http://www.w3.org/TR/cors/}}.
+This is quite a major semantic addition to HTTP, but for which there is a widely adopted precedent, namely CORS\footnote{\url{http://www.w3.org/TR/cors/}}, the Cross Origin Resource Sharing spec at the W3C.
 CORS identifies the remote \textit{principal} with an \lstinline|Origin| header, and uses any HTTP authentication method to identify the \textit{secretary} which in this case is the browser.
@@
 \begin{itemize}
-  \item The Browser: it is in the role of the \textit{secretary} as it is acting on behalf of javascript agents - the \textit{principals} - that execute themselves in cpu space provided by the browers.
-  \item JavaScript code: found on the internet and identified by the Origin Server that hosted the javascript.
-This javascript agent is in the role of the \textit{principal}, making a request to the Browser for some resources, but unable to make the request directly.
+  \item The Browser: it takes the role of the \textit{secretary} as it is acting on behalf of javascript agents - the \textit{principals}.
+  \item JavaScript code: hosted on the internet and identified by the Origin Server that hosted the javascript.
+This javascript agent requests resources from the Browser, but it is unable to do it directly.
 \end{itemize}
 
-The use cases for CORS is slightly different to the one for our delegation proposal. 
-The use cases we have proposed are ones where the \textit{secretary} acts on behalf of a user, it is very much as an independent agent, working at its own pace, such as fetching resources on the internet as needed, responding to pingback requests, ...
+The use cases for CORS are slightly different from the ones for our delegation proposal. 
+The use cases we have proposed are ones where the \textit{secretary} acts on behalf of a user, it is very much as an independent agent, working at its own pace, such as fetching resources on the internet as needed, responding to pingback requests, etc.
 In CORS the browser is acting directly on a request by a JavaScript agent to fetch a resource.
-The browser here is using its own identity credentials when connecting to remote servers - such as a bank for example - and it needs to alert the remote service that the request it is making comes from a particular agent.
-The browser also needs to make sure the remote server understands this, especially when doing something that requires authentication, so that it can leave the remote server to evaluate the strenght of the Javascript trust relation.
-In CORS the remote site initially trusts the \textit{secretary/user agent}, but it is being told that it needs to take into account that the request is not directly from the user but from a remote \textit{principal} .
-In the Delegation use case we are discussing the remote site trusts the \textit{principal}, but may not be aware of the \textit{secretary}.
+The browser here is using its own identity credentials when connecting to remote servers - such as a bank for example - and it needs to alert the remote service that the request originates from a particular agent.
+The browser also needs to make sure the remote server understands this, especially when doing something that requires authentication, to allow the remote server to evaluate the strength of the Javascript trust relation.
+In CORS the remote site initially trusts the \textit{secretary/user agent}, but it is being told that it needs to take into account that the request does not directly originated from the user but from a remote \textit{principal} .
+In the Section~\ref{sec:spec} use cases, the remote site trusts the \textit{principal}, but may not be aware of the \textit{secretary}.
 
-Furthermore the identification of the agent in the \lstinline|On-Behalf-Of| header is much more precise.
-Combined with the ability of the secretary to also identify herself with a WebID, both of these make it possible for the trust relation between the user and the secretary to be made explicit, a situation which the vagueness of the \lstinline|Origin| identity of the \textit{principal} make a lot more difficult.
+Furthermore, the identification of the agent in the proposed \lstinline|On-Behalf-Of| header is much more precise.
+Combined with the ability of the secretary to also identify herself with a WebID, both of these make it possible for the trust relation between the user and the secretary to be made explicit, a situation which the vagueness of the \lstinline|Origin| identity of the \textit{principal} makes a lot more difficult.
 
-It is a topic of further research to evaluate in which circumstances it is important for the delegation secretary we have been discussing to also make sure that the remote server is aware that the connection being made is \lstinline|On-Behalf-Of| the specified \textit{principal}.
-For otherwise it is quite possible that the \textit{secretary} itself be made liable for the actions of a remote agent on behalf of which it is acting.
+Further research involves evaluating in which circumstances it is important for the delegation secretary we have been discussing to also make sure that the remote server is aware that the connection being made is \lstinline|On-Behalf-Of| the specified \textit{principal}.
+Otherwise it is quite possible that the \textit{secretary} itself be made liable for the actions of a remote agent on behalf of whom it is acting.
 

### 2012-08-04 paper.tex
Shortened the CORS section a little.

@@
 The use cases for CORS are slightly different from the ones for our delegation proposal. 
-The use cases we have proposed are ones where the \textit{secretary} acts on behalf of a user, it is very much as an independent agent, working at its own pace, such as fetching resources on the internet as needed, responding to pingback requests, etc.
-In CORS the browser is acting directly on a request by a JavaScript agent to fetch a resource.
-The browser here is using its own identity credentials when connecting to remote servers - such as a bank for example - and it needs to alert the remote service that the request originates from a particular agent.
-The browser also needs to make sure the remote server understands this, especially when doing something that requires authentication, to allow the remote server to evaluate the strength of the Javascript trust relation.
-In CORS the remote site initially trusts the \textit{secretary/user agent}, but it is being told that it needs to take into account that the request does not directly originated from the user but from a remote \textit{principal} .
+In CORS the browser is using its own identity credentials when connecting to remote servers (e.g. a bank), as it needs to alert the remote service that the request originates from a particular agent.
+The browser also needs to make sure the remote server understands this, especially when authentication is required, to allow the remote server to evaluate the strength of the Javascript trust relation.
 In the Section~\ref{sec:spec} use cases, the remote site trusts the \textit{principal}, but may not be aware of the \textit{secretary}.
 
-Furthermore, the identification of the agent in the proposed \lstinline|On-Behalf-Of| header is much more precise.
-Combined with the ability of the secretary to also identify herself with a WebID, both of these make it possible for the trust relation between the user and the secretary to be made explicit, a situation which the vagueness of the \lstinline|Origin| identity of the \textit{principal} makes a lot more difficult.
-
-Further research involves evaluating in which circumstances it is important for the delegation secretary we have been discussing to also make sure that the remote server is aware that the connection being made is \lstinline|On-Behalf-Of| the specified \textit{principal}.
-Otherwise it is quite possible that the \textit{secretary} itself be made liable for the actions of a remote agent on behalf of whom it is acting.
+In our proposal, the identification of the agent in the \lstinline|On-Behalf-Of| header is much more precise.
+Combined with the ability of the secretary to also identify herself with a WebID, it builds an explicit trust relation between the user and the secretary, a situation in which the vagueness of the \lstinline|Origin| identity of the \textit{principal} is made a lot more difficult.
 

### 2012-08-04 paper.tex
upgrade 3.3

@@
 
-\todo{insert description of On-behalf-Of header (at least the importance of such a feature)}
+%\todo{insert description of On-behalf-Of header (at least the importance of such a feature)}
 
@@
 It can no longer just compare the TLS keys of the requesting agent to see if it comes from the same Origin Server.
-We need to make this relation explicity by use of a special RDF relation provisionally called \lstinline|cert:secretary|\footnote{which we will provisionally place
-in the cert: namespace, though it may be more appropriately placed in the auth: namespace}
+We need to make this relation explicity by use of a special RDF relation provisionally called \lstinline|cert:secretary|%
+\footnote{A object property with a domain and range as \lstinline|foaf:Agent| which we will provisionally place
+in the \lstinline|cert:| namespace, though it may be more appropriately placed in the \lstinline|auth:| namespace.}
 
-\lstinputlisting[
-    name=schema,style=turtle,float=htb,label=listing:schema,
-    basicstyle=\ttfamily\scriptsize,
-    caption={Schema description of the delegation property},
-]{Listings/schema.ttl}
+%\lstinputlisting[
+    %name=schema,style=turtle,float=htb,label=listing:schema,
+    %basicstyle=\ttfamily\scriptsize,
+    %caption={Schema description of the delegation property},
+%]{Listings/schema.ttl}
 
-The remote server can then verify that the identified agent ( Laurence in the example ), is the secretary of the agent he wishes to act on behalf of (as sepecified in the \lstinline|On-Behalf-Of| header , by dereferencing that users Profile and verifying that the user specifies the \lstinline|cert:secretary| relation there, as it would if Romeo had the foaf profiles as shown in Listing \ref{listing:webid1}
+The remote server can then verify that the identified agent is the secretary of the agent he wishes to act on behalf of (as sepecified in the \lstinline|On-Behalf-Of| header, by dereferencing that users profile and verifying that the user specifies the \lstinline|cert:secretary| relation there, as it would if Romeo had the foaf profiles as shown in Listing \ref{listing:webid1}.
 
@@
 ]{Listings/webid1.ttl}
-
-\autoref{fig:AuthSequence} depicts the process of a WebID authentication which is extended with the following components to allow access delegation:
-
-\begin{itemize}
-    \item The requesting agent (the secretary) claims a request as requested in the name of a principal agent (see point 2).
-        This adds a HTTP request header to the specification.
-    \item The WebID verifier needs to verify not only one but two different WebID incl. the relation between these two resources (see point 4).
-        This adds additional verification rules to the specification.
-    \item The principal agent (Bob) can declare any relation to his secretary agents in his WebID profile.
-        This adds a vocabulary for describing access delegation to the specification.
-\end{itemize}
 
@@
 
-The following enumeration describe each authentication step in detail but concentrates on the context of access delegation:
+%\autoref{fig:AuthSequence} depicts the process of a WebID authentication which is extended with the following components to allow access delegation:
+%\begin{itemize}
+    %\item The requesting agent (the secretary) claims a request as requested in the name of a principal agent (see point 2).
+        %This adds a HTTP request header to the specification.
+    %\item The WebID verifier needs to verify not only one but two different WebID incl. the relation between these two resources (see point 4).
+        %This adds additional verification rules to the specification.
+    %\item The principal agent (Bob) can declare any relation to his secretary agents in his WebID profile.
+        %This adds a vocabulary for describing access delegation to the specification.
+%\end{itemize}
+
+%\autoref{fig:AuthSequence} depicts the process of a WebID authentication which is extended with the following components to allow access delegation:
+The following enumeration describes each authentication step of \autoref{fig:AuthSequence} in detail but concentrates on the context of access delegation:
 
 \begin{enumerate}
-    \item Bob's secretary agent opens a TLS connection with the server of the protected resource.
-    \item Once TLS is set up, the HTTP request is sent to the server (e.g. a \verb!HTTP GET!) to consume or manipulate a resource.
-        Here our first addition comes into play, the HTTP request header to claim an request as a secretary.
+    \item[1] The secretary agent opens a TLS connection with the server of the protected resource.
+    \item[2]  Once TLS is set up, the HTTP request is sent to the server (e.g. a \verb!HTTP GET!) to consume or manipulate a resource.
+        Here our first addition comes into play, the HTTP request header \lstinline|On-Behalf-Of| to claim an request as a secretary.
         We assume that the guard intercepts this HTTP request, and requests for a client authentication (using the TLS service)
-    \item This authentication request is done using public key cryptography, sign a token with the guards private key and have the secretary send its certificate.
+    \item[3] This authentication request is done using public key cryptography, sign a token with the guards private key and have the secretary send its certificate.
         This is defined in the TLS protocol which is specified in \cite{dierks-t-2012--a} and its successive RFCs.
         At the end of this step, the secretaries certificate is handled back to the guard.
-    \item The guard ask the verification agent to verify the WebID is named in the certificate.
-
-        %The WebID Certificate is then passed on to the Guard with the proviso that the WebIDs still needs to be verified.
-    %The Guard then must ask the Verification Agent to verify that the WebIDs do identify the agent who knows the given public key.
-    %The WebID is verified by looking up the definition of the URL at its canonical location.
-This can be done by dereferencing it.
-The Verification Agent must extract the public key and all the URI entries contained in the Subject Alternative Name extension of the WebID Certificate.
-A WebID Certificate may contain multiple URI entries which are considered claimed WebIDs at this point, since they have not been verified.
-The Verification Agent may verify as many or as few WebIDs it has time for.
-It may do it in parallel and asynchronously.
-However that is done, a claimed WebIDs can only be considered verified if the following steps have been accomplished successfully:
-        %If the WebID Verifier does not have an up to date version of the WebID profile in the cache, then it must dereference the WebID using the canonical method for dereferencing a URL of that scheme.
-For an https://...
-WebID this would be done using the [HTTP-TLS] protocol.
-        %The returned representation is then transformed into an RDF graph as specified in Processing the WebID Profile
-        %That graph is then queried as explained in Querying the Graph. If the query succeeds, then that WebID is verified.
-    %With the set of verified WebIDs the Guard can then check its access control rules using information from the web and other information available to it, to verify if the referent of the WebID is indeed allowed access to the protected resource.
-The exact nature of those Access Control Rules is left for another specification.
-Suffice it to say that it can be something as simple as a lookup in a table.
-    %If access is granted, then the guard can pass on the request to the protected resource, which can then interact unimpeded with the client.
+    \item[4,5a+5b] The guard ask the verification component to verify the secretary WebID which is named in the certificate.
+This process is described in~\cite{story-h-2009--a} and is not touched by the delegation extension.
+However, since the \lstinline|On-Behalf-Of| header was sent, the verifier component also fetches the WebID of the principal agent which is refered there.
+The principal agents WebID is not verified in the same way as the secretary (e.g. no public key needed) but the secretary relation between secretary and principal agent is verified here.
+For doing this, the verifier component simply needs to query an exact SPARQL ASK query for that triple.
+   \item[6] After this authentication process, the authorization process is executed.
+This process is not topic of the paper and can involve a different resources.
+An important issue here is, that the authorization has to be dann with the principal agent WebID and not with the secretary WebID.
+    \item[7] If the authorization process decides an access, the protected resource can be requested, otherwise a \lstinline|403 Forbidden| HTTP result is sent.
 \end{enumerate}
@@
 
-\todo{Nice up wording esp. our terms and language}
+%\todo{Nice up wording esp. our terms and language}
 In this paper we discussed different ways how an agent, such as a Social Web application, can act on behalf of a user and request as well as manipulate resources on the Web in the name this user.
 Our proposal for supporting such a communication schema involves an extension to the WebID protocol, which allows for delegation of access authorization from one agent to another agent, both identified by its WebID.
-The technical solution annotates these \textit{in-the-name-of} HTTP requests by adding a HTTP request header field which refers to the WebID of the user in which name the agent acts on.
+The technical solution annotates these \textit{in-the-name-of} HTTP requests by adding the \lstinline|On-Behalf-Of| HTTP request header field which refers to the WebID of the user in which name the agent acts on.
 This distinguish the identities of the user and the agent and allows for creation of policy descriptions which use both WebIDs to specify the relations between the agent and the user in order to setup the access rules for this agent.

### 2012-08-04 paper.tex
shorten more

@@
 The following enumeration describes each authentication step of \autoref{fig:AuthSequence} in detail but concentrates on the context of access delegation:
-
-\begin{enumerate}
-    \item[1] The secretary agent opens a TLS connection with the server of the protected resource.
-    \item[2]  Once TLS is set up, the HTTP request is sent to the server (e.g. a \verb!HTTP GET!) to consume or manipulate a resource.
+(1) The secretary agent opens a TLS connection with the server of the protected resource.
+(2) Once TLS is set up, the HTTP request is sent to the server (e.g. a \verb!HTTP GET!) to consume or manipulate a resource.
         Here our first addition comes into play, the HTTP request header \lstinline|On-Behalf-Of| to claim an request as a secretary.
         We assume that the guard intercepts this HTTP request, and requests for a client authentication (using the TLS service)
-    \item[3] This authentication request is done using public key cryptography, sign a token with the guards private key and have the secretary send its certificate.
+(3) This authentication request is done using public key cryptography, sign a token with the guards private key and have the secretary send its certificate.
         This is defined in the TLS protocol which is specified in \cite{dierks-t-2012--a} and its successive RFCs.
         At the end of this step, the secretaries certificate is handled back to the guard.
-    \item[4,5a+5b] The guard ask the verification component to verify the secretary WebID which is named in the certificate.
+(4) The guard ask the verification component to verify the secretary WebID which is named in the certificatei (5a).
 This process is described in~\cite{story-h-2009--a} and is not touched by the delegation extension.
 However, since the \lstinline|On-Behalf-Of| header was sent, the verifier component also fetches the WebID of the principal agent which is refered there.
-The principal agents WebID is not verified in the same way as the secretary (e.g. no public key needed) but the secretary relation between secretary and principal agent is verified here.
+(5b) The principal agents WebID is not verified in the same way as the secretary (e.g. no public key needed) but the secretary relation between secretary and principal agent is verified here.
 For doing this, the verifier component simply needs to query an exact SPARQL ASK query for that triple.
-   \item[6] After this authentication process, the authorization process is executed.
+(6) After this authentication process, the authorization process is executed.
 This process is not topic of the paper and can involve a different resources.
 An important issue here is, that the authorization has to be dann with the principal agent WebID and not with the secretary WebID.
-    \item[7] If the authorization process decides an access, the protected resource can be requested, otherwise a \lstinline|403 Forbidden| HTTP result is sent.
-\end{enumerate}
+(7) If the authorization process decides an access, the protected resource can be requested, otherwise a \lstinline|403 Forbidden| HTTP result is sent.
 
@@
 %\subsection{OAuth}
-OAuth~2.0~\cite{hardt-d-2012--a} is the latest version of the OAuth protocol, which is being presented as an access delegation protocol, enabling users to grant access to third-party services to their personal resources, instead of sharing their passwords with those third-party services.
+\paragraph{OAuth~2.0}\cite{hardt-d-2012--a} is the latest version of the OAuth protocol, which is being presented as an access delegation protocol, enabling users to grant access to third-party services to their personal resources, instead of sharing their passwords with those third-party services.
 OAuth includes two main parts: obtaining an access token by asking the resource owner (i.e. the user) to grant access, and then using the tokens to access protected resources. 
@@
 
-\subsection{Cross Origin Resource Sharing (CORS)}
-
+\paragraph{Cross Origin Resource Sharing (CORS)}
 In this paper we proposed to add an \lstinline|On-Behalf-Of| header to each HTTP request made by a \textit{secretary} in order to be able to identify the \textit{principal} she is working for in that particular request.
@@
 CORS has two agents, one acting on behalf of the other, and these are: 
-\begin{itemize}
-  \item The Browser: it takes the role of the \textit{secretary} as it is acting on behalf of javascript agents - the \textit{principals}.
-  \item JavaScript code: hosted on the internet and identified by the Origin Server that hosted the javascript.
+The Browser -- it takes the role of the \textit{secretary} as it is acting on behalf of javascript agents - the \textit{principals}.
+JavaScript code -- hosted on the internet and identified by the Origin Server that hosted the javascript.
 This javascript agent requests resources from the Browser, but it is unable to do it directly.
-\end{itemize}
 
@@
 In the Section~\ref{sec:spec} use cases, the remote site trusts the \textit{principal}, but may not be aware of the \textit{secretary}.
-
 In our proposal, the identification of the agent in the \lstinline|On-Behalf-Of| header is much more precise.
@@
 However, at this point we postpone the answer to the question of how we should describe the access control rules in a users WebID profile.
-There already exists first attempts from the Linked Data / Semantic Web and the Read Write Web communities such as the WebAccessControl vocabulary\footnote{\url{http://www.w3.org/wiki/WebAccessControl}}, $_{dg}$FOAF~\cite{schwagereit-f-2010-181-a} as well as different projects on policy creation and management~\cite{kagal-l-2005--a,kagal-l-2005--b}.
+There already exists first attempts from the Linked Data / Semantic Web and the Read Write Web communities such as the WebAccessControl vocabulary\footnote{\url{http://www.w3.org/wiki/WebAccessControl}}, $_{dg}$FOAF~\cite{schwagereit-f-2010-181-a} as well as different projects on policy creation and management~\cite{kagal-l-2005--a}.
 In our future work we will try to close the gap between the policy and access control vocabularies on the one hand and WebID authentication on the other hand.

### 2012-08-04 paper.tex
remove todos
fix abstract

@@
 \begin{abstract}
-The WebID protocol enables the global identification of agents in a distributed manner by combining asymmetric cryptography and Linked Data.
-But in order for such a server to decide whether access should be granted or denied to a particular WebID, the web server may need to retrieve other profiles and linked resources to work out e.g.
-if the requesting agent is member of an authorized group (e.g.
-is a friend of a friend (FOAF) of the resource owner).
+The WebID protocol enables the global identification and authentication of agents in a distributed manner by combining asymmetric cryptography and Linked Data.
+But in order to decide whether access should be granted or denied to a particular WebID, the authenticating web server may need to retrieve other profiles and linked resources to work out e.g.
+if the requesting agent is member of an authorized group.
 If these linked resources (e.g. FOAF profiles) are required to be publicly available for the server to access it, then this would be a major privacy limitation on a linked Social Network.
@@
 %\todo{calculate how inefficient this is, and at what size of network this starts really become problematic}
-\todo{ST: add disadvantages according to the requirements (identity)}
+%\todo{ST: add disadvantages according to the requirements (identity)}
 

### 2012-08-04 paper.tex
Reworked Section 3.1.

@@
 
-The simplest solution for any user agent $A$ wishing to act as the user $U$, is for it to create a public / private key pair,  and with the public key thus generated create a certificate $C_u$ with $U$'s WebID in the Subject Alternative Name position and add the public key to the user $U$'s profile $P_u$.
-Having done this the agent $A$ can then connect using the certificate $C_u$ and its associated private key, to any service it wishes to, when it wants to work for / as the user $U$.
-This has the advantage of requiring no change to the WebID protocol.
-It does give the agent $A$ all powers of the user $U$ and so this type of privilege should be limited to agents in which are either extensions of $U$ or ones $U$ can or must fully trust anyway.
+The simplest solution for any user agent $A$ wishing to act as the user $U$, is for it to create its own certificate $C_u$ with $U$'s WebID URI in the Subject Alternative Name position and add the public key to the user $U$'s profile $P_u$.
+By doing this, the agent $A$ can then connect using its personal certificate $C_u$ and $U$'s profile, whenever it wants to work for / as the user $U$.
+This solution has the advantage of reusing the existing WebID protocol in its current state, as well as that it transfers all powers of user $U$ to agent $A$.
+Therefore, this type of privilege should be limited to agents that are either extensions of $U$ or ones $U$ can or must fully trust anyway.
 
-\lstinputlisting[
-    firstline=6,lastline=26,name=webid,style=turtle,float=htb,label=listing:multipleKeyProfile,
-    basicstyle=\ttfamily\scriptsize,
-    caption={Profile allowing three different agents to act as Romeo}
-]{Listings/mutlipleKeys.ttl}
-
-What kind of agents does it make sense to give such rights to?
-Or put another way: what agent would giving such rights to not constitute a reduction in security to the user?
-Or: which agent does the user and the authorization server already rely on completely?
+%\lstinputlisting[
+%    firstline=6,lastline=26,name=webid,style=turtle,float=htb,label=listing:multipleKeyProfile,
+%    basicstyle=\ttfamily\scriptsize,
+%    caption={Profile allowing three different agents to act as Romeo}
+%]{Listings/mutlipleKeys.ttl}
 
 In addition to the well known User Agents found in browsers on many different devices, there is one agent on which any service requiring WebID authentication relies on completely and this is the WebID profile's origin server~\cite{barth-a-2011--a}.
-Any server requiring authentication of an agent using WebID must trust the origin server serving the WebID Profile.
-That origin server can at any time change the public keys in the profiles sent back to any authorization agents and indeed change any information in the profile it wants to.
-Any user profile can then be thought of as being a user according to the origin server ie a \url{user@origin.org:port} - where \url{origin.org} is the domain of the origin server, and \url{port} is the port the server is running on.
+Any server requiring authentication of an agent using WebID must trust the server hosting the WebID profile, since the profile hosting server can change any information in the profile.
+Any user profile can then be thought of as being a user according to the origin server i.e.
+a \textit{user@origin.org:port} - where \textit{origin.org} is the domain of the origin server, and \textit{port} is the port the server is running on.
 
-When the user owns the origin server and there is a one to one relation between the two, as is principally the case in a personal FreedomBox, then the origin server is again just an extension of the user, and in that case there need be no thought of a difference between the user and the origin server.
-In that case the origin server can in fact just authenticate as the user whenever needed.
+When the user owns the origin server and there is a one to one relation between the two, as it is the case in a personal FreedomBox, then the origin server is just an extension of the user, and in that case trusting the server is the same as trusting the user.
+%In that case the origin server can in fact just authenticate as the user whenever needed.
 
 It should be noted that each device can still be distinguished by servers in case of a problem by logging the exact public key that was used to connect to a service. 
-It should be possible then to track down which device's private key had been compromised in case of unusual authentication behavior .
+It should be possible then to track down which device's private key had been compromised in case of unusual behaviour .
 
-Things get more interesting when an origin server agent $A$ is serving a number of different profiles $P_1$ \ldots $P_n$ each identifying respectively users $U_1$ \ldots $U_n$ and needs to act on behalf of these users.
-This would be the situation for servers acting for companies, government agencies, educational instituion, charities, football club, ....
-This brings up two issues that need to be taken into account: first an issue of data perspective and an efficiency issue.
+Things get more interesting when an origin server agent $A$ is serving a number of different profiles $P_1$ \ldots $P_n$ each identifying respectively users $U_1$ \ldots $U_n$ and needs to act on behalf of each of these users.
+This would be the situation for company servers, government agencies, educational institutions, charities, football clubs, etc.
+This brings up two issues that need to be taken into account, an issue of data perspective and an issue of efficiency.
 
@@
 
-First whenever $A$ connects as $U_1$ to a remote resource $R$ it has to place the data received in a seperate graph from the one it stores public non authenticated data in, and to the one it stores a representation to the same resurce $R$ seen when connected as the different user $U_2$.
-This is because the resource may return different representations depending on who is connecting to it - one representation for close friends of the owner of $R$ perhaps, and one for more distant ones.
-This can be illustrated using N3 graphs, by specifying a relation between a view on a resource (using a yet to be settled on vocabulary), and a graph which is the log:semantics of that view (cf.
+%First whenever $A$ connects as $U_1$ to a remote resource $R$ it has to place the data received in a separate graph from the one it stores public non authenticated data in, and to the one it stores a representation to the same resource $R$ seen when connected as the different user $U_2$.
+%This is because the resource may return different representations depending on who is connecting to it - one representation for close friends of the owner of $R$ perhaps, and one for more distant ones.
+Whenever $A$ connects as $U_1$ to a remote resource $R$, the received data will reflect $R$'s access control policies specific for $U_1$, and thus the data needs to be placed in a separate graph corresponding to $U_1$.
+Results for unauthenticated requests are stored in a common public graph.
+%This can be illustrated using N3 graphs, by specifying a relation between a view on a resource (using a yet to be settled on vocabulary), and a graph which is the log:semantics of that view (cf.
 Listing~\ref{listing:views}).
 It is very important that the agent receiving information from different users not merge the information that was destined to different users, or else information leakage will severely reduce the trust other agents have in that server $A$.
-This requires carefully keeping identified information that was aimed at different users seperate, perhaps by creating different graph stores: one for publically - non authenticated - information, and one graph store for each user the server needs to authenticate as.
+A possible solution involves carefully keeping identified information that was aimed at different users separate, perhaps by creating different graph stores: one for public - unauthenticated - information, and one graph store for each user the server needs to authenticate as.
 
-\lstinputlisting[
-    firstline=8,lastline=36,name=views,style=turtle,float=htb,label=listing:views,
-    basicstyle=\ttfamily\scriptsize,
-    caption={Views on Juliet's FOAF profile by Freedom Box Laurence, when acting as Romeo and when acting as Lord Montague }
-]{Listings/views.n3}
+%\lstinputlisting[
+%    firstline=8,lastline=36,name=views,style=turtle,float=htb,label=listing:views,
+%    basicstyle=\ttfamily\scriptsize,
+%    caption={Views on Juliet's FOAF profile by Freedom Box Laurence, when acting as Romeo and when acting as Lord Montague }
+%]{Listings/views.n3}
 
-Secondly, whenever the Origin Server needs to act as $U_1$ to a remote server $R$ it will need to open a new TLS connection to that server using the certificate $C_{u1}$ for that user.
+Secondly, whenever the Origin Server needs to act as $U_1$ to a remote server $R$, it will need to open a new TLS connection to that server using the certificate $C_{u1}$ for that user.
 This could require $N$ parallel connections to the same server $S$. 
-Opening TLS connections is somewhat expensive: it requires opening up a new TCP connection and starting an expensive asymmetrick key cryptographic handshake. 
-For small numbers of N this can be defended, but as N becomes large the inefficiency this could create between two
-organisations may be a serious drawback.
+Opening TLS connections is somewhat expensive, as it requires expensive asymmetric key cryptographic computations. 
+When N becomes large, this inefficiency will be perceived as a serious drawback between two organisations.
 %\todo{calculate how inefficient this is, and at what size of network this starts really become problematic}

### 2012-08-04 paper.tex

@@
 $S$ would send $R$ its certificate, thereby requiring $R$ to dereference $S$'s profile $P_s$ in order to verify the WebID.
-If $P_s$ itself requires authentiction of $R$ and if $R$ sends a certificate containing a WebID with its profile $P_r$, and if $P_r$ itself requires authentication then it looks like we have a deadlock.}.
+If $P_s$ itself requires authentication of $R$ and if $R$ sends a certificate containing a WebID with its profile $P_r$, and if $P_r$ itself requires authentication then it looks like we have a deadlock.}.
 
@@
 Delegation should not be handled by camouflaging an request of an agent in the sense that this request is indistinguishable from a principal agent request.
-A secretary agent should use its own certificate (see efficency requirement) and it should be identified and described by its own WebID profile.
+A secretary agent should use its own certificate (see efficiency requirement) and it should be identified and described by its own WebID profile.
 The motivation for this is variously.
@@
 By doing this, the agent $A$ can then connect using its personal certificate $C_u$ and $U$'s profile, whenever it wants to work for / as the user $U$.
-This solution has the advantage of reusing the existing WebID protocol in its current state, as well as that it transfers all powers of user $U$ to agent $A$.
-Therefore, this type of privilege should be limited to agents that are either extensions of $U$ or ones $U$ can or must fully trust anyway.
+This solution has the advantage of not making any modifications to the WebID protocol, as well as that it transfers all powers of user $U$ to agent $A$.
+However, this type of privilege should be limited to agents that are either extensions of $U$ or ones $U$ can or must fully trust anyway.
 
@@
 
-In addition to the well known User Agents found in browsers on many different devices, there is one agent on which any service requiring WebID authentication relies on completely and this is the WebID profile's origin server~\cite{barth-a-2011--a}.
-Any server requiring authentication of an agent using WebID must trust the server hosting the WebID profile, since the profile hosting server can change any information in the profile.
-Any user profile can then be thought of as being a user according to the origin server i.e.
-a \textit{user@origin.org:port} - where \textit{origin.org} is the domain of the origin server, and \textit{port} is the port the server is running on.
+%In addition to the well known User Agents found in browsers on many different devices, there is one agent on which any service requiring WebID authentication trusts implicitly and this is the WebID profile's origin server.
+Any server requiring authentication of an agent using WebID must implicitly trust the origin server~\cite{barth-a-2011--a} hosting the WebID profile, since the profile hosting server can change any information in the profile.
+%Any user profile can then be thought of as being a user according to the origin server, i.e.
+\textit{user@origin.org:port} - where \textit{origin.org} is the domain of the origin server, and \textit{port} is the port the server is running on.
 
-When the user owns the origin server and there is a one to one relation between the two, as it is the case in a personal FreedomBox, then the origin server is just an extension of the user, and in that case trusting the server is the same as trusting the user.
+When the user owns the origin server and there is a one-to-one relation between the two, as it is the case in a personal FreedomBox\footnote{http://www.freedomboxfoundation.org/}, then the origin server is just an extension of the user, and in that case trusting the server is the same as trusting the user.
 %In that case the origin server can in fact just authenticate as the user whenever needed.
@@
 
-Things get more interesting when an origin server agent $A$ is serving a number of different profiles $P_1$ \ldots $P_n$ each identifying respectively users $U_1$ \ldots $U_n$ and needs to act on behalf of each of these users.
+Things become more interesting when an origin server agent $A$ is serving a number of different profiles $P_1$ \ldots $P_n$ each identifying respectively users $U_1$ \ldots $U_n$ and needs to act on behalf of each of these users.
 This would be the situation for company servers, government agencies, educational institutions, charities, football clubs, etc.
@@
 A possible solution involves carefully keeping identified information that was aimed at different users separate, perhaps by creating different graph stores: one for public - unauthenticated - information, and one graph store for each user the server needs to authenticate as.
-
-%\lstinputlisting[
-%    firstline=8,lastline=36,name=views,style=turtle,float=htb,label=listing:views,
-%    basicstyle=\ttfamily\scriptsize,
-%    caption={Views on Juliet's FOAF profile by Freedom Box Laurence, when acting as Romeo and when acting as Lord Montague }
-%]{Listings/views.n3}
 
@@
 It could even use the same certificate.
-This would make clear to any server it was connecting to, that it could rely on this server as much as it could on the identity of any resource, and in particular any WebID profils served by that server.
+This would make clear to any server it was connecting to, that it could rely on this server as much as it could on the identity of any resource, and in particular any WebID profiles served by that server.
 
 Still, such an agent connecting to a remote service on behalf of one of its users would then need to identify which user it was acting on behalf of, or the remote service receiving a request would not know which access control rule to apply to the requesting origin server.
-For example in our previous example in the Romeo and Juliet story we showed how the Capulet family Freedom Box only shows Juliet as knowing Romeo, when Romeo makes the request on the resource, but not when the request is made by Romeo's father, lord Montague.
-That was an easy access control rule for the Capulet Freedbom Box to make when the request was using the WebID protocol simipliciter, since there it would know via the WebID authentication process exactly which identity the user was making the request as.
-But if it is the Origin Server connecting to the Capulet Freedom Box, identified as their Montague Origin Server, then what representation should the Capulet FB return? 
+For example in our previous example in the Romeo and Juliet story we showed how the Capulet family FreedomBox only shows Juliet as knowing Romeo, when Romeo makes the request on the resource, but not when the request is made by Romeo's father, lord Montague.
+That was an easy access control rule for the Capulet FreedomBox to make when the request was using the WebID protocol, since there it would know via the WebID authentication process exactly which identity the user was making the request as.
+But if it is the Origin Server connecting to the Capulet (FreedomBox), identified as their Montague Origin Server, then what representation should the Capulet FreedomBox return? 
 Should it return the reduced version available to Lord Montague?
 Or should it return the more complete version available to Romeo and his close friends?
+
+%\lstinputlisting[
+%    firstline=8,lastline=36,name=views,style=turtle,float=htb,label=listing:views,
+%    basicstyle=\ttfamily\scriptsize,
+%    caption={Views on Juliet's FOAF profile by Freedom Box Laurence, when acting as Romeo and when acting as Lord Montague }
+%]{Listings/views.n3}
 
@@
 
-The Capulet FB Guard having verified that this request does indeed come from the origin server of Romeo's profile
-https://montague.net/romeo would then be able to accept that since the requesting server could in any case act as Romeo whenever it chose to do so, this protocol making exchange between the Montague and Capulet housholds more efficient without making it less secure, this be justification enough for it (the capulet freedom box) to  serve the representation that Romeo would have received had he connected to the server directly.
-We will argue further down that this is very similar to the way CORS deals with access control, namely by adding a header to a request to clarify what agent is making the request.
+The Capulet FreedomBox Guard having verified that this request does indeed come from the origin server of Romeo's profile
+https://montague.net/romeo would then be able to accept that since the requesting server could in any case act as Romeo whenever it chose to do so, this protocol making exchange between the Montague and Capulet houses more efficient without making it less secure, this be justification enough for it (the Capulet FreedomBox) to  serve the representation that Romeo would have received had he connected to the server directly.
+In Section~\ref{sec:relatedwork} we will argue that this is very similar to the way CORS deals with access control, namely by adding a header to a request in order to clarify what agent is making the request.
 
 This On-Behalf-Of header makes it possible for one agent to open only one TLS connection to a remote server and be 
-able to sepecify for each request on behalf of whome it is making it.
-The Montague Freedom Box could make a request to the capulet Freedom Box On-Behalf-Of Romeo, a few milliseconds later On-Behalf-Of Lord Montague, and so on...
-Again as explained in the previous section is is the responsibility of the Montague Freedom Box to keep these inforation seperate, and act with secrecy whenever it is acting on behalf of one or the other of the users.
+able to specify for each request on behalf of whom it is making it.
+The Montague FreedomBox could make a request to the Capulet FreedomBox \textit{On-Behalf-Of} Romeo, a few milliseconds later On-Behalf-Of Lord Montague, and so on.
+Again as explained in the previous section is is the responsibility of the Montague FreedomBox to keep these information separate, and act with secrecy whenever it is acting on behalf of one or the other of the users.
 As such it's role is not unlike the role of Friar Laurence in the play - dedication to people's private matters requires tact and secrecy.
@@
 If we now identify with a WebID the secretary that can act on behalf of a user, we can generalise the protocol somewhat.
-That is, when an agent - such as the Montague Freedom Box Laurence with WebID \lstinline|<http://montague.net/fb#laurence>| - authenticates to a remote server it can use its own WebID. 
+That is, when an agent - such as the Montague FreedomBox Laurence with WebID \lstinline|<http://montague.net/fb#laurence>| - authenticates to a remote server it can use its own WebID. 
 This would allow the Agent to have its own public key, and so for a compromise of the client public key not to affect the server public key.
@@
 It can no longer just compare the TLS keys of the requesting agent to see if it comes from the same Origin Server.
-We need to make this relation explicity by use of a special RDF relation provisionally called \lstinline|cert:secretary|%
+We need to make this relation explicit by use of a special RDF relation provisionally called \lstinline|cert:secretary|%
 \footnote{A object property with a domain and range as \lstinline|foaf:Agent| which we will provisionally place
@@
 
-The remote server can then verify that the identified agent is the secretary of the agent he wishes to act on behalf of (as sepecified in the \lstinline|On-Behalf-Of| header, by dereferencing that users profile and verifying that the user specifies the \lstinline|cert:secretary| relation there, as it would if Romeo had the foaf profiles as shown in Listing \ref{listing:webid1}.
+The remote server can then verify that the identified agent is the secretary of the agent he wishes to act on behalf of (as specified in the \lstinline|On-Behalf-Of| header, by dereferencing that users profile and verifying that the user specifies the \lstinline|cert:secretary| relation there, as it would if Romeo had the FOAF profiles as shown in Listing \ref{listing:webid1}.
 
@@
         At the end of this step, the secretaries certificate is handled back to the guard.
-(4) The guard ask the verification component to verify the secretary WebID which is named in the certificatei (5a).
+(4) The guard ask the verification component to verify the secretary WebID which is named in the certificate (5a).
 This process is described in~\cite{story-h-2009--a} and is not touched by the delegation extension.
-However, since the \lstinline|On-Behalf-Of| header was sent, the verifier component also fetches the WebID of the principal agent which is refered there.
+However, since the \lstinline|On-Behalf-Of| header was sent, the verifier component also fetches the WebID of the principal agent which is referred there.
 (5b) The principal agents WebID is not verified in the same way as the secretary (e.g. no public key needed) but the secretary relation between secretary and principal agent is verified here.
@@
 This process is not topic of the paper and can involve a different resources.
-An important issue here is, that the authorization has to be dann with the principal agent WebID and not with the secretary WebID.
+An important issue here is, that the authorization has to be done with the principal agent WebID and not with the secretary WebID.
 (7) If the authorization process decides an access, the protected resource can be requested, otherwise a \lstinline|403 Forbidden| HTTP result is sent.

### 2012-08-04 paper.tex
reducing

--- 2012-08-04 paper.tex
@@
 \begin{abstract}
-The WebID protocol enables the global identification and authentication of agents in a distributed manner by combining asymmetric cryptography and Linked Data.
-But in order to decide whether access should be granted or denied to a particular WebID, the authenticating web server may need to retrieve other profiles and linked resources to work out e.g.
-if the requesting agent is member of an authorized group.
+The WebID protocol enables the global identification of agents in a distributed manner by combining asymmetric cryptography and Linked Data.
+But in order for such a server to decide whether access should be granted or denied to a particular WebID, the web server may need to retrieve other profiles and linked resources to work out e.g.
+if the requesting agent is member of an authorized group (e.g.
+is a friend of a friend (FOAF) of the resource owner).
 If these linked resources (e.g. FOAF profiles) are required to be publicly available for the server to access it, then this would be a major privacy limitation on a linked Social Network.
-In this paper we explore different ways how an agent can act as a user as well as we propose an extension to the WebID protocol which allows for delegation of access authorization from a WebID to a third party, e.g.
+In this paper we explore different ways how an agent can act as a user and we propose an extension to the WebID protocol which allows for delegation of access authorization from a WebID to a third party, e.g.
 allowing a server to be able to act on behalf of its users.
@@
 
-Based on the introductory usage scenario from the previous section as well as additional preliminary considerations, we issue the following implementation relevant requirements for an access delegation solution based on the WebID authentication protocol.
+In order to make discussion of the problems easier, we distinguish the following roles in the access delegation process:
+\begin{enumerate}
+    \item The \textit{secretary} acts in the name of another agent, the \textit{principal}.
+    \item The \textit{principal} is the agent who has a secretary that acts on its behalf.
+\end{enumerate}
 
-Beside that, we have identified the following roles being part of the access delegation process:
-\begin{enumerate}
-    \item The \textit{secretary agent} is the agent which acts in the name of another agent.
-This agent actually requests some resources and tries to do that on behalf of someone.
-    \item The \textit{principal agent} is the agent which is represented by the secretary.
-This agent does not have an active role in the request but is principal as the origin of the activity.
-\end{enumerate}
-We use both terms consequently to avoid confusion.
+The solution we will propose will be based on the following general principles:
 
-\paragraph{Distinguish secretary agents from principal agents}
-Delegation should not be handled by camouflaging an request of an agent in the sense that this request is indistinguishable from a principal agent request.
-A secretary agent should use its own certificate (see efficency requirement) and it should be identified and described by its own WebID profile.
-The motivation for this is variously.
+\paragraph{Distinguish secretary from principal }-
+Identity should as far as possible be transparent.
+A secretary should have it's own WebID.
+The motivation for this is:
 (1) It allows resource guards to permit or deny requests based on this information.
-(2) Applications which are secretary for many different principal agents do not need to switch their certificate between requests.
-Also they do not need to handle hundreds of different keys.
-(3) It allows for describing access control rules and the relation of a secretary agent to its principal agent.
-Without a secretary WebID, this would not be possible.
+(2) Secretary that have many principals do not need to switch their certificate between requests.
+(3) It makes it possible to describe the relation between a principal and its secretary using linked data.
 
-\paragraph{Easy to use}
-The one and only place to describe which secretary agents are allowed to operate as a principal agent should be the WebID profile itself or another Linked Data available document.
-To grant delegated access to a secretary agent, no other actions than simply adding triples to the WebID profile should be needed.
-To reset this grant the same triple can removed from the WebID profile.
+\paragraph{Easy to use}-
+The one and only place to describe which secretary are allowed to operate for a principal should be the principal's WebID profile.
+To grant delegated access to a secretary agent, no other actions than adding 1 triple to the WebID profile should be needed.
+Retracting this grant should involve simply removing it from the WebID profile.
 
@@
 
-\paragraph{Minimal protocol footprint}
+\paragraph{Minimal protocol footprint}-
 %In addition to the integration requirement
-We argue that a minimal protocol footprint should be achieved to allow a wide adoption of the solution.
-This includes the requirement to not add an additional service to the authentication process than using the existing ones.
-This also shifts the responsibility for an access control decision from a service to a machine readable document.
+By using HTTP and working declaratively by placing statements in documents, we make adoption of the delegation easier and avoid complex protocol developments.
 We believe that this is a crucial feature of Linked Data in general.
 
-\paragraph{Efficiency}
-Finally, we have in mind that a proposed solution should scale in the sense of users and connections.
-In our context this means that an Social Web application should be able to act in the name of thousands of users without having scalability issues which conclude from WebID authentication.
+\paragraph{Efficiency}-
+Finally, the proposed solution should scale with growing number of users and connections.
+In our context this means that an Social Web application should be able to act in the name of thousands of users.
 
@@
 
-This section in organized in multiple subsections which all discuss a possible solution for enabling access delegation.
-All but the last solution fail in one or more requirement or based on other issues.
+This section is organized in subsections which build up step by step to the proposed protocol, adding and validating the need at each step for the next one, the final proposed protocol satisfying the previous principles.
 
@@
 
-The simplest solution for any user agent $A$ wishing to act as the user $U$, is for it to create a public / private key pair,  and with the public key thus generated create a certificate $C_u$ with $U$'s WebID in the Subject Alternative Name position and add the public key to the user $U$'s profile $P_u$.
-Having done this the agent $A$ can then connect using the certificate $C_u$ and its associated private key, to any service it wishes to, when it wants to work for / as the user $U$.
+The simplest solution for any user agent $A$ wishing to act as the user $U$, is for it to create a public/private key pair,  and with the public key thus generated create a certificate $C_u$ with $U$'s WebID in the Subject Alternative Name position and add the public key to the user $U$'s profile $P_u$.
+Having done this the agent $A$ can then connect using the certificate $C_u$ and its associated private key, to any service it wishes to, when it wants to work for/as the user $U$.
 This has the advantage of requiring no change to the WebID protocol.
@@
 %\todo{calculate how inefficient this is, and at what size of network this starts really become problematic}
-%\todo{ST: add disadvantages according to the requirements (identity)}
 

### 2012-08-04 paper.tex

@@
 \begin{abstract}
-The WebID protocol enables the global identification of agents in a distributed manner by combining asymmetric cryptography and Linked Data.
-But in order for such a server to decide whether access should be granted or denied to a particular WebID, the web server may need to retrieve other profiles and linked resources to work out e.g.
-if the requesting agent is member of an authorized group (e.g.
-is a friend of a friend (FOAF) of the resource owner).
+The WebID protocol enables the global identification and authentication of agents in a distributed manner by combining asymmetric cryptography and Linked Data.
+But in order to decide whether access should be granted or denied to a particular WebID, the authenticating web server may need to retrieve other profiles and linked resources to work out e.g.
+if the requesting agent is member of an authorized group.
 If these linked resources (e.g. FOAF profiles) are required to be publicly available for the server to access it, then this would be a major privacy limitation on a linked Social Network.
-In this paper we explore different ways how an agent can act as a user and we propose an extension to the WebID protocol which allows for delegation of access authorization from a WebID to a third party, e.g.
+In this paper we explore different ways in which an agent can act as a user and we propose an extension to the WebID protocol which allows for delegation of access authorization from a WebID to a third party, e.g.
 allowing a server to be able to act on behalf of its users.
@@
 
-The simplest solution for any user agent $A$ wishing to act as the user $U$, is for it to create a public/private key pair,  and with the public key thus generated create a certificate $C_u$ with $U$'s WebID in the Subject Alternative Name position and add the public key to the user $U$'s profile $P_u$.
-Having done this the agent $A$ can then connect using the certificate $C_u$ and its associated private key, to any service it wishes to, when it wants to work for/as the user $U$.
+The simplest solution for any user agent $A$ wishing to act as the user $U$, is for it to create a public / private key pair,  and with the public key thus generated create a certificate $C_u$ with $U$'s WebID in the Subject Alternative Name position and add the public key to the user $U$'s profile $P_u$.
+Having done this the agent $A$ can then connect using the certificate $C_u$ and its associated private key, to any service it wishes to, when it wants to work for / as the user $U$.
 This has the advantage of requiring no change to the WebID protocol.

### 2012-08-04 paper.tex
further cleaning up and making things more concise.

@@
 \end{enumerate}
-
-The solution we will propose will be based on the following general principles:
+The solution we propose will be based on the following general principles:
 
@@
 
-\subsubsection{Keeping views distinct: }
-
+\paragraph{Keeping views distinct}-
 First whenever $A$ connects as $U_1$ to a remote resource $R$ it has to place the data received in a seperate graph from the one it stores public non authenticated data in, and to the one it stores a representation to the same resurce $R$ seen when connected as the different user $U_2$.
@@
 
-Secondly, whenever the Origin Server needs to act as $U_1$ to a remote server $R$ it will need to open a new TLS connection to that server using the certificate $C_{u1}$ for that user.
+\paragraph{Efficiency}-Secondly, whenever the Origin Server needs to act as $U_1$ to a remote server $R$ it will need to open a new TLS connection to that server using the certificate $C_{u1}$ for that user.
 This could require $N$ parallel connections to the same server $S$. 
-Opening TLS connections is somewhat expensive: it requires opening up a new TCP connection and starting an expensive asymmetrick key cryptographic handshake. 
+Opening TLS connections is somewhat expensive: it requires opening up a new TCP connection and starting an expensive asymmetric key cryptography handshake. 
 For small numbers of N this can be defended, but as N becomes large the inefficiency this could create between two
@@
 
-The proposal here is for the Origin Server to add to each HTTP request (made over TLS) an On-Behalf-Of header identifying the user on behalf of which the request is being made with that user's WebID.
+The proposal here is for the Origin Server to add to each HTTP request (made over TLS) an \lstinline|On-Behalf-Of| header identifying the user on behalf of which the request is being made with that user's WebID.
 
@@
 The Capulet FB Guard having verified that this request does indeed come from the origin server of Romeo's profile
-https://montague.net/romeo would then be able to accept that since the requesting server could in any case act as Romeo whenever it chose to do so, this protocol making exchange between the Montague and Capulet housholds more efficient without making it less secure, this be justification enough for it (the capulet freedom box) to  serve the representation that Romeo would have received had he connected to the server directly.
+\lstinline|<https://montague.net/romeo>| would then be able to accept that since the requesting server could in any case act as Romeo whenever it chose to do so, this protocol making exchange between the Montague and Capulet housholds more efficient without making it less secure, this be justification enough for it (the capulet freedom box) to  serve the representation that Romeo would have received had he connected to the server directly.
 We will argue further down that this is very similar to the way CORS deals with access control, namely by adding a header to a request to clarify what agent is making the request.
 
-This On-Behalf-Of header makes it possible for one agent to open only one TLS connection to a remote server and be 
-able to sepecify for each request on behalf of whome it is making it.
-The Montague Freedom Box could make a request to the capulet Freedom Box On-Behalf-Of Romeo, a few milliseconds later On-Behalf-Of Lord Montague, and so on...
-Again as explained in the previous section is is the responsibility of the Montague Freedom Box to keep these inforation seperate, and act with secrecy whenever it is acting on behalf of one or the other of the users.
+This \lstinline|On-Behalf-Of| header makes it possible for the \textit{secretary} to open only one TLS connection to a remote server and be 
+able to specify for each request on behalf of whome it is making it.
+The Montague Freedom Box could make a request to the capulet Freedom Box \lstinline|On-Behalf-Of| Romeo, a few milliseconds later \lstinline|On-Behalf-Of| Lord Montague, and so on...
+Again as explained in the previous section is is the responsibility of the Montague Freedom Box to keep the returned information seperate, and act with secrecy whenever it is acting on behalf of one or the other of the users.
 As such it's role is not unlike the role of Friar Laurence in the play - dedication to people's private matters requires tact and secrecy.
@@
 Using the same cryptographic key between the server acting as client and as server risks making the keys available to a wider audience, and so increases the risk of key compromise. 
-It may be useful if it were possible to decouple the identity of the agent acting on behalf of another user from the Origin Server.
+It may be useful if it were possible to decouple the identity of the agent acting on behalf of another user - the \textit{secretary} - from the Origin Server.
 
@@
 
-The remote server can then verify that the identified agent is the secretary of the agent he wishes to act on behalf of (as sepecified in the \lstinline|On-Behalf-Of| header, by dereferencing that users profile and verifying that the user specifies the \lstinline|cert:secretary| relation there, as it would if Romeo had the foaf profiles as shown in Listing \ref{listing:webid1}.
+The remote server can then verify that the identified agent is the secretary of the agent he wishes to act on behalf of (as sepecified in the \lstinline|On-Behalf-Of| header, by dereferencing that user's profile and verifying that the user specifies the \lstinline|cert:secretary| relation there, as it would if Romeo had the foaf profiles as shown in Listing \ref{listing:webid1}.
 
 \lstinputlisting[
-    firstline=4,lastline=14,name=webid,style=turtle,float=htb,label=listing:webid1,
+    firstline=5,lastline=14,name=webid,style=turtle,float=htb,label=listing:webid1,
     basicstyle=\ttfamily\scriptsize,
@@
 The following enumeration describes each authentication step of \autoref{fig:AuthSequence} in detail but concentrates on the context of access delegation:
-(1) The secretary agent opens a TLS connection with the server of the protected resource.
-(2) Once TLS is set up, the HTTP request is sent to the server (e.g. a \verb!HTTP GET!) to consume or manipulate a resource.
-        Here our first addition comes into play, the HTTP request header \lstinline|On-Behalf-Of| to claim an request as a secretary.
-        We assume that the guard intercepts this HTTP request, and requests for a client authentication (using the TLS service)
-(3) This authentication request is done using public key cryptography, sign a token with the guards private key and have the secretary send its certificate.
-        This is defined in the TLS protocol which is specified in \cite{dierks-t-2012--a} and its successive RFCs.
-        At the end of this step, the secretaries certificate is handled back to the guard.
-(4) The guard ask the verification component to verify the secretary WebID which is named in the certificatei (5a).
-This process is described in~\cite{story-h-2009--a} and is not touched by the delegation extension.
-However, since the \lstinline|On-Behalf-Of| header was sent, the verifier component also fetches the WebID of the principal agent which is refered there.
-(5b) The principal agents WebID is not verified in the same way as the secretary (e.g. no public key needed) but the secretary relation between secretary and principal agent is verified here.
-For doing this, the verifier component simply needs to query an exact SPARQL ASK query for that triple.
-(6) After this authentication process, the authorization process is executed.
-This process is not topic of the paper and can involve a different resources.
-An important issue here is, that the authorization has to be dann with the principal agent WebID and not with the secretary WebID.
-(7) If the authorization process decides an access, the protected resource can be requested, otherwise a \lstinline|403 Forbidden| HTTP result is sent.
+(1) The secretary  opens a TLS connection with the server of the protected resource.
+(2) Once TLS is set up, the HTTP request is sent to the server (e.g.
+a \verb!HTTP GET!), with an additional \lstinline|On-Behalf-Of| header, which thereby defines the requesting agent as a \textit{secretary} and the referred to agent as the \textit{principal}
+(3) The guard intercepts this request, and  in turn requests client authentication using TLS session renegotiation.
+The \textit{secretary} authenticates as itself by sending a Certificate containing a WebID refering to it.
+The TLS-Light service verifies that the \textit{secretary} really is in possession of the private key corresponding to the public key sent in the certificate.
+This is defined in the TLS protocol \cite{dierks-t-2012--a}.
+(4) The guard ask the verification agent to verify the secretary WebID which is named in the certificate (5a).
+This process is exactly as described in the WebID protocol~\cite{story-h-2009--a}.
+The guard also asks the verifier agent to check the secretary claim implied by the \lstinline|On-Behalf-Of| header.
+(5b) The \textit{principal} agent's relation to the \textit{secretary} is  verified by dereferencing the \textit{principal}'s WebID Profile, and verifying it responds with a true to the SPARQL ASK query \lstinline|ASK { ?principal cert:secretary ?secretary .
+}| where the \lstinline|?principal| and \lstinline|?secretary| variables have been bound to the correct URIs.
+(6) The authentication and verification process having succeeded, the authorization process checking if the \textit{principal} would get access to the requested resource.
+(7) The resource representation can then be returned or not depending on the access control rules.
 
@@
 \textbf{MyProfile}\footnote{\url{http://myprofile-project.org/}}
-intends to provide a solution for managing the numerous accounts and profiles that users have on the Web.
-Its main purpose is to provide a unified user account, or simply \textit{user profile}, which as opposed to current \textit{silo} profiles, would really be under the user's control, on a device located within the user physical reach.
+is a web server demonstrating how easy it is to create a WebID profile, and buidling up some distributed social web applications upon this.
+Its main purpose is to provide a unified user account, or simply \textit{user profile}.
+Currently these are tied to the my-profile-project web site, but it has been architected from the ground up to  work with distributed linked data, making it then easy to dissociate the software stack from the myprofile-project domain name,  and allowing it to be deployed on a machine under the user's control, prefereably even a device located within the user physical reach.
 
@@
 \textbf{OntoWiki}
-\cite{auer-s-2006-736-a} is a web application, which allows for publication, exploration as well as manipulation of arbitrary RDF knowledge bases in distributed scenarios.
+\cite{auer-s-2006-736-a} is a web application, which allows publication, exploration as well as manipulation of arbitrary RDF knowledge bases in distributed scenarios.
 We refer to it as a data wiki, since it adopts the wiki philosophy (ease of editing, tracking of changes, integrated discussions) on the one hand, while focussing on structured information on the other hand.
@@
 With WebID access delegation again, the resources can be fetched by the Pingback server on behalf of the resource owner.
+
+This will require some further changes to the delegation protocol discussed up to now.
+Specifically the \lstinline|cert:secretary| relation currently does not carefully distinguish what kind of repsonsibilities the \textit{principal} wishes to give to the \textit{secretary}.
+For ontowiki knowing the social network may be all that is needed to make access control decisions.
+Full delegation powers may not be needed.
 

### 2012-08-04 paper.tex
final changes

@@
 It can no longer just compare the TLS keys of the requesting agent to see if it comes from the same Origin Server.
-We need to make this relation explicity by use of a special RDF relation provisionally called \lstinline|cert:secretary|%
+We need to make this relation explicity by use of a special RDF relation provisionally called \lstinline|:secretary|%
 \footnote{A object property with a domain and range as \lstinline|foaf:Agent| which we will provisionally place
@@
 
-The remote server can then verify that the identified agent is the secretary of the agent he wishes to act on behalf of (as sepecified in the \lstinline|On-Behalf-Of| header, by dereferencing that user's profile and verifying that the user specifies the \lstinline|cert:secretary| relation there, as it would if Romeo had the foaf profiles as shown in Listing \ref{listing:webid1}.
+The remote server can then verify that the identified agent is the secretary of the agent he wishes to act on behalf of (as sepecified in the \lstinline|On-Behalf-Of| header, by dereferencing that user's profile and verifying that the user specifies the \lstinline|:secretary| relation there, as it would if Romeo had the foaf profiles as shown in Listing \ref{listing:webid1}.
 
@@
 The guard also asks the verifier agent to check the secretary claim implied by the \lstinline|On-Behalf-Of| header.
-(5b) The \textit{principal} agent's relation to the \textit{secretary} is  verified by dereferencing the \textit{principal}'s WebID Profile, and verifying it responds with a true to the SPARQL ASK query \lstinline|ASK { ?principal cert:secretary ?secretary .
+(5b) The \textit{principal} agent's relation to the \textit{secretary} is  verified by dereferencing the \textit{principal}'s WebID Profile, and verifying it responds with a true to the SPARQL ASK query \lstinline|ASK { ?principal :secretary ?secretary .
 }| where the \lstinline|?principal| and \lstinline|?secretary| variables have been bound to the correct URIs.
@@
 
-In the case of MyProfile, it is very important to be able to offer WebID access delegation, because a single MyProfile server instance can host multiple users.
+In the case of MyProfile, it is very important to be able to offer WebID access delegation, because a single MyProfile server instance can host multiple users, and must fetch resources for each user asynchronously in order to be able to provide a seamless and rapid user experience.
 To improve user experience and overall performance, a caching mechanism is used to refresh local copies or "views" of external data.
-Due to multiple users coexisting on the same server, the caching mechanism needs to be able to differentiate between views belonging to each user, according to their specific access control policies configured on external resource providers.
+Due to multiple users coexisting on the same server, the caching mechanism needs to be able to distinguish views of remote resources as seen by different users, as they are served by remote servers depending on their access control and resoure filtering policies.
 
@@
 Charley is an external user with access control policies set up on his private server.
-When Ann requests to view Charley's profile data, a personalized view of the profile is displayed, corresponding to access control policies for Ann.
+When Ann requests to view Charley's profile data, a personalized view of the profile is displayed, corresponding to access control policies by Barry for requests made by Ann.
 When Barry requests to view Charley's profile, different profile data is displayed, since there are different access control policies for Barry.
-At this point, the caching mechanism needs to be able to cache two different profile views, each corresponding to access control policies specific for the user requesting the data.
-For this reason, the caching mechanism is required to act as a service agent, identifying itself as well as conveying the identity of the user on  behalf of whom the agent is requesting data.
+The caching mechanism needs to be able to cache two different profile views, each corresponding to access control policies specific for the user requesting the data.
+As the number of users on MyProfile grows this has to be done as efficiently as possible, and so re-using TLS connections where possible is a laudable aim.
 
@@
 In addition to the usual features of wikis, OntoWiki provides a sophisticated extension system, such that it can be adapted for a variety of use-cases.
-Although the wiki philosophy proposes that everyone can edit everything, numerous real-world applications imply the need for access-control mechanisms.
+Although the wikis usually enable anyone to edit everything, numerous real-world applications require aaccess-control mechanisms.
 OntoWiki has built-in support for authorization on graph and action level.
@@
 This will require some further changes to the delegation protocol discussed up to now.
-Specifically the \lstinline|cert:secretary| relation currently does not carefully distinguish what kind of repsonsibilities the \textit{principal} wishes to give to the \textit{secretary}.
+Specifically the \lstinline|:secretary| relation currently does not distinguish what kind of repsonsibilities the \textit{principal} wishes to give to the \textit{secretary}.
+It is currently assumed that the secretary has full rights.
 For ontowiki knowing the social network may be all that is needed to make access control decisions.
 Full delegation powers may not be needed.
+The ability to describe more limited secretary relations could be very helpful here.
 
@@
 This is quite a major semantic addition to HTTP, but for which there is a widely adopted precedent, namely CORS\footnote{\url{http://www.w3.org/TR/cors/}}, the Cross Origin Resource Sharing spec at the W3C.
-CORS identifies the remote \textit{principal} with an \lstinline|Origin| header, and uses any HTTP authentication method to identify the \textit{secretary} which in this case is the browser.
+CORS identifies the remote \textit{principal} with an \lstinline|Origin| header, and uses any HTTP authentication method to identify the \textit{secretary} which is the browser.
 
@@
 CORS has two agents, one acting on behalf of the other, and these are: 
-The Browser -- it takes the role of the \textit{secretary} as it is acting on behalf of javascript agents - the \textit{principals}.
-JavaScript code -- hosted on the internet and identified by the Origin Server that hosted the javascript.
+(1) The Browser: it takes the role of the \textit{secretary} as it is acting on behalf of javascript agents - the \textit{principals}.
+(2) JavaScript code: hosted on the internet and identified by the Origin Server that hosted the javascript.
 This javascript agent requests resources from the Browser, but it is unable to do it directly.
@@
 In our proposal, the identification of the agent in the \lstinline|On-Behalf-Of| header is much more precise.
-Combined with the ability of the secretary to also identify herself with a WebID, it builds an explicit trust relation between the user and the secretary, a situation in which the vagueness of the \lstinline|Origin| identity of the \textit{principal} is made a lot more difficult.
+Combined with the ability of the secretary to also identify herself with a WebID, it builds an explicit trust relation between the \textit{principal} and the \textit{secretary}.
+The vagueness of the \lstinline|Origin| identity of the \textit{principal} in CORS makes a lot of this more difficult.
+
+It is a topic of further research to evaluate in which circumstances it is important for the \lstinline|secretary| to also make sure that the remote server is aware that the connection being made is \lstinline|On-Behalf-Of| the specified \textit{principal}.
+For otherwise it is possible that the \textit{secretary} herself be made liable for the actions she is making on behalf of her \textit{principal}, especially were she to make \texttt{PUT}, \texttt{POST} or \texttt{DELETE} requests.
+The CORS protocol determines this by  requiring an initial \texttt{HEAD} request to a resource to be made, which will determine whether the server understands CORS.
+With the help of TLS the server hosting the remote resource could have a WebID Profile describing it to be an understander of the \lstinline|On-Behalf-Of| header, makeing the protocol a lot more efficient and secure once more.
 
@@
 %\todo{Nice up wording esp. our terms and language}
-In this paper we discussed different ways how an agent, such as a Social Web application, can act on behalf of a user and request as well as manipulate resources on the Web in the name this user.
-Our proposal for supporting such a communication schema involves an extension to the WebID protocol, which allows for delegation of access authorization from one agent to another agent, both identified by its WebID.
-The technical solution annotates these \textit{in-the-name-of} HTTP requests by adding the \lstinline|On-Behalf-Of| HTTP request header field which refers to the WebID of the user in which name the agent acts on.
+In this paper we discussed different ways in which an agent, such as a Social Web application, can act on behalf of a user and request as well as manipulate resources on the Web in the name this user.
+Our proposal for supporting such a communication schema involves an extension to the HTTP protocol, which allows for delegation of access authorization from one agent to another agent, both identified by their WebID.
+The technical solution annotates these HTTP requests by adding the \lstinline|On-Behalf-Of| header field which refers to the WebID of the user in whose name the agent acts.
 This distinguish the identities of the user and the agent and allows for creation of policy descriptions which use both WebIDs to specify the relations between the agent and the user in order to setup the access rules for this agent.
@@
 However, at this point we postpone the answer to the question of how we should describe the access control rules in a users WebID profile.
-There already exists first attempts from the Linked Data / Semantic Web and the Read Write Web communities such as the WebAccessControl vocabulary\footnote{\url{http://www.w3.org/wiki/WebAccessControl}}, $_{dg}$FOAF~\cite{schwagereit-f-2010-181-a} as well as different projects on policy creation and management~\cite{kagal-l-2005--a}.
+There already exists first attempts from the Linked Data/Semantic Web and the Read Write Web communities such as the WebAccessControl vocabulary\footnote{\url{http://www.w3.org/wiki/WebAccessControl}}, $_{dg}$FOAF~\cite{schwagereit-f-2010-181-a} as well as different projects on policy creation and management~\cite{kagal-l-2005--a}.
 In our future work we will try to close the gap between the policy and access control vocabularies on the one hand and WebID authentication on the other hand.

### 2012-08-04 paper.tex

@@
 This has the advantage of requiring no change to the WebID protocol.
-It does give the agent $A$ all powers of the user $U$ and so this type of privilege should be limited to agents in which are either extensions of $U$ or ones $U$ can or must fully trust anyway.
+It does give the agent $A$ all powers of the user $U$ and so this type of privilege should be limited to agents which are either extensions of $U$ or ones $U$ can or must fully trust anyway.
 
@@
 
-What kind of agents does it make sense to give such rights to?
-Or put another way: what agent would giving such rights to not constitute a reduction in security to the user?
-Or: which agent does the user and the authorization server already rely on completely?
+%In addition to the well known User Agents found in browsers on many different devices, there is one agent on which any service requiring WebID authentication trusts implicitly and this is the WebID profile's origin server.
+Any server requiring authentication of an agent using WebID must implicitly trust the origin server~\cite{barth-a-2011--a} hosting the WebID profile, since the profile hosting server can change any information in the profile.
+%Any user profile can then be thought of as being a user according to the origin server, i.e.
+\textit{user@origin.org:port} - where \textit{origin.org} is the domain of the origin server, and \textit{port} is the port the server is running on.
 
-In addition to the well known User Agents found in browsers on many different devices, there is one agent  on which any service requiring WebID authentication relies on completely and this is the WebID profile's origin server~\cite{barth-a-2011--a}.
-Any server requiring authentication of an agent using WebID must trust the origin server serving the WebID Profile.
-That origin server can at any time change the public keys in the profiles sent back to any authorization agents and indeed change any information in the profile it wants to.
-Any user profile can then be thought of as being a user according to the origin server ie a \url{user@origin.org:port} - where \url{origin.org} is the domain of the origin server, and \url{port} is the port the server is running on.
-
-When the user owns the origin server and there is a one to one relation between the two, as is principally the case in a personal FreedomBox, then the origin server is again just an extension of the user, and in that case there need be no thought of a difference between the user and the origin server.
-In that case the origin server can in fact just authenticate as the user whenever needed.
+When the user owns the origin server and there is a one-to-one relation between the two, as it is the case in a personal FreedomBox\footnote{http://www.freedomboxfoundation.org/}, then the origin server is just an extension of the user, and in that case trusting the server is the same as trusting the user.
+%In that case the origin server can in fact just authenticate as the user whenever needed.
 
 It should be noted that each device can still be distinguished by servers in case of a problem by logging the exact public key that was used to connect to a service. 
-It should be possible then to track down which device's private key had been compromised in case of unusual authentication behavior .
+It should be possible then to track down which device's private key had been compromised in case of unusual behaviour .
 
-Things get more interesting when an origin server agent $A$ is serving a number of different profiles $P_1$ \ldots $P_n$ each identifying respectively users $U_1$ \ldots $U_n$ and needs to act on behalf of these users.
-This would be the situation for servers acting for companies, government agencies, educational instituion, charities, football club, ....
-This brings up two issues that need to be taken into account: first an issue of data perspective and an efficiency issue.
+Things become more interesting when an origin server agent $A$ is serving a number of different profiles $P_1$ \ldots $P_n$ each identifying respectively users $U_1$ \ldots $U_n$ and needs to act on behalf of each of these users.
+This would be the situation for company servers, government agencies, educational institutions, charities, football clubs, etc.
+This brings up two issues that need to be taken into account, an issue of data perspective and an issue of efficiency.
 
 \paragraph{Keeping views distinct}-
-First whenever $A$ connects as $U_1$ to a remote resource $R$ it has to place the data received in a seperate graph from the one it stores public non authenticated data in, and to the one it stores a representation to the same resurce $R$ seen when connected as the different user $U_2$.
+First whenever $A$ connects as $U_1$ to a remote resource $R$ it has to place the data received in a separate graph from the one it stores public non authenticated data in, and to the one it stores a representation to the same resurce $R$ seen when connected as the different user $U_2$.
 This is because the resource may return different representations depending on who is connecting to it - one representation for close friends of the owner of $R$ perhaps, and one for more distant ones.
@@
 This could require $N$ parallel connections to the same server $S$. 
-Opening TLS connections is somewhat expensive: it requires opening up a new TCP connection and starting an expensive asymmetric key cryptography handshake. 
-For small numbers of N this can be defended, but as N becomes large the inefficiency this could create between two
-organisations may be a serious drawback.
+Opening TLS connections is somewhat expensive, as it requires expensive asymmetric key cryptographic computations. 
+When N becomes large, this inefficiency will be perceived as a serious drawback between two organisations.
 %\todo{calculate how inefficient this is, and at what size of network this starts really become problematic}
@@
 It could even use the same certificate.
-This would make clear to any server it was connecting to, that it could rely on this server as much as it could on the identity of any resource, and in particular any WebID profils served by that server.
+This would make clear to any server it was connecting to, that it could rely on this server as much as it could on the identity of any resource, and in particular any WebID profiles served by that server.
 
 Still, such an agent connecting to a remote service on behalf of one of its users would then need to identify which user it was acting on behalf of, or the remote service receiving a request would not know which access control rule to apply to the requesting origin server.
-For example in our previous example in the Romeo and Juliet story we showed how the Capulet family Freedom Box only shows Juliet as knowing Romeo, when Romeo makes the request on the resource, but not when the request is made by Romeo's father, lord Montague.
-That was an easy access control rule for the Capulet Freedbom Box to make when the request was using the WebID protocol simipliciter, since there it would know via the WebID authentication process exactly which identity the user was making the request as.
-But if it is the Origin Server connecting to the Capulet Freedom Box, identified as their Montague Origin Server, then what representation should the Capulet FB return? 
+For example in our previous example in the Romeo and Juliet story we showed how the Capulet family FreedomBox only shows Juliet as knowing Romeo, when Romeo makes the request on the resource, but not when the request is made by Romeo's father, lord Montague.
+That was an easy access control rule for the Capulet FreedomBox to make when the request was using the WebID protocol, since there it would know via the WebID authentication process exactly which identity the user was making the request as.
+But if it is the Origin Server connecting to the Capulet (FreedomBox), identified as their Montague Origin Server, then what representation should the Capulet FreedomBox return? 
 Should it return the reduced version available to Lord Montague?
@@
 
-The Capulet FB Guard having verified that this request does indeed come from the origin server of Romeo's profile
-\lstinline|<https://montague.net/romeo>| would then be able to accept that since the requesting server could in any case act as Romeo whenever it chose to do so, this protocol making exchange between the Montague and Capulet housholds more efficient without making it less secure, this be justification enough for it (the capulet freedom box) to  serve the representation that Romeo would have received had he connected to the server directly.
-We will argue further down that this is very similar to the way CORS deals with access control, namely by adding a header to a request to clarify what agent is making the request.
+The Capulet FreedomBox Guard having verified that this request does indeed come from the origin server of Romeo's profile
+https://montague.net/romeo would then be able to accept that since the requesting server could in any case act as Romeo whenever it chose to do so, this protocol making exchange between the Montague and Capulet houses more efficient without making it less secure, this be justification enough for it (the Capulet FreedomBox) to  serve the representation that Romeo would have received had he connected to the server directly.
+In Section~\ref{sec:relatedwork} we will argue that this is very similar to the way CORS deals with access control, namely by adding a header to a request in order to clarify what agent is making the request.
 
 This \lstinline|On-Behalf-Of| header makes it possible for the \textit{secretary} to open only one TLS connection to a remote server and be 
-able to specify for each request on behalf of whome it is making it.
-The Montague Freedom Box could make a request to the capulet Freedom Box \lstinline|On-Behalf-Of| Romeo, a few milliseconds later \lstinline|On-Behalf-Of| Lord Montague, and so on...
-Again as explained in the previous section is is the responsibility of the Montague Freedom Box to keep the returned information seperate, and act with secrecy whenever it is acting on behalf of one or the other of the users.
+able to specify for each request on behalf of whom it is making it.
+The Montague FreedomBox could make a request to the Capulet Freedom Box \lstinline|On-Behalf-Of| Romeo, a few milliseconds later \lstinline|On-Behalf-Of| Lord Montague, and so on.
+Again as explained in the previous section is is the responsibility of the Montague FreedomBox to keep the returned information separate, and act with secrecy whenever it is acting on behalf of one or the other of the users.
 As such it's role is not unlike the role of Friar Laurence in the play - dedication to people's private matters requires tact and secrecy.
@@
 It can no longer just compare the TLS keys of the requesting agent to see if it comes from the same Origin Server.
-We need to make this relation explicity by use of a special RDF relation provisionally called \lstinline|:secretary|%
+We need to make this relation explicit by use of a special RDF relation provisionally called \lstinline|:secretary|%
 \footnote{A object property with a domain and range as \lstinline|foaf:Agent| which we will provisionally place
@@
 
-The remote server can then verify that the identified agent is the secretary of the agent he wishes to act on behalf of (as sepecified in the \lstinline|On-Behalf-Of| header, by dereferencing that user's profile and verifying that the user specifies the \lstinline|:secretary| relation there, as it would if Romeo had the foaf profiles as shown in Listing \ref{listing:webid1}.
+The remote server can then verify that the identified agent is the secretary of the agent he wishes to act on behalf of (as specified in the \lstinline|On-Behalf-Of| header, by dereferencing that user's profile and verifying that the user specifies the \lstinline|:secretary| relation there, as it would if Romeo had the FOAF profiles as shown in Listing \ref{listing:webid1}.
 
@@
 Specifically the \lstinline|:secretary| relation currently does not distinguish what kind of repsonsibilities the \textit{principal} wishes to give to the \textit{secretary}. 
-It is currently assumed that the secretary has full rights.
-For ontowiki knowing the social network may be all that is needed to make access control decisions.
-Full delegation powers may not be needed.
-The ability to describe more limited secretary relations could be very helpful here.
+It is currently assumed that the secretary has full rights. For ontowiki knowing the social network may be all that is needed to make access control decisions. 
+Full delegation powers may not be needed. The ability to describe more limited secretary relations could be very helpful here.
 
@@
 However, at this point we postpone the answer to the question of how we should describe the access control rules in a users WebID profile.
-There already exists first attempts from the Linked Data/Semantic Web and the Read Write Web communities such as the WebAccessControl vocabulary\footnote{\url{http://www.w3.org/wiki/WebAccessControl}}, $_{dg}$FOAF~\cite{schwagereit-f-2010-181-a} as well as different projects on policy creation and management~\cite{kagal-l-2005--a}.
+There already exists first attempts from the Linked Data / Semantic Web and the Read Write Web communities such as the WebAccessControl vocabulary\footnote{\url{http://www.w3.org/wiki/WebAccessControl}}, $_{dg}$FOAF~\cite{schwagereit-f-2010-181-a} as well as different projects on policy creation and management~\cite{kagal-l-2005--a}.
 In our future work we will try to close the gap between the policy and access control vocabularies on the one hand and WebID authentication on the other hand.

### 2012-08-05 paper.tex
smaller fixes

@@
 
-The proposal here is for the Origin Server to add to each HTTP request (made over TLS) an \lstinline|On-Behalf-Of| header identifying the user on behalf of which the request is being made with that user's WebID.
+The proposal here is for the Origin Server to add to each HTTP request (made over TLS) an \lstinline|On-Behalf-Of| header identifying the user on behalf of which the request is being made with that user's WebID, as shown below:
 
@@
 Host: capulet.org
+On-Behalf-Of: https://montague.net/romeo#me
 User-Agent: FreedomBox_FamilyEdition/0.1 
 Accept: application/rdf+xml,text/turtle,application/xhtml+xml
-On-Behalf-Of: https://montague.net/romeo#me
 \end{verbatim}
@@
 The Capulet FreedomBox Guard having verified that this request does indeed come from the origin server of Romeo's profile
-https://montague.net/romeo would then be able to accept that since the requesting server could in any case act as Romeo whenever it chose to do so, this protocol making exchange between the Montague and Capulet houses more efficient without making it less secure, this be justification enough for it (the Capulet FreedomBox) to  serve the representation that Romeo would have received had he connected to the server directly.
+\lstinline|<https://montague.net/romeo>| would then be able to accept that since the requesting server could in any case act as Romeo whenever it chose to do so, this protocol making exchange between the Montague and Capulet houses more efficient without making it less secure, this be justification enough for it (the Capulet FreedomBox) to  serve the representation that Romeo would have received had he connected to the server directly.
 In Section~\ref{sec:relatedwork} we will argue that this is very similar to the way CORS deals with access control, namely by adding a header to a request in order to clarify what agent is making the request.
@@
 The Montague FreedomBox could make a request to the Capulet Freedom Box \lstinline|On-Behalf-Of| Romeo, a few milliseconds later \lstinline|On-Behalf-Of| Lord Montague, and so on.
-Again as explained in the previous section is is the responsibility of the Montague FreedomBox to keep the returned information separate, and act with secrecy whenever it is acting on behalf of one or the other of the users.
-As such it's role is not unlike the role of Friar Laurence in the play - dedication to people's private matters requires tact and secrecy.
+Again as explained in the previous section it is the responsibility of the Montague FreedomBox to keep the returned information separate, and act with discretion whenever it is acting on behalf of one or the other of the users.
+As such it's role is not unlike the role of Friar Laurence in the play - dedication to people's private matters requires tact and discretion.
 
@@
 
-If we now identify with a WebID the secretary that can act on behalf of a user, we can generalise the protocol somewhat.
+If we now identify the secretary that can act on behalf of a user using a WebID, we can generalise the protocol somewhat.
 That is, when an agent - such as the Montague FreedomBox Laurence with WebID \lstinline|<http://montague.net/fb#laurence>| - authenticates to a remote server it can use its own WebID. 
-This would allow the Agent to have its own public key, and so for a compromise of the client public key not to affect the server public key.
+This would allow the \textit{secretary} to have her own public key, and so to reduce the risk of her private key being compromised affecting the server public key.
 

### 2012-08-05 paper.tex
small fixes

@@
 The WebID protocol enables the global identification and authentication of agents in a distributed manner by combining asymmetric cryptography and Linked Data.
-But in order to decide whether access should be granted or denied to a particular WebID, the authenticating web server may need to retrieve other profiles and linked resources to work out e.g.
+In order to decide whether access should be granted or denied to a particular WebID, the authenticating web server may need to retrieve other profiles and linked resources to work out e.g.
 if the requesting agent is member of an authorized group.
-If these linked resources (e.g. FOAF profiles) are required to be publicly available for the server to access it, then this would be a major privacy limitation on a linked Social Network.
+If these resources are required to be publicly available for the server to access it, then this would be a major privacy limitation on a linked Social Network.
 In this paper we explore different ways in which an agent can act as a user and we propose an extension to the WebID protocol which allows for delegation of access authorization from a WebID to a third party, e.g.
@@
 \paragraph{Keeping views distinct}-
-First whenever $A$ connects as $U_1$ to a remote resource $R$ it has to place the data received in a separate graph from the one it stores public non authenticated data in, and to the one it stores a representation to the same resurce $R$ seen when connected as the different user $U_2$.
+First whenever $A$ connects as $U_1$ to a remote resource $R$ it has to place the data received in a separate graph from the one it stores public non authenticated data in, and to the one it stores a representation to the same resource $R$ seen when connected as the different user $U_2$.
 This is because the resource may return different representations depending on who is connecting to it - one representation for close friends of the owner of $R$ perhaps, and one for more distant ones.
@@
 It is very important that the agent receiving information from different users not merge the information that was destined to different users, or else information leakage will severely reduce the trust other agents have in that server $A$.
-This requires carefully keeping identified information that was aimed at different users seperate, perhaps by creating different graph stores: one for publically - non authenticated - information, and one graph store for each user the server needs to authenticate as.
+This requires carefully keeping identified information that was aimed at different users separate, perhaps by creating different graph stores: one for public - non authenticated - information, and one graph store for each user the server needs to authenticate as.
 
@@
 Opening TLS connections is somewhat expensive, as it requires expensive asymmetric key cryptographic computations. 
-When N becomes large, this inefficiency will be perceived as a serious drawback between two organisations.
+When $N$ becomes large, this inefficiency will be perceived as a serious drawback between two organisations.
 %\todo{calculate how inefficient this is, and at what size of network this starts really become problematic}
@@
 (3) The guard intercepts this request, and  in turn requests client authentication using TLS session renegotiation.
-The \textit{secretary} authenticates as itself by sending a Certificate containing a WebID refering to it.
+The \textit{secretary} authenticates as itself by sending a Certificate containing a WebID referring to it.
 The TLS-Light service verifies that the \textit{secretary} really is in possession of the private key corresponding to the public key sent in the certificate.
@@
 Its main purpose is to provide a unified user account, or simply \textit{user profile}.
-Currently these are tied to the my-profile-project web site, but it has been architected from the ground up to  work with distributed linked data, making it then easy to dissociate the software stack from the myprofile-project domain name,  and allowing it to be deployed on a machine under the user's control, prefereably even a device located within the user physical reach.
+Currently these are tied to the my-profile-project web site, but it has been architect from the ground up to work with distributed linked data, making it then easy to dissociate the software stack from the myprofile-project domain name, and allowing it to be deployed on a machine under the user's control, preferably even a device located within the user physical reach.
 
@@
 To improve user experience and overall performance, a caching mechanism is used to refresh local copies or "views" of external data.
-Due to multiple users coexisting on the same server, the caching mechanism needs to be able to distinguish views of remote resources as seen by different users, as they are served by remote servers depending on their access control and resoure filtering policies.
+Due to multiple users coexisting on the same server, the caching mechanism needs to be able to distinguish views of remote resources as seen by different users, as they are served by remote servers depending on their access control and resource filtering policies.
 
@@
 In addition to the usual features of wikis, OntoWiki provides a sophisticated extension system, such that it can be adapted for a variety of use-cases.
-Although the wikis usually enable anyone to edit everything, numerous real-world applications require aaccess-control mechanisms.
+Although the wikis usually enable anyone to edit everything, numerous real-world applications require access-control mechanisms.
 OntoWiki has built-in support for authorization on graph and action level.
@@
 This will require some further changes to the delegation protocol discussed up to now. 
-Specifically the \lstinline|:secretary| relation currently does not distinguish what kind of repsonsibilities the \textit{principal} wishes to give to the \textit{secretary}. 
+Specifically the \lstinline|:secretary| relation currently does not distinguish what kind of responsibilities the \textit{principal} wishes to give to the \textit{secretary}. 
 It is currently assumed that the secretary has full rights. For ontowiki knowing the social network may be all that is needed to make access control decisions. 
@@
 In this paper we proposed to add an \lstinline|On-Behalf-Of| header to each HTTP request made by a \textit{secretary} in order to be able to identify the \textit{principal} she is working for in that particular request.
-This is quite a major semantic addition to HTTP, but for which there is a widely adopted precedent, namely CORS\footnote{\url{http://www.w3.org/TR/cors/}}, the Cross Origin Resource Sharing spec at the W3C.
+This is quite a major semantic addition to HTTP, but for which there is a widely adopted precedent, namely CORS\footnote{\url{http://www.w3.org/TR/cors/}}, the Cross Origin Resource Sharing specification at the W3C.
 CORS identifies the remote \textit{principal} with an \lstinline|Origin| header, and uses any HTTP authentication method to identify the \textit{secretary} which is the browser.
@@
 CORS has two agents, one acting on behalf of the other, and these are: 
-(1) The Browser: it takes the role of the \textit{secretary} as it is acting on behalf of javascript agents - the \textit{principals}.
-(2) JavaScript code: hosted on the internet and identified by the Origin Server that hosted the javascript.
-This javascript agent requests resources from the Browser, but it is unable to do it directly.
+(1) The Browser: it takes the role of the \textit{secretary} as it is acting on behalf of JavaScript agents - the \textit{principals}.
+(2) JavaScript code: hosted on the internet and identified by the Origin Server that hosted the JavaScript.
+This JavaScript agent requests resources from the Browser, but it is unable to do it directly.
 
@@
 In CORS the browser is using its own identity credentials when connecting to remote servers (e.g. a bank), as it needs to alert the remote service that the request originates from a particular agent.
-The browser also needs to make sure the remote server understands this, especially when authentication is required, to allow the remote server to evaluate the strength of the Javascript trust relation.
+The browser also needs to make sure the remote server understands this, especially when authentication is required, to allow the remote server to evaluate the strength of the JavaScript trust relation.
 In the Section~\ref{sec:spec} use cases, the remote site trusts the \textit{principal}, but may not be aware of the \textit{secretary}.
@@
 The CORS protocol determines this by  requiring an initial \texttt{HEAD} request to a resource to be made, which will determine whether the server understands CORS.
-With the help of TLS the server hosting the remote resource could have a WebID Profile describing it to be an understander of the \lstinline|On-Behalf-Of| header, makeing the protocol a lot more efficient and secure once more.
+With the help of TLS the server hosting the remote resource could have a WebID Profile describing it to be an understander of the \lstinline|On-Behalf-Of| header, making the protocol a lot more efficient and secure once more.
 
@@
 In this paper we discussed different ways in which an agent, such as a Social Web application, can act on behalf of a user and request as well as manipulate resources on the Web in the name this user.
-Our proposal for supporting such a communication schema involves an extension to the HTTP protocol, which allows for delegation of access authorization from one agent to another agent, both identified by their WebID.
-The technical solution annotates these HTTP requests by adding the \lstinline|On-Behalf-Of| header field which refers to the WebID of the user in whose name the agent acts.
+Our proposal for supporting such a communication schema involves an extension to the WebID protocol, which allows for delegation of access authorization from one agent to another agent, both identified by their WebID.
+The technical solution for this concept annotates HTTP requests by adding the \lstinline|On-Behalf-Of| header field which refers to the WebID of the user in whose name the agent acts.
 This distinguish the identities of the user and the agent and allows for creation of policy descriptions which use both WebIDs to specify the relations between the agent and the user in order to setup the access rules for this agent.

### 2012-08-25 paper.tex
use autoref instead of ref

@@
 ]{hyperref}
+\def\sectionautorefname{Section}% redefine the label for section links
 
@@
 This can be illustrated using N3 graphs, by specifying a relation between a view on a resource (using a yet to be settled on vocabulary), and a graph which is the log:semantics of that view (cf.
-Listing~\ref{listing:views}).
+\autoref{listing:views}).
 It is very important that the agent receiving information from different users not merge the information that was destined to different users, or else information leakage will severely reduce the trust other agents have in that server $A$.
@@
 \lstinline|<https://montague.net/romeo>| would then be able to accept that since the requesting server could in any case act as Romeo whenever it chose to do so, this protocol making exchange between the Montague and Capulet houses more efficient without making it less secure, this be justification enough for it (the Capulet FreedomBox) to  serve the representation that Romeo would have received had he connected to the server directly.
-In Section~\ref{sec:relatedwork} we will argue that this is very similar to the way CORS deals with access control, namely by adding a header to a request in order to clarify what agent is making the request.
+In \autoref{sec:relatedwork} we will argue that this is very similar to the way CORS deals with access control, namely by adding a header to a request in order to clarify what agent is making the request.
 
@@
 
-The remote server can then verify that the identified agent is the secretary of the agent he wishes to act on behalf of (as specified in the \lstinline|On-Behalf-Of| header, by dereferencing that user's profile and verifying that the user specifies the \lstinline|:secretary| relation there, as it would if Romeo had the FOAF profiles as shown in Listing \ref{listing:webid1}.
+The remote server can then verify that the identified agent is the secretary of the agent he wishes to act on behalf of (as specified in the \lstinline|On-Behalf-Of| header, by dereferencing that user's profile and verifying that the user specifies the \lstinline|:secretary| relation there, as it would if Romeo had the FOAF profiles as shown in \autoref{listing:webid1}.
 
@@
 A first use-case for WebID access delegation within OntoWiki arises from an important functionality within OntoWiki, namely \textit{import of external data}.
-%Figure \ref{fig:ontowiki} shows a WebID profile that was imported via the Linked Data principles into a local knowledge base.
+%\autoref{fig:ontowiki} shows a WebID profile that was imported via the Linked Data principles into a local knowledge base.
 Since WebID profiles can contain personal information that is in need of protection, access to such data should be restricted with the WebID protocol.
@@
 The browser also needs to make sure the remote server understands this, especially when authentication is required, to allow the remote server to evaluate the strength of the JavaScript trust relation.
-In the Section~\ref{sec:spec} use cases, the remote site trusts the \textit{principal}, but may not be aware of the \textit{secretary}.
+In the \autoref{sec:spec} use cases, the remote site trusts the \textit{principal}, but may not be aware of the \textit{secretary}.
 In our proposal, the identification of the agent in the \lstinline|On-Behalf-Of| header is much more precise.

### 2012-08-25 paper.tex
add notes to the reviews, fix some issues

@@
 Things get more interesting in the authorization space.
-Consider a very natural application of WebID: allowing friends of one's friends (FOAF) access to some resources.
+Consider a very natural application of WebID: allowing friends of one's friends access to some resources.
 This authorization rule will require the web server to fetch each of its users' friends profiles, in order to build up the list of authorised users.
 But there is a privacy issue involved here: not everyone wants to make all of their social network publicly visible, and some may not want to make any of it publicly visible.
-Those people may then protect their FOAF profile with access control rules such as only allowing FOAF access to it.
-How can a server that needs access to these FOAF profiles in order to apply its own access control rules - such as only allowing access to FOAF - get access to the information? 
-Would the server itself need to be listed as a FOAF by each of the users friends?
+Those people may then protect their FOAF profile with access control rules such as only allowing friends of their friends access to it.
+How can a server that needs access to these FOAF profiles in order to apply its own access control rules get access to the information? 
+Would the server itself need to be listed as a friend of a friend by each of the users friends?
 Should the server take on the identity of the user it is fetching resources for? 
@@
 (2) Secretary that have many principals do not need to switch their certificate between requests.
-(3) It makes it possible to describe the relation between a principal and its secretary using linked data.
+(3) It makes it possible to describe the relation between a principal and its secretary using Linked Data.
 
@@
 
-The simplest solution for any user agent $A$ wishing to act as the user $U$, is for it to create a public/private key pair,  and with the public key thus generated create a certificate $C_u$ with $U$'s WebID in the Subject Alternative Name position and add the public key to the user $U$'s profile $P_u$.
+The simplest solution for any user agent $A$ wishing to act as the user $U$, is for it to create a public/private key pair,  and with the public key thus generated create a certificate $C_u$ with $U$'s WebID in the Subject Alternative Name position and add the public key to the user $U$'s profile $P_u$ (see \autoref{listing:multipleKeyProfile}).
 Having done this the agent $A$ can then connect using the certificate $C_u$ and its associated private key, to any service it wishes to, when it wants to work for/as the user $U$.
@@
 
-The remote server can then verify that the identified agent is the secretary of the agent he wishes to act on behalf of (as specified in the \lstinline|On-Behalf-Of| header, by dereferencing that user's profile and verifying that the user specifies the \lstinline|:secretary| relation there, as it would if Romeo had the FOAF profiles as shown in \autoref{listing:webid1}.
+The remote server can then verify that the identified agent is the secretary of the agent he wishes to act on behalf of (as specified in the \lstinline|On-Behalf-Of| header, by dereferencing that user's profile and verifying that the user specifies the \texttt{:secretary} relation there, as it would if Romeo had the FOAF profiles as shown in \autoref{listing:webid1}.
 
@@
 Its main purpose is to provide a unified user account, or simply \textit{user profile}.
-Currently these are tied to the my-profile-project web site, but it has been architect from the ground up to work with distributed linked data, making it then easy to dissociate the software stack from the myprofile-project domain name, and allowing it to be deployed on a machine under the user's control, preferably even a device located within the user physical reach.
+Currently these are tied to the my-profile-project web site, but it has been architect from the ground up to work with distributed Linked Data, making it then easy to dissociate the software stack from the myprofile-project domain name, and allowing it to be deployed on a machine under the user's control, preferably even a device located within the user physical reach.
 

### 2012-09-06 paper.tex

@@
 \medskip\and
-CNRS Samovar UMR 5157, TELECOM SudParis\\
+CNRS Samovar UMR 5157, Institut Mines-Telecom / Telecom SudParis\\
 \email{andrei.sambra@it-sudparis.eu}\\
@@
 As two real-world examples we describe two different implementations where WebID delegation is deployed and needed.
-MyProfile is WebID profile service application and OntoWiki a semantic data wiki.
+MyProfile is a WebID identity service application and OntoWiki a semantic data wiki.
 
 \textbf{MyProfile}\footnote{\url{http://myprofile-project.org/}}
-is a web server demonstrating how easy it is to create a WebID profile, and buidling up some distributed social web applications upon this.
+is a web service demonstrating how easy it is to create a WebID profile, and also building up distributed social web applications upon it.
 Its main purpose is to provide a unified user account, or simply \textit{user profile}.
-Currently these are tied to the my-profile-project web site, but it has been architect from the ground up to work with distributed Linked Data, making it then easy to dissociate the software stack from the myprofile-project domain name, and allowing it to be deployed on a machine under the user's control, preferably even a device located within the user physical reach.
+Currently these are tied to the MyProfile project web site, but it has been designed from the ground up to work with distributed Linked Data, making it then easy to dissociate the software stack from the MyProfile project domain name, allowing it to be deployed on a machine under the user's control, preferably even a device located within the user physical reach.
 

### 2012-09-07 paper.tex
simplifications in the text. (should have been part of previous comit)

@@
 The WebID protocol enables the global identification and authentication of agents in a distributed manner by combining asymmetric cryptography and Linked Data.
-In order to decide whether access should be granted or denied to a particular WebID, the authenticating web server may need to retrieve other profiles and linked resources to work out e.g.
-if the requesting agent is member of an authorized group.
-If these resources are required to be publicly available for the server to access it, then this would be a major privacy limitation on a linked Social Network.
-In this paper we explore different ways in which an agent can act as a user and we propose an extension to the WebID protocol which allows for delegation of access authorization from a WebID to a third party, e.g.
-allowing a server to be able to act on behalf of its users.
+In order to decide whether access should be granted or denied to a particular WebID, the authenticating web server may need to retrieve other profiles and linked resources to work out if the requesting agent is member of an authorized group (e.g.
+friends of the resource owner's friends).
+If it were required for such resources to be publicly available, this would be a major privacy limitation on a linked Social Network.
+In this paper we explore different ways in which an agent can act on behalf of a user and we propose an extension to the WebID protocol which allows for delegation of access authorization.
 This extends the range of application scenarios where WebID authentication can be efficiently deployed while increasing privacy.
@@
 
-The World Wide Web is a peer to peer communication system designed from the outset to work in a global space, between agents distributed around the world and acting in parallel, with no center of control, in a space where new agents can at any point join and there is no complete overview of the whole system.
+The World Wide Web is a peer to peer communication system designed from the outset to work in a global space, between agents distributed around the world and acting independently, with no center of control, in a space where new agents can at any point join and there is no complete overview of the whole system.
 These agents need know nothing of each other up to the point of their interaction.
-This is the force that leads the web to its declarative functional architecture, with its emphasis on naming and a logic of unalterability of the meaning of names (URIs).
+These architectural requirements are the reason for the web's declarative functional architecture, with its emphasis on naming and a logic of unalterability of the meaning of names (URIs).
 
@@
 
-The WebID protocol enables the global identification of agents using asymmetric cryptography in a way that fits cleanly with this architecture:
-namely in such a way that agents can verify each others identity without having had any previous interactions and in such a way as to allow trust to build up in a decentralized manner.
+A \textit{WebID} is a URI that refers to an agent - person, robot, group or other thing that can act intentionally.
+The WebID should be a URI which when dereferenced returns a representation whose description uniquely identifies the agent as the controller of a public key~\cite{sporny-m-2011--a,story-h-2009--a}.
 
-A \textit{WebID} is a URI that refers to an agent - person, robot, group or other thing that can have intentions.
-The WebID should be a URI which when dereferenced returns a representation whose description uniquely identifies the agent as the controller of a public key~\cite{sporny-m-2011--a,story-h-2009--a}
+The WebID protocol enables the global identification of agents using asymmetric cryptography in a way that fits cleanly with web architecture:
+namely in such a way that agents can verify each others identity without having had any previous interactions and in such a way as to allow trust to build up in a decentralized manner through a linked web of trust.
 
-The WebID protocol is used currently mostly for client authentication%
-\footnote{Server authentication using IETF DANE follows much the same logic, except that the lookup for the identity is not done using the HTTP protocol but DNSSEC~\cite{hoffman-p-2012--a}.}.
 It is worth noting that the host serving the WebID profiles controls the identity of every agent whose URI is within that server's namespace.
 This service is known as the origin server~\cite{barth-a-2011--a}.
-It is the origin of all resources served by it.
 
-We can easily think of the origin server as not only able to respond to requests, but also as an agent able to make requests.
-Indeed WebID authentication requires the server to make WebID profile requests to other servers in order to verify the identity of agents making a request to it.
-The WebID specification describes this task as being accomplished by a separate agent, the WebID verifier - which could indeed be done by another service on the web (WebID proxy authentication servers).
-But it can also be so closely tied to the web service that it would be natural to think of it as part of that same service.
-The WebID profile furthermore could be served by the same agent as the one making the request, in which case we have a minimal case of a peer to peer communication.
-Note that fetching a WebID profile for WebID authentication should be done anonymously, for fear of authentication deadlocks%
-\footnote{For example one can imagine an agent $S$ with profile $P_s$ requesting a resource on server $R$ which requires authentication.
+The WebID protocol is designed for client authentication%
+\footnote{Server authentication using IETF DANE follows much the same logic, except that the lookup for the identity is not done using the HTTP protocol but DNSSEC~\cite{hoffman-p-2012--a}.}.
+But the origin server does not just respond to requests, it also is able to make requests.
+Indeed WebID authentication requires the server to make WebID profile requests to other servers in order to verify the identity of agents%
+\footnote{Note that fetching a WebID profile for WebID authentication should be done anonymously, for fear of authentication deadlocks. 
+For example one can imagine an agent $S$ with profile $P_s$ requesting a resource on server $R$ which requires authentication.
 $S$ would send $R$ its certificate, thereby requiring $R$ to dereference $S$'s profile $P_s$ in order to verify the WebID.
@@
 Consider a very natural application of WebID: allowing friends of one's friends access to some resources.
-This authorization rule will require the web server to fetch each of its users' friends profiles, in order to build up the list of authorised users.
+This authorization rule will require the web server to fetch each of the resource owner's friends profiles, in order to build up the list of authorised users.
 But there is a privacy issue involved here: not everyone wants to make all of their social network publicly visible, and some may not want to make any of it publicly visible.
-Those people may then protect their FOAF profile with access control rules such as only allowing friends of their friends access to it.
+Those people may then protect their FOAF profile with access control rules such as one only allowing friends of their friends access to it.
 How can a server that needs access to these FOAF profiles in order to apply its own access control rules get access to the information? 
@@
 
-When the user owns the origin server and there is a one-to-one relation between the two, as it is the case in a personal FreedomBox\footnote{http://www.freedomboxfoundation.org/}, then the origin server is just an extension of the user, and in that case trusting the server is the same as trusting the user.
+When the user owns the origin server and there is a one-to-one relation between the two, as it is the case in a personal FBx\footnote{\url{http://www.freedomboxfoundation.org/}} (FBx henceforth), then the origin server is just an extension of the user, and in that case trusting the server is the same as trusting the user.
 %In that case the origin server can in fact just authenticate as the user whenever needed.
@@
 Still, such an agent connecting to a remote service on behalf of one of its users would then need to identify which user it was acting on behalf of, or the remote service receiving a request would not know which access control rule to apply to the requesting origin server.
-For example in our previous example in the Romeo and Juliet story we showed how the Capulet family FreedomBox only shows Juliet as knowing Romeo, when Romeo makes the request on the resource, but not when the request is made by Romeo's father, lord Montague.
-That was an easy access control rule for the Capulet FreedomBox to make when the request was using the WebID protocol, since there it would know via the WebID authentication process exactly which identity the user was making the request as.
-But if it is the Origin Server connecting to the Capulet (FreedomBox), identified as their Montague Origin Server, then what representation should the Capulet FreedomBox return? 
+For example in our previous example in the Romeo and Juliet story we showed how the Capulet family FBx only shows Juliet as knowing Romeo, when Romeo makes the request on the resource, but not when the request is made by Romeo's father, lord Montague.
+That was an easy access control rule for the Capulet FBx to make when the request was using the WebID protocol, since there it would know via the WebID authentication process exactly which identity the user was making the request as.
+But if it is the Origin Server connecting to the Capulet FB, identified as their Montague Origin Server, then what representation should the Capulet FBx return? 
 Should it return the reduced version available to Lord Montague?
@@
 
-The proposal here is for the Origin Server to add to each HTTP request (made over TLS) an \lstinline|On-Behalf-Of| header identifying the user on behalf of which the request is being made with that user's WebID, as shown below:
+The proposal here is for the Origin Server to add to each HTTP request (made over TLS) an \lstinline|X-On-Behalf-Of| header identifying the user on behalf of which the request is being made with that user's WebID, as shown below:
 
@@
 Host: capulet.org
-On-Behalf-Of: https://montague.net/romeo#me
+X-On-Behalf-Of: https://montague.net/romeo#me
 User-Agent: FreedomBox_FamilyEdition/0.1 
@@
 
-The Capulet FreedomBox Guard having verified that this request does indeed come from the origin server of Romeo's profile
-\lstinline|<https://montague.net/romeo>| would then be able to accept that since the requesting server could in any case act as Romeo whenever it chose to do so, this protocol making exchange between the Montague and Capulet houses more efficient without making it less secure, this be justification enough for it (the Capulet FreedomBox) to  serve the representation that Romeo would have received had he connected to the server directly.
+The Capulet FBx Guard having verified that this request does indeed come from the origin server of Romeo's profile
+\lstinline|<https://montague.net/romeo>| would then be able to accept that since the requesting server could in any case act as Romeo whenever it chose to do so, this protocol making exchange between the Montague and Capulet houses more efficient without making it less secure, this be justification enough for it (the Capulet FBx) to  serve the representation that Romeo would have received had he connected to the server directly.
 In \autoref{sec:relatedwork} we will argue that this is very similar to the way CORS deals with access control, namely by adding a header to a request in order to clarify what agent is making the request.
 
-This \lstinline|On-Behalf-Of| header makes it possible for the \textit{secretary} to open only one TLS connection to a remote server and be 
+This \lstinline|X-On-Behalf-Of| header makes it possible for the \textit{secretary} to open only one TLS connection to a remote server and be 
 able to specify for each request on behalf of whom it is making it.
-The Montague FreedomBox could make a request to the Capulet Freedom Box \lstinline|On-Behalf-Of| Romeo, a few milliseconds later \lstinline|On-Behalf-Of| Lord Montague, and so on.
-Again as explained in the previous section it is the responsibility of the Montague FreedomBox to keep the returned information separate, and act with discretion whenever it is acting on behalf of one or the other of the users.
+The Montague FBx could make a request to the Capulet Freedom Box \lstinline|X-On-Behalf-Of| Romeo, a few milliseconds later \lstinline|X-On-Behalf-Of| Lord Montague, and so on.
+Again as explained in the previous section it is the responsibility of the Montague FBx to keep the returned information separate, and act with discretion whenever it is acting on behalf of one or the other of the users.
 As such it's role is not unlike the role of Friar Laurence in the play - dedication to people's private matters requires tact and discretion.
@@
 If we now identify the secretary that can act on behalf of a user using a WebID, we can generalise the protocol somewhat.
-That is, when an agent - such as the Montague FreedomBox Laurence with WebID \lstinline|<http://montague.net/fb#laurence>| - authenticates to a remote server it can use its own WebID. 
+That is, when an agent - such as the Montague FBx Laurence with WebID \lstinline|<http://montague.net/fb#laurence>| - authenticates to a remote server it can use its own WebID. 
 This would allow the \textit{secretary} to have her own public key, and so to reduce the risk of her private key being compromised affecting the server public key.
@@
 We need to make this relation explicit by use of a special RDF relation provisionally called \lstinline|:secretary|%
-\footnote{A object property with a domain and range as \lstinline|foaf:Agent| which we will provisionally place
-in the \lstinline|cert:| namespace, though it may be more appropriately placed in the \lstinline|auth:| namespace.}
+\footnote{\url{http://bblfish.net/work/2012/09/trust#secretary} }
 
@@
 
-The remote server can then verify that the identified agent is the secretary of the agent he wishes to act on behalf of (as specified in the \lstinline|On-Behalf-Of| header, by dereferencing that user's profile and verifying that the user specifies the \texttt{:secretary} relation there, as it would if Romeo had the FOAF profiles as shown in \autoref{listing:webid1}.
+The remote server can then verify that the identified agent is the secretary of the agent he wishes to act on behalf of (as specified in the \lstinline|X-On-Behalf-Of| header, by dereferencing that user's profile and verifying that the user specifies the \texttt{:secretary} relation there, as it would if Romeo had the FOAF profiles as shown in \autoref{listing:webid1}.
 
@@
 This is defined in the TLS protocol \cite{dierks-t-2012--a}.
-(4) The guard ask the verification agent to verify the secretary WebID which is named in the certificate (5a).
+(4) The guard asks the verification agent to verify the secretary WebID which is named in the certificate (5a).
 This process is exactly as described in the WebID protocol~\cite{story-h-2009--a}.
-The guard also asks the verifier agent to check the secretary claim implied by the \lstinline|On-Behalf-Of| header.
+The guard also asks the verifier agent to check the secretary claim implied by the \lstinline|X-On-Behalf-Of| header.
 (5b) The \textit{principal} agent's relation to the \textit{secretary} is  verified by dereferencing the \textit{principal}'s WebID Profile, and verifying it responds with a true to the SPARQL ASK query \lstinline|ASK { ?principal :secretary ?secretary .
@@
 \paragraph{Cross Origin Resource Sharing (CORS)}
-In this paper we proposed to add an \lstinline|On-Behalf-Of| header to each HTTP request made by a \textit{secretary} in order to be able to identify the \textit{principal} she is working for in that particular request.
+In this paper we proposed to add an \lstinline|X-On-Behalf-Of| header to each HTTP request made by a \textit{secretary} in order to be able to identify the \textit{principal} she is working for in that particular request.
 This is quite a major semantic addition to HTTP, but for which there is a widely adopted precedent, namely CORS\footnote{\url{http://www.w3.org/TR/cors/}}, the Cross Origin Resource Sharing specification at the W3C.
@@
 In the \autoref{sec:spec} use cases, the remote site trusts the \textit{principal}, but may not be aware of the \textit{secretary}.
-In our proposal, the identification of the agent in the \lstinline|On-Behalf-Of| header is much more precise.
+In our proposal, the identification of the agent in the \lstinline|X-On-Behalf-Of| header is much more precise.
 Combined with the ability of the secretary to also identify herself with a WebID, it builds an explicit trust relation between the \textit{principal} and the \textit{secretary}.
@@
 
-It is a topic of further research to evaluate in which circumstances it is important for the \lstinline|secretary| to also make sure that the remote server is aware that the connection being made is \lstinline|On-Behalf-Of| the specified \textit{principal}.
+It is a topic of further research to evaluate in which circumstances it is important for the \lstinline|secretary| to also make sure that the remote server is aware that the connection being made is \lstinline|X-On-Behalf-Of| the specified \textit{principal}.
 For otherwise it is possible that the \textit{secretary} herself be made liable for the actions she is making on behalf of her \textit{principal}, especially were she to make \texttt{PUT}, \texttt{POST} or \texttt{DELETE} requests.
 The CORS protocol determines this by  requiring an initial \texttt{HEAD} request to a resource to be made, which will determine whether the server understands CORS.
-With the help of TLS the server hosting the remote resource could have a WebID Profile describing it to be an understander of the \lstinline|On-Behalf-Of| header, making the protocol a lot more efficient and secure once more.
+With the help of TLS the server hosting the remote resource could have a WebID Profile describing it to be an understander of the \lstinline|X-On-Behalf-Of| header, making the protocol a lot more efficient and secure once more.
 
@@
 Our proposal for supporting such a communication schema involves an extension to the WebID protocol, which allows for delegation of access authorization from one agent to another agent, both identified by their WebID.
-The technical solution for this concept annotates HTTP requests by adding the \lstinline|On-Behalf-Of| header field which refers to the WebID of the user in whose name the agent acts.
+The technical solution for this concept annotates HTTP requests by adding the \lstinline|X-On-Behalf-Of| header field which refers to the WebID of the user in whose name the agent acts.
 This distinguish the identities of the user and the agent and allows for creation of policy descriptions which use both WebIDs to specify the relations between the agent and the user in order to setup the access rules for this agent.

### 2012-09-07 paper.tex

@@
 
-As two real-world examples we describe two different implementations where WebID delegation is deployed and needed.
+We describe two different implementations where WebID delegation is deployed and needed.
 MyProfile is a WebID identity service application and OntoWiki a semantic data wiki.
@@
 \textbf{MyProfile}\footnote{\url{http://myprofile-project.org/}}
-is a web service demonstrating how easy it is to create a WebID profile, and also building up distributed social web applications upon it.
-Its main purpose is to provide a unified user account, or simply \textit{user profile}.
-Currently these are tied to the MyProfile project web site, but it has been designed from the ground up to work with distributed Linked Data, making it then easy to dissociate the software stack from the MyProfile project domain name, allowing it to be deployed on a machine under the user's control, preferably even a device located within the user physical reach.
+is a web service demonstrating how easy it is to both create a WebID profile, and to build up distributed social web applications upon it.
+Its main purpose is to provide a unified user account through a simple \textit{user profile}.
+Currently these are tied to the MyProfile project web site, but it has been designed from the ground up to work with distributed Linked Data, making it easy to dissociate the software stack from the MyProfile project domain name, allowing it to be deployed on a machine under the user's control such as a FBx.
 
@@
 
-In the case of MyProfile, it is very important to be able to offer WebID access delegation, because a single MyProfile server instance can host multiple users, and must fetch resources for each user asynchronously in order to be able to provide a seamless and rapid user experience.
+It is very important for MyProfile to be able to use WebID access delegation, because a single MyProfile server instance can host multiple users, and must fetch resources for each user asynchronously in order to be able to provide a seamless and rapid user experience.
 To improve user experience and overall performance, a caching mechanism is used to refresh local copies or "views" of external data.
-Due to multiple users coexisting on the same server, the caching mechanism needs to be able to distinguish views of remote resources as seen by different users, as they are served by remote servers depending on their access control and resource filtering policies.
-
-Let's take for example the following case:
-Ann and Barry are both local users on a single MyProfile server.
-Charley is an external user with access control policies set up on his private server.
-When Ann requests to view Charley's profile data, a personalized view of the profile is displayed, corresponding to access control policies by Barry for requests made by Ann.
-When Barry requests to view Charley's profile, different profile data is displayed, since there are different access control policies for Barry.
-The caching mechanism needs to be able to cache two different profile views, each corresponding to access control policies specific for the user requesting the data.
-As the number of users on MyProfile grows this has to be done as efficiently as possible, and so re-using TLS connections where possible is a laudable aim.
+With multiple users coexisting on the same server, the caching mechanism needs to be able to distinguish views of remote resources as seen by different users, as they are served by remote servers depending on their access control and resource filtering policies.
+As the number of users on MyProfile grows this has to be done as efficiently as possible, and so re-using TLS connections where possible is important.
 
@@
 %\paragraph{Data import}
-A first use-case for WebID access delegation within OntoWiki arises from an important functionality within OntoWiki, namely \textit{import of external data}.
+A first use-case for WebID access delegation within OntoWiki arises from the need to \textit{import external data}.
 %\autoref{fig:ontowiki} shows a WebID profile that was imported via the Linked Data principles into a local knowledge base.
-Since WebID profiles can contain personal information that is in need of protection, access to such data should be restricted with the WebID protocol.
+Since WebID profiles can contain personal information, access to such data should be restricted with the WebID protocol.
 Although a user may (or may not in the case of a periodically executed automatic synchronization process) initiate the import procedure manually via the OntoWiki user interface, the actual fetching is done in the background.
@@
 Thus the system is not able to use that information when requesting data.
-With WebID access delegation though, the profile can be fetched on behalf of the user instead.
+With WebID access delegation though, profiles can be fetched on behalf of the user instead.
 
@@
 Even if OAuth provides authentication as a by-product of having the resource owner authorize a third-party client to her resource server, its main focus is on resource authorization rather than on federated identity.
-The conclusion is that OAuth is used to \textit{provide access for external services to local user resources} without disclosing the user's credentials.
+In short OAuth is used to \textit{provide access for external services to local user resources} without disclosing the user's credentials.
 %On the other hand, in WebID access delegation, the secretary is used to \textit{gain access to external resources} on behalf of a given user.
-Or in other words: OAuth is used to allow an agent to \textit{request a users resources} while WebID delegation is used to allow an agent to \textit{request resources the user could request herself}.
+OAuth is used to allow an agent to \textit{request a user's resources} while WebID delegation is used to allow an agent to \textit{request resources the user could request herself}.
 
@@
 This is quite a major semantic addition to HTTP, but for which there is a widely adopted precedent, namely CORS\footnote{\url{http://www.w3.org/TR/cors/}}, the Cross Origin Resource Sharing specification at the W3C.
-CORS identifies the remote \textit{principal} with an \lstinline|Origin| header, and uses any HTTP authentication method to identify the \textit{secretary} which is the browser.
 
-Let us look at this in more detail.
 CORS has two agents, one acting on behalf of the other, and these are: 
-(1) The Browser: it takes the role of the \textit{secretary} as it is acting on behalf of JavaScript agents - the \textit{principals}.
-(2) JavaScript code: hosted on the internet and identified by the Origin Server that hosted the JavaScript.
+(1) The Browser: it takes the role of the \textit{secretary} as it is acting on behalf of a JavaScript agent - the \textit{principal}. It identifies itself as the browser user.
+(2) JavaScript code: hosted on the internet and identified by the Origin Server that hosted it.
 This JavaScript agent requests resources from the Browser, but it is unable to do it directly. 
+CORS identifies the remote \textit{principal} with an \lstinline|Origin| header, and uses any HTTP authentication method to identify the \textit{secretary}.
 
-The use cases for CORS are slightly different from the ones for our delegation proposal. 
-In CORS the browser is using its own identity credentials when connecting to remote servers (e.g. a bank), as it needs to alert the remote service that the request originates from a particular agent.
-The browser also needs to make sure the remote server understands this, especially when authentication is required, to allow the remote server to evaluate the strength of the JavaScript trust relation.
+The use cases for CORS are slightly different from the ones for our delegation proposal but the logic is similar. 
+In CORS the browser is using its own identity credentials when connecting to remote servers (e.g. a bank), but it needs to alert the remote service that the request originates from a different agent.
+The browser also needs to make sure the remote server understands this, especially when authentication is required, to allow the remote server to evaluate wether it trusts the JavaScript agent.
 In the \autoref{sec:spec} use cases, the remote site trusts the \textit{principal}, but may not be aware of the \textit{secretary}.
@@
 Combined with the ability of the secretary to also identify herself with a WebID, it builds an explicit trust relation between the \textit{principal} and the \textit{secretary}.
-The vagueness of the \lstinline|Origin| identity of the \textit{principal} in CORS makes a lot of this more difficult.
+The vagueness of the \lstinline|Origin| identity of the \textit{principal} in CORS makes a lot of this close to impossible.
 
@@
 
-However, at this point we postpone the answer to the question of how we should describe the access control rules in a users WebID profile.
+However, at this point we postpone the answer to the question of how we should describe the access control rules in a user's WebID profile.
 There already exists first attempts from the Linked Data / Semantic Web and the Read Write Web communities such as the WebAccessControl vocabulary\footnote{\url{http://www.w3.org/wiki/WebAccessControl}}, $_{dg}$FOAF~\cite{schwagereit-f-2010-181-a} as well as different projects on policy creation and management~\cite{kagal-l-2005--a}.

### 2012-09-07 paper.tex
Add section on Usage Restrictions.

@@
 It should know how to distinguish what remote servers tell it when it is acting on behalf of one user, from what a remote server tells it when it is acting on behalf of another user.
-The role of the keeper of secrets for a person is known as the secretary role - a prestigious role taken on for example by figures such as the Secretary of State, Hillary Clinton.
+The role of the keeper of secrets for a person is known as the secretary role - a prestigious role taken on for example by figures such as the Secretary of State.
 
@@
 With multiple users coexisting on the same server, the caching mechanism needs to be able to distinguish views of remote resources as seen by different users, as they are served by remote servers depending on their access control and resource filtering policies.
-As the number of users on MyProfile grows this has to be done as efficiently as possible, and so re-using TLS connections where possible is important.
+As the number of users on MyProfile grows this has to be done efficiently, and so re-using TLS connections where possible is important.
 
@@
 
+\paragraph{Usage Restrictions}
+
+Oshani Seneviratne and Lalana Kagal have proposed\cite{DBLP:conf/policy/SeneviratneK11} to allow clients and servers to specify restrictions on what is allowed to be done with the documents they publish using headers such as \lstinline|X-UsageRestrictions|.
+This would for example allow someone posting a picture to a server to specify that this does not entail transfer of ownership.
+
+Similarly, using such an HTTP header, it should be possible for the server serving a protected resource to specify which groups of users a resource representation is intended for.
+This could remove an important reason for the existence of the \lstinline|X-On-Behalf-Of| header discussed above.
+The Guard on the server would just need to add the secretary for the principal as one of those agents authorized to access the information.
+It would know the identity of the secretary for that user by consulting the WebID profile, which it needs to have downloaded anyway.
+
+But how would the Guard know that the secretary understood the header and the corresponding restriction vocabulary? 
+After all most servers and clients do not know this vocabulary - it has not even been settled on yet - and so cannot be held responsible for not understanding it.
+We can reach again here to our WebID Profile to settle this: the secretary can specify herself as being an understander of that vocabulary in her profile with a triple such as \lstinline|:me a trust:VocabularyUnderstander.|
+The server would check for this statement in the secretary's WebID Profile before serving the resource.
+The advantage of this method would be that it would require less changes to the WebID authentication protocol, could be a lot more flexible, but does require the development of a simple usage restriction vocabulary.
+The secretary relation still remains essential.
+
 \section{Conclusion and Future Work}\label{sec:conclusion}
@@
 %\todo{Nice up wording esp. our terms and language}
-In this paper we discussed different ways in which an agent, such as a Social Web application, can act on behalf of a user and request as well as manipulate resources on the Web in the name this user.
-Our proposal for supporting such a communication schema involves an extension to the WebID protocol, which allows for delegation of access authorization from one agent to another agent, both identified by their WebID.
-The technical solution for this concept annotates HTTP requests by adding the \lstinline|X-On-Behalf-Of| header field which refers to the WebID of the user in whose name the agent acts.
-This distinguish the identities of the user and the agent and allows for creation of policy descriptions which use both WebIDs to specify the relations between the agent and the user in order to setup the access rules for this agent.
-Since the protocol footprint is minimal, the main information entropy to decide whether an agent has the right to request a specific resource or not is available as part of the content of a WebID profile which can be requested as Linked Data.
-We believe that such an shift of the entropy from a protocol endpoint (such as in OAuth) to a machine readable document is a crucial feature of Linked Data in general and WebID in detail.
+In this paper we justified the need for an agent, such as a Social Web application, to act on behalf of a user in the role of a secretary.
+The server may need to do things asynchronously in the background for the user ( the principal ), and may have a number of different users for which this needs to be done efficiently.
+Our proposal for supporting such a communication schema involves adding a \lstinline|:secretary| relation from the principal's profile to the agent that acts on its behalf. 
+The secretary then connects to the resource using her own WebID.
+We then came up with two solutions on how the client can specify that it is acting as a secretary:
 
-However, at this point we postpone the answer to the question of how we should describe the access control rules in a user's WebID profile.
-There already exists first attempts from the Linked Data / Semantic Web and the Read Write Web communities such as the WebAccessControl vocabulary\footnote{\url{http://www.w3.org/wiki/WebAccessControl}}, $_{dg}$FOAF~\cite{schwagereit-f-2010-181-a} as well as different projects on policy creation and management~\cite{kagal-l-2005--a}.
+(1) The secretary making the request can add an  \lstinline|X-On-Behalf-Of| header field refering to the WebID of the principal in whose name she acts.
+This is especially useful if resources return different representations depending on who makes the request, or on behalf of whome a request is made.
+
+(2) The server can specify usage restrictions in the header of the HTTP response, allowing the secretary only to pass the information on to the principal for example.  
+Perhaps this could be done using the WebAccessControl vocabulary\footnote{\url{http://www.w3.org/wiki/WebAccessControl}}, $_{dg}$FOAF~\cite{schwagereit-f-2010-181-a}, or ideas coming from the policy creation and management communities~\cite{kagal-l-2005--a}.
+
 In our future work we will try to close the gap between the policy and access control vocabularies on the one hand and WebID authentication on the other hand.
-A rough abstract in which direction this should be elaborated is presented in \autoref{listing:views} and we hope that we can sensitize others to take up this challenge too.
-
+This will require mostly standardisation work and seeing which type of solution is the most apt to gain traction in a wider community.
+As we deploy Social Web servers the need for a such a standard will be felt more and more strongly.
 \bibliographystyle{plain}

### 2012-09-07 paper.tex
shortened title

@@
 pdfauthor={Sebastian Tramp, Henry Story, Andrei Sambra, Philipp Frischmut, Michael Martin, and S\"oren Auer},
-pdftitle={Extending the WebID Protocol with Access Delegation},
+pdftitle={The WebID Protocol and Access Delegation},
 pdfkeywords={WebID, Social Semantic Web, Access Delegation}
@@
 
-\title{Extending the WebID Protocol with Access Delegation}
+\title{The WebID Protocol and Access Delegation}
 

### 2012-09-10 paper.tex
fix url
proof reading everything except conclusion

--- 2012-09-07 paper.tex
@@
 
-It is worth noting that the host serving the WebID profiles controls the identity of every agent whose URI is within that server's namespace.
+It is worth noting that the host serving the WebID profiles controls the identity of every agent whose URI is within that server's namespaces.
 This service is known as the origin server~\cite{barth-a-2011--a}.
@@
 \footnote{Server authentication using IETF DANE follows much the same logic, except that the lookup for the identity is not done using the HTTP protocol but DNSSEC~\cite{hoffman-p-2012--a}.}.
-But the origin server does not just respond to requests, it also is able to make requests.
+But the origin server does not just respond to requests, the server is also able to make requests.
 Indeed WebID authentication requires the server to make WebID profile requests to other servers in order to verify the identity of agents%
@@
 Consider a very natural application of WebID: allowing friends of one's friends access to some resources.
-This authorization rule will require the web server to fetch each of the resource owner's friends profiles, in order to build up the list of authorised users.
+This authorization rule will require the web server to fetch each of the resource owner's friends profiles, in order to build up the list of authorized users.
 But there is a privacy issue involved here: not everyone wants to make all of their social network publicly visible, and some may not want to make any of it publicly visible.
@@
 The rest of the paper is organized in the following way:
-\autoref{sec:req} describes preliminary requirements which we had in mind for our solution,
+\autoref{sec:req} describes preliminary requirements which we had in mind for our solution and clarifies some important terms,
 \autoref{sec:spec} goes into detail with the WebID specification and adds support for authorization delegation,
-in \autoref{sec:eval} we describe our reference implementations based on two web applications which is followed by \autoref{sec:relatedwork} where we compare our proposal with two other protocols, namely CORS and OAuth.
+in \autoref{sec:eval} we describe our reference scenarios based on two web applications which is followed by \autoref{sec:relatedwork} where we compare our proposal with other protocols, namely CORS, OAuth and Usage Restrictions.
 Finally, we conclude our work in \autoref{sec:conclusion} and give directions for future work.
@@
 
-\paragraph{Distinguish secretary from principal }-
+\paragraph{Distinguish secretary from principal} -
 Identity should as far as possible be transparent.
@@
 (2) Secretary that have many principals do not need to switch their certificate between requests.
-(3) It makes it possible to describe the relation between a principal and its secretary using Linked Data.
+(3) It makes it possible to describe the relationship between a principal and its secretary using Linked Data.
 
-\paragraph{Easy to use}-
+\paragraph{Easy to use} -
 The one and only place to describe which secretary are allowed to operate for a principal should be the principal's WebID profile.
@@
 
-\paragraph{Minimal protocol footprint}-
+\paragraph{Minimal protocol footprint} -
 %In addition to the integration requirement
@@
 
-\paragraph{Efficiency}-
+\paragraph{Efficiency} -
 Finally, the proposed solution should scale with growing number of users and connections.
@@
 The simplest solution for any user agent $A$ wishing to act as the user $U$, is for it to create a public/private key pair, and with the public key thus generated create a certificate $C_u$ with $U$'s WebID in the Subject Alternative Name position and add the public key to the user $U$'s profile $P_u$ (see \autoref{listing:multipleKeyProfile}).
-Having done this the agent $A$ can then connect using the certificate $C_u$ and its associated private key, to any service it wishes to, when it wants to work for/as the user $U$.
+Having done this, the agent $A$ can then connect using the certificate $C_u$ and its associated private key to any service it wishes to, when it wants to work for/as the user $U$.
 This has the advantage of requiring no change to the WebID protocol.
-It does give the agent $A$ all powers of the user $U$ and so this type of privilege should be limited to agents which are either extensions of $U$ or ones $U$ can or must fully trust anyway.
+It does give the agent $A$ all powers of the user $U$ and so this type of privilege should be limited to agents which are either extensions of $U$ such as smartphones are, or ones $U$ can or must fully trust anyway.
 
@@
 
-When the user owns the origin server and there is a one-to-one relation between the two, as it is the case in a personal FBx\footnote{\url{http://www.freedomboxfoundation.org/}} (FBx henceforth), then the origin server is just an extension of the user, and in that case trusting the server is the same as trusting the user.
+When the user owns the origin server and there is a one-to-one relation between the two, as it is the case in a personal FreedomBox\footnote{\url{http://www.freedomboxfoundation.org/}} (FBx henceforth), then the origin server is just an extension of the user, and in that case trusting the server is the same as trusting the user.
 %In that case the origin server can in fact just authenticate as the user whenever needed.
@@
 It should be noted that each device can still be distinguished by servers in case of a problem by logging the exact public key that was used to connect to a service. 
-It should be possible then to track down which device's private key had been compromised in case of unusual behaviour .
+It should be possible then to track down which device's private key had been compromised in case of unusual behavior.
 
@@
 
-\paragraph{Keeping views distinct}-
+\paragraph{Keeping views distinct}
 First whenever $A$ connects as $U_1$ to a remote resource $R$ it has to place the data received in a separate graph from the one it stores public non authenticated data in, and to the one it stores a representation to the same resource $R$ seen when connected as the different user $U_2$.
@@
 \autoref{listing:views}).
-It is very important that the agent receiving information from different users not merge the information that was destined to different users, or else information leakage will severely reduce the trust other agents have in that server $A$.
+It is very important that the agent receiving information from different users does not merge the information that was destined to different users, or else information leakage will severely reduce the trust other agents have in that server $A$.
 This requires carefully keeping identified information that was aimed at different users separate, perhaps by creating different graph stores: one for public - non authenticated - information, and one graph store for each user the server needs to authenticate as.
@@
 
-\paragraph{Efficiency}-Secondly, whenever the Origin Server needs to act as $U_1$ to a remote server $R$ it will need to open a new TLS connection to that server using the certificate $C_{u1}$ for that user.
+\paragraph{Efficiency}
+Secondly, whenever the Origin Server needs to act as $U_1$ to a remote server $R$ it will need to open a new TLS connection to that server using the certificate $C_{u1}$ for that user.
 This could require $N$ parallel connections to the same server $S$. 
 Opening TLS connections is somewhat expensive, as it requires expensive asymmetric key cryptographic computations. 
-When $N$ becomes large, this inefficiency will be perceived as a serious drawback between two organisations.
+When $N$ becomes large, this inefficiency will be perceived as a serious drawback between two organizations.
 %\todo{calculate how inefficient this is, and at what size of network this starts really become problematic}
@@
 \paragraph{Conclusion} 
-
 It is possible for any number of software agents to act AS the user by creating themselves a public key as described above.
@@
 This method also becomes inefficient the greater the number of different users  an agent is working for.
+In addition to that, identification of different secretaries is done using cryptographic keys rather than URIs.
 
@@
 Still, such an agent connecting to a remote service on behalf of one of its users would then need to identify which user it was acting on behalf of, or the remote service receiving a request would not know which access control rule to apply to the requesting origin server.
-For example in our previous example in the Romeo and Juliet story we showed how the Capulet family FBx only shows Juliet as knowing Romeo, when Romeo makes the request on the resource, but not when the request is made by Romeo's father, lord Montague.
+For example in our previous example, in the Romeo and Juliet story, we showed how the Capulet family FBx only shows Juliet as knowing Romeo, when Romeo makes the request on the resource, but not when the request is made by Romeo's father, lord Montague.
 That was an easy access control rule for the Capulet FBx to make when the request was using the WebID protocol, since there it would know via the WebID authentication process exactly which identity the user was making the request as.
-But if it is the Origin Server connecting to the Capulet FB, identified as their Montague Origin Server, then what representation should the Capulet FBx return? 
+But if it is the Origin Server connecting to the Capulet FBx, identified as their Montague Origin Server, then what representation should the Capulet FBx return? 
 Should it return the reduced version available to Lord Montague?
@@
 
-The proposal here is for the Origin Server to add to each HTTP request (made over TLS) an \lstinline|X-On-Behalf-Of| header identifying the user on behalf of which the request is being made with that user's WebID, as shown below:
+The proposal here is for the Origin Server to add to \textit{each HTTP request} (made over TLS) an \lstinline|X-On-Behalf-Of| header identifying the user on behalf of which the request is being made with that user's WebID, as shown below:
 
@@
 
-This \lstinline|X-On-Behalf-Of| header makes it possible for the \textit{secretary} to open only one TLS connection to a remote server and be 
-able to specify for each request on behalf of whom it is making it.
+This \lstinline|X-On-Behalf-Of| header makes it possible for the \textit{secretary} to open only one TLS connection to a remote server and be able to specify for each request on behalf of whom it is making it.
 The Montague FBx could make a request to the Capulet Freedom Box \lstinline|X-On-Behalf-Of| Romeo, a few milliseconds later \lstinline|X-On-Behalf-Of| Lord Montague, and so on. 
@@
 
-If we now identify the secretary that can act on behalf of a user using a WebID, we can generalise the protocol somewhat.
+If we now identify the secretary that can act on behalf of a user using a WebID, we can generalize the protocol somewhat.
 That is, when an agent - such as the Montague FBx Laurence with WebID \lstinline|<http://montague.net/fb#laurence>| - authenticates to a remote server it can use its own WebID. 
@@
 We need to make this relation explicit by use of a special RDF relation provisionally called \lstinline|:secretary|%
-\footnote{\url{http://bblfish.net/work/2012/09/trust#secretary} }
+\footnote{\url{http://bblfish.net/work/2012/09/trust\#secretary} }
 
@@
 (2) Once TLS is set up, the HTTP request is sent to the server (e.g.
-a \verb!HTTP GET!), with an additional \lstinline|On-Behalf-Of| header, which thereby defines the requesting agent as a \textit{secretary} and the referred to agent as the \textit{principal}
+a \verb!HTTP GET!), with an additional \lstinline|X-On-Behalf-Of| header, which thereby defines the requesting agent as a \textit{secretary} and the referred to agent as the \textit{principal}.
 (3) The guard intercepts this request, and in turn requests client authentication using TLS session renegotiation.
-The \textit{secretary} authenticates as itself by sending a Certificate containing a WebID referring to it.
+The \textit{secretary} authenticates as itself by sending a certificate containing a WebID referring to it.
 The TLS-Light service verifies that the \textit{secretary} really is in possession of the private key corresponding to the public key sent in the certificate.
-This is defined in the TLS protocol \cite{dierks-t-2012--a}.
+This is defined in the TLS protocol~\cite{dierks-t-2012--a}.
 (4) The guard asks the verification agent to verify the secretary WebID which is named in the certificate (5a).
@@
 The guard also asks the verifier agent to check the secretary claim implied by the \lstinline|X-On-Behalf-Of| header.
-(5b) The \textit{principal} agent's relation to the \textit{secretary} is  verified by dereferencing the \textit{principal}'s WebID Profile, and verifying it responds with a true to the SPARQL ASK query \lstinline|ASK { ?principal :secretary ?secretary .
+(5b) The \textit{principal} agent's relation to the \textit{secretary} is verified by dereferencing the \textit{principal}'s WebID profile, and verifying it responds with a true to the SPARQL ASK query \lstinline|ASK { ?principal :secretary ?secretary .
 }| where the \lstinline|?principal| and \lstinline|?secretary| variables have been bound to the correct URIs.
 (6) The authentication and verification process having succeeded, the authorization process checking if the \textit{principal} would get access to the requested resource.
-(7) The resource representation can then be returned or not depending on the access control rules.
+(7) The resource representation can then be returned or not, depending on the access control rules.
 
@@
 
-\section{Implementation and Evaluation}\label{sec:eval}
+\section{Application Scenarios}\label{sec:eval}
 
-We describe two different implementations where WebID delegation is deployed and needed.
+We describe two different application scenarios where WebID delegation is essential:
 MyProfile is a WebID identity service application and OntoWiki a semantic data wiki.
@@
 \cite{auer-s-2006-736-a} is a web application, which allows publication, exploration as well as manipulation of arbitrary RDF knowledge bases in distributed scenarios.
-We refer to it as a data wiki, since it adopts the wiki philosophy (ease of editing, tracking of changes, integrated discussions) on the one hand, while focussing on structured information on the other hand.
+We refer to it as a data wiki, since it adopts the wiki philosophy (ease of editing, tracking of changes, integrated discussions) on the one hand, while focusing on structured information on the other hand.
 Furthermore OntoWiki is an adaptable application framework, which supports the creation of Linked Data based applications on the web~\cite{heino-n-2009-61-a}.
@@
 Specifically the \lstinline|:secretary| relation currently does not distinguish what kind of responsibilities the \textit{principal} wishes to give to the \textit{secretary}. 
-It is currently assumed that the secretary has full rights. For ontowiki knowing the social network may be all that is needed to make access control decisions. 
-Full delegation powers may not be needed. The ability to describe more limited secretary relations could be very helpful here.
+It is currently assumed that the secretary has full rights.
+For OntoWiki knowing the Social Network is all that is needed to make access control decisions and full delegation powers may not be needed.
+The ability to describe more limited secretary relations could be very helpful here.
 
@@
 OAuth includes two main parts: obtaining an access token by asking the resource owner (i.e. the user) to grant access, and then using the tokens to access protected resources. 
-%Here is a typical example of using OAuth. 
-%Ann has a Twitter account.
-%One day she decides to support her favourite project by using Flattr\footnote{\url{http://flattr.com}}, a micro payment service.
-%Since she would rather not create a new account, Flattr offers her the possibility of using her Twitter account to log into Flattr.
+Here is a typical example of using OAuth. 
+Ann has a Twitter account and decides to support her favorite project by using Flattr\footnote{A micro payment service: \url{http://flattr.com}}.
+Since she would rather not create a new account, Flattr offers her the possibility of using her Twitter account to log into Flattr.
 %After clicking the "Login using Twitter" button, she is redirected to Twitter's login page where she inputs her user name and password.
-%Once authenticated, Twitter informs her that Flattr would like to access her personal information (e.g. name, picture, etc.).
-%She can now choose if she wants to grant or deny to Flattr access to her Twitter account information.
+Once authenticated, Twitter informs her that Flattr would like to access her personal information.
+She can now choose if she wants to grant or deny to Flattr access to her Twitter account information.
 %Once she accepts, she is redirected back to Flattr where she notices that she is now authenticated, and her Twitter user name, full name and picture now appear in Flattr.
+
 The advantage here is that Ann only had to use her Twitter credentials to log into Flattr.
@@
 Even if OAuth provides authentication as a by-product of having the resource owner authorize a third-party client to her resource server, its main focus is on resource authorization rather than on federated identity.
-In short OAuth is used to \textit{provide access for external services to local user resources} without disclosing the user's credentials.
+In short, OAuth is used to \textit{provide access for external services to local user resources} without disclosing the user's credentials.
 %On the other hand, in WebID access delegation, the secretary is used to \textit{gain access to external resources} on behalf of a given user.
@@
 
-CORS has two agents, one acting on behalf of the other, and these are: 
+CORS defines two agents, one acting on behalf of the other, and these are: 
 (1) The Browser: it takes the role of the \textit{secretary} as it is acting on behalf of a JavaScript agent - the \textit{principal}. It identifies itself as the browser user.
-(2) JavaScript code: hosted on the internet and identified by the Origin Server that hosted it.
+(2) JavaScript code: hosted on the WWW and identified by the Origin Server that hosted it.
 This JavaScript agent requests resources from the Browser, but it is unable to do it directly. 
@@
 In CORS the browser is using its own identity credentials when connecting to remote servers (e.g. a bank), but it needs to alert the remote service that the request originates from a different agent.
-The browser also needs to make sure the remote server understands this, especially when authentication is required, to allow the remote server to evaluate wether it trusts the JavaScript agent.
+The browser also needs to make sure the remote server understands this, especially when authentication is required, to allow the remote server to evaluate whether it trusts the JavaScript agent.
 In the \autoref{sec:spec} use cases, the remote site trusts the \textit{principal}, but may not be aware of the \textit{secretary}.
@@
 It is a topic of further research to evaluate in which circumstances it is important for the \lstinline|secretary| to also make sure that the remote server is aware that the connection being made is \lstinline|X-On-Behalf-Of| the specified \textit{principal}.
-For otherwise it is possible that the \textit{secretary} herself be made liable for the actions she is making on behalf of her \textit{principal}, especially were she to make \texttt{PUT}, \texttt{POST} or \texttt{DELETE} requests.
+Otherwise it is possible that the \textit{secretary} herself be made liable for the actions she is making on behalf of her \textit{principal}, especially were she to make \texttt{PUT}, \texttt{POST} or \texttt{DELETE} requests.
 The CORS protocol determines this by requiring an initial \texttt{HEAD} request to a resource to be made, which will determine whether the server understands CORS.
-With the help of TLS the server hosting the remote resource could have a WebID Profile describing it to be an understander of the \lstinline|X-On-Behalf-Of| header, making the protocol a lot more efficient and secure once more.
+With the help of TLS the server hosting the remote resource could have a WebID profile describing it to be an understander of the \lstinline|X-On-Behalf-Of| header, making the protocol a lot more efficient and secure once more.
 
@@
 
-Oshani Seneviratne and Lalana Kagal have proposed\cite{DBLP:conf/policy/SeneviratneK11} to allow clients and servers to specify restrictions on what is allowed to be done with the documents they publish using headers such as \lstinline|X-UsageRestrictions|.
+such as proposed in~\cite{DBLP:conf/policy/SeneviratneK11} can be used to allow clients and servers to specify restrictions on what is allowed to be done with the documents they publish using headers such as \lstinline|X-UsageRestrictions|.
 This would for example allow someone posting a picture to a server to specify that this does not entail transfer of ownership.
@@
 This could remove an important reason for the existence of the \lstinline|X-On-Behalf-Of| header discussed above.
-The Guard on the server would just need to add the secretary for the principal as one of those agents authorized to access the information.
+The guard on the server would just need to add the secretary for the principal as one of those agents authorized to access the information.
 It would know the identity of the secretary for that user by consulting the WebID profile, which it needs to have downloaded anyway.
 
-But how would the Guard know that the secretary understood the header and the corresponding restriction vocabulary? 
+But how would the guard know that the secretary understood the header and the corresponding restriction vocabulary? 
 After all most servers and clients do not know this vocabulary - it has not even been settled on yet - and so cannot be held responsible for not understanding it.
-We can reach again here to our WebID Profile to settle this: the secretary can specify herself as being an understander of that vocabulary in her profile with a triple such as \lstinline|:me a trust:VocabularyUnderstander.|
-The server would check for this statement in the secretary's WebID Profile before serving the resource.
-The advantage of this method would be that it would require less changes to the WebID authentication protocol, could be a lot more flexible, but does require the development of a simple usage restriction vocabulary.
+We can reach again here to our WebID profile to settle this: the secretary can specify herself as being an understander of that vocabulary in her profile with a triple such as \lstinline|:me a trust:VocabularyUnderstander.|
+The server would check for this statement in the secretary's WebID profile before serving the resource.
+The advantage of this method would be that it would require less changes to the WebID authentication protocol, could be a lot more flexible but does require the development of a simple usage restriction vocabulary.
 The secretary relation still remains essential.

### 2012-09-10 paper.tex
proof read conclusion

@@
 In this paper we justified the need for an agent, such as a Social Web application, to act on behalf of a user in the role of a secretary.
-The server may need to do things asynchronously in the background for the user ( the principal ), and may have a number of different users for which this needs to be done efficiently.
+The server may need to do things asynchronously in the background for the user (the principal), and may have a number of different users for which this needs to be done efficiently.
 Our proposal for supporting such a communication schema involves adding a \lstinline|:secretary| relation from the principal's profile to the agent that acts on its behalf. 
@@
 
-(1) The secretary making the request can add an  \lstinline|X-On-Behalf-Of| header field refering to the WebID of the principal in whose name she acts.
-This is especially useful if resources return different representations depending on who makes the request, or on behalf of whome a request is made.
+(1) The secretary making the request can add an  \lstinline|X-On-Behalf-Of| header field referring to the WebID of the principal in whose name she acts.
+This is especially useful if resources return different representations depending on who makes the request, or on behalf of whom a request is made.
 
@@
 In our future work we will try to close the gap between the policy and access control vocabularies on the one hand and WebID authentication on the other hand.
-This will require mostly standardisation work and seeing which type of solution is the most apt to gain traction in a wider community.
+This will require mostly standardization work and seeing which type of solution is the most apt to gain traction in a wider community.
 As we deploy Social Web servers the need for a such a standard will be felt more and more strongly.
+
 \bibliographystyle{plain}
